---
title: "Workflow to use agGraphSearch and Mesh RDF: WF-002"
shorttitle: "WF-002: match labels to the Mesh data via SPARQL"
author:
  - name: Satoshi Kume
date: "`r Sys.Date()`"
graphics: no
package: agGraphSearch, knitr, SPARQL
output:
  BiocStyle::html_document:
  toc_float: true
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{agGraphSearch}
  %\VignetteIndexEntry{WF-002: match labels to the wikidata via SPARQL}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r style, echo=FALSE, message=FALSE, results='asis'}
BiocStyle::markdown()
```

**Last modified:** `r file.info("agGraphSearch-WF-002.Rmd")$mtime`<br />
**Compiled**: `r date()`

# Getting started

Once `r Rpackage("agGraphSearch")` is installed, it can be loaded by the following command.

```{r library, echo=TRUE, eval=FALSE}
#rm( list=ls() )
library(agGraphSearch)
library(magrittr)

#Re-build
rm( list=ls() )

if(TRUE){
system("rm -rf ./agGraphSearch/NAMESPACE")
roxygen2::roxygenise("./agGraphSearch")
system("cat ./agGraphSearch/NAMESPACE")
remove.packages("agGraphSearch", lib=.libPaths())
.rs.restartR()
}

#install.packages(c("SPARQL", "franc", "formattable"))

if(T){
system("R CMD INSTALL agGraphSearch")
Sys.sleep(1)
library(agGraphSearch)
}

if(F){
proxy_url = "http://wwwproxy.osakac.ac.jp:8080"
Sys.setenv("http_proxy" = proxy_url)
Sys.setenv("https_proxy" = proxy_url)
Sys.setenv("ftp_proxy" = proxy_url)
}

if(F){
proxy_url = "http://wwwproxy.osakac.ac.jp:8080"
Sys.setenv("http_proxy" = proxy_url)
Sys.setenv("https_proxy" = proxy_url)
Sys.setenv("ftp_proxy" = proxy_url)
devtools::install_github( "kumeS/agGraphSearch" )
library(agGraphSearch)
}

if(F){
devtools::install_github( "kumeS/agGraphSearch" )
library(agGraphSearch)
}

```

# Read the csv files

You should split compound words as a pre-processing.

```{r echo=TRUE, eval=FALSE}
words <- data.frame(readr::read_csv("./00_Mesh_Input/words.cR.csv", col_names = F, show_col_types = F))
words <- unlist(words, use.names = F)
words <- data.frame(X1=words[!is.na(words)])
```

if the WF-001 is skipped, start with the command as follows.

```{r echo=TRUE, eval=FALSE}
f <- system.file("extdata", "Mesh_words.cR.csv", package="agGraphSearch")
words <- data.frame(readr::read_csv(f, col_names = F, show_col_types = F))

```

# check the data

```{r echo=TRUE, eval=FALSE}
head(words)
dim(words)

#unique number
length(unique(words))

#table
head(words)
#agTableKB(words, Head = F, Align = 3)
```

# Downloads the Mesh files from the repository (Google Drive).

```{r, echo=TRUE, eval=FALSE}
#save
if(!dir.exists("00_Mesh_Input")){dir.create("00_Mesh_Input")}

#file path
proxy <- 'export https_proxy="http://wwwproxy.osakac.ac.jp:8080"; export ftp_proxy="http://wwwproxy.osakac.ac.jp:8080"'
scr <- system.file("script", "gdrive_download.sh", package="agGraphSearch")

#mesh219_2020_2021_others2_df.Rds
File_ID <- "1Pf28EA4mRc59JeFi4VREcBuS-AcTqxQm"
File_Name <- "mesh219_2020_2021_others2_df.Rds"
system(paste0(proxy, "; source ", scr, "; gdrive_download ", File_ID, " ./00_Mesh_Input/", File_Name, " "))

#mesh219_2020_2021_Label_en_df.Rds
File_ID <- "1afoPL1xEJPxW7k72nD3ZWXEGMq94JMno"
File_Name <- "mesh219_2020_2021_Label_en_df.Rds"
system(paste0(proxy, "; source ", scr, "; gdrive_download '", File_ID, "' ./00_Mesh_Input/", File_Name, " "))

```

# Import Mesh data (2021)

```{r, echo=TRUE, eval=FALSE}
MeshLabels <- readRDS("./00_Mesh_Input/mesh2021_Label_en_df_R.Rds")
head(MeshLabels)
table(stringr::str_sub(MeshLabels$Subject, start=1, end=6))

#check property
table(MeshLabels$Property)

MeshOthers <- readRDS("./00_Mesh_Input/mesh2021_others_df_R.Rds")
MeshOthersR <- readRDS("./00_Mesh_Input/mesh2021_others_df_RR.Rds")
dim(MeshOthers)
dim(MeshOthersR)

#check property
table(MeshOthers$Property)

```

# remove other data

```{r echo=TRUE, eval=FALSE}
if(F){
#head(MeshLabels[!grepl("^A[0-9][0-9]|^B[0-9][0-9]", MeshLabels$Object),])
MeshLabels00 <- MeshLabels
MeshLabels00 <- MeshLabels00[!grepl("^[A-Z][0-9][0-9]|^[[]OBSOLETE", MeshLabels00$Object),]

#property
MeshLabels00 <- MeshLabels00[!grepl("meshv:scopeNote|meshv:thesaurusID|meshv:lexicalTag|meshv:lastActiveYear", MeshLabels00$Property),]
MeshLabels00 <- MeshLabels00[!grepl("meshv:historyNote|meshv:publicMeSHNote|meshv:previousIndexing|meshv:annotation|meshv:source|meshv:note|meshv:sortVersion|meshv:abbreviation|meshv:onlineNote|meshv:considerAlso|meshv:entryVersion", MeshLabels00$Property),]

#Order
MeshLabels00 <- MeshLabels00[order(MeshLabels00$Property),]

#check property
table(MeshLabels00$Property)
head(MeshLabels00)
table(stringr::str_sub(MeshLabels00$Subject, start=1, end=6))

#Extract D terms
table(grepl("[:]D", MeshLabels00$Subject))
table(grepl("[:]D|[:]M", MeshLabels00$Subject))
head(MeshLabels00[grepl("[:]D", MeshLabels00$Subject),], n=20)
MeshLabels_D00 <- MeshLabels00[grepl("[:]D", MeshLabels00$Subject),]
#head(MeshLabels_D00, n=20)

#head(MeshLabels00)
if(T){
readr::write_csv(MeshLabels00, file="./00_Mesh_Input/MeshLabels00.csv", col_names = F, append=F)
saveRDS(MeshLabels00, "./00_Mesh_Input/MeshLabels00.Rds")
readr::write_csv(MeshLabels_D00, file="./00_Mesh_Input/MeshLabels_D00.csv", col_names = F, append=F)
saveRDS(MeshLabels_D00, "./00_Mesh_Input/MeshLabels_D00.Rds")
}
}
```

# Linking of input words to the Mesh words

Input words in English are 428.

```{r echo=TRUE, eval=FALSE}
##restart
rm( list=ls() )

MeshLabels00 <- readRDS("./00_Mesh_Input/MeshLabels_D00.Rds")

head( MeshLabels00, n=10 )
dim(MeshLabels00)
length(unique(MeshLabels00$Object))

words <- unlist(data.frame(readr::read_csv("./00_Mesh_Input/words.cR.csv", col_names = F, show_col_types = FALSE)), use.names = F)
words <- unlist(words, use.names = F)
words <- words[!is.na(words)]
words <- words[words != ""]
words <- unique(words)

head(words)
length(unique(words))

#小文字変換
head(MeshLabels00)
MeshLabels01 <- unique(tolower(MeshLabels00$Object))
head(MeshLabels01)
length(MeshLabels01)

head(words)
words00 <- unique(unlist(words)); words00 <- words00[!is.na(words00)]
words01 <- unique(tolower(words00))
head(words01)

#文字列距離実行
library( agGraphSearch )
Dat <- ComputeDistance(InputTerms=words01,
                       RDFterms=MeshLabels01,
                       q=2, nthread=4, TopWords=3)
  
head(Dat)
table(Dat$PerfectMatch > 0)
table(Dat$PartialMatch > 0)
table(Dat$cosine1 > 0)

if(!dir.exists("01_Mesh_Out")){dir.create("01_Mesh_Out")}
readr::write_csv(Dat, file="./01_Mesh_Out/DistanceDat_Out.csv", col_names = T, append=F)
saveRDS(Dat, "./01_Mesh_Out/DistanceDat_Out.Rds")
```

#O/Xをつけて、閾値を決める
#コサインが良いかも

```{r echo=TRUE, eval=FALSE}
rm( list=ls() )

#options(digits=5) 
Thres <- data.frame(readr::read_csv("./01_Mesh_Out/Dat210610_v02.csv", col_names = T))

head(Thres)
tail(Thres)
Thres$Check0 <- NA
Thres$Check0[Thres$Check == 0] <- "X"
Thres$Check0[Thres$Check == 1] <- "O"
Thres$cosine3 <- as.integer(Thres$cosine3*10000)/10000

#Create the plot
library(ggplot2)
ggplot(Thres, aes(x = Check0, y = cosine3)) +
  geom_boxplot(outlier.colour = NA, width = .4) +
  geom_dotplot(binaxis = "y", binwidth = .005, stackdir = "center", fill = NA)

summary(Thres$cosine3[Thres$Check == 0])
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.0762  0.2417  0.3164  0.3138  0.3814  0.6087 
#厳し目基準なら、Thres = 0.075

head(Thres)
words02 <- Thres[Thres$cosine3 < 0.075, ]
head(words02)
dim(words02)
rownames(words02) <- 1:nrow(words02)

saveRDS(words02, "./01_Mesh_Out/words02.Rds")
```

# Translate English to Japanese

```{r echo=TRUE, eval=FALSE}
rm(list=ls())

words02 <- readRDS("./01_Mesh_Out/words02.Rds")
head(words02)

words02$Lab00 <- NA
head(words02)

#ラベルを逆にする
head(words02)
words02$Lab00 <- tolower(words02$cosine2)
words02$Lab01 <- NA
head(words02)

table(grepl("[,][ ]", words02$Lab00))
table(grepl("[,][ ]and", words02$Lab00))

for(n in 1:length(words02$Lab00)){
#n <- 5
if(grepl("[,][ ]", words02$Lab00[n])){
 aa <- strsplit(words02$Lab00[n], split = ", ")[[1]]
 words02$Lab01[n] <- paste(aa[length(aa):1], collapse = " ")
}else{
 aa <-  words02$Lab00[n]
 words02$Lab01[n] <- aa
}}
table(grepl("[,]", words02$Lab01))

words02$Jpn <- NA
head(words02, n=10)

#Translate to Jpn
if(F){
proxy_url = "http://wwwproxy.osakac.ac.jp:8080"
Sys.setenv("http_proxy" = proxy_url)
Sys.setenv("https_proxy" = proxy_url)
Sys.setenv("ftp_proxy" = proxy_url)
}

head(words02)
for(n in 1:length(words02$Lab01)){
#n <- 1
print(n)
Result <- DeePL(Sentence=words02$Lab01[n], Auth_Key="43725ffd-d3d3-a301-c92d-8d7e2070f71c:fx")
words02$Jpn[n] <- Result
}

head(words02, n=10)
tail(words02, n=10)
words02[is.na(words02)] <- 0

#PerfectMatch
a <- words02$PerfectMatch > 0
unique(words02$Terms[a])
sum(a)
#[1] 54

#PartialMatch
a <- words02$PartialMatch > 0
unique(words02$Terms[a])
sum(a)
#[1] 57

#cosine3
a <- words02$cosine3 < 0.075
unique(words02$Terms[a])
sum(a)
#[1] 101

#######################################
#Save
saveRDS(words02, "./01_Mesh_Out/words02_Jpn.Rds")
readr::write_excel_csv(words02, file="./01_Mesh_Out/words02_Jpn.csv", col_names = T, append=F)
#######################################
```

# Linking to the Mesh

Use the below propertys for researching the class hierarchy.
- meshv:broaderDescriptor
- meshv:concept => meshv:reverseConcept

```{r echo=TRUE, eval=FALSE}
rm(list=ls())

#Match List
words02 <- readRDS("./01_Mesh_Out/words02_Jpn.Rds")
head(words02)

table(words02$cosine2 == words02$Lab00)
table(words02$cosine2 == words02$Lab01)

#Mesh D term List
MeshLabels00 <- readRDS("./00_Mesh_Input/MeshLabels_D00.Rds")
head( MeshLabels00 )

dim( MeshLabels00 )
length(unique(MeshLabels00$Subject))
length(unique(MeshLabels00$Property))
length(unique(MeshLabels00$Object))

#Check
library( magrittr )

####################################################
#Extract IDs
####################################################
#一時的に小文字に変換してマッティング
MeshLabels01 <- MeshLabels00[c(tolower(MeshLabels00$Object) %in% tolower(words02$Lab00)),]

head(MeshLabels01)
dim(MeshLabels01)
length(unique(MeshLabels01$Subject))
length(unique(MeshLabels01$Property))
unique(MeshLabels01$Property)
length(unique(MeshLabels01$Object))

LabList00 <- unique(MeshLabels01$Subject)

head(LabList00)
saveRDS(LabList00, "./01_Mesh_Out/LabList00.Rds")

```

# Check structures of Polymers

```{r echo=TRUE, eval=FALSE}
#修正版の読み込み
rm(list=ls())

#mesh2021_Label_en_df_RR.Rds
MeshLabel_2021df <- readRDS("./00_Mesh_Input/mesh2021_Label_en_df_RR.Rds")

head(MeshLabel_2021df); dim(MeshLabel_2021df)
table(MeshLabel_2021df$OtherInfo == "BLANK")
table(MeshLabel_2021df$Property)
table(MeshLabel_2021df$SubInfo)

#mesh2021_others_df_RR.Rds
MeshOthers_2021df <- readRDS("./00_Mesh_Input/Mesh_othersR.Rds")

head(MeshOthers_2021df); dim(MeshOthers_2021df)
table(MeshOthers_2021df$OtherInfo == "BLANK")
table(MeshOthers_2021df$Property)
table(MeshOthers_2021df$SubInfo)
table(MeshOthers_2021df$ObjInfo)

##############################################
#Trial 01
##############################################
txt <- "Polymers"
a1 <- MeshLabel_2021df[MeshLabel_2021df$Object == txt,]

a1
#              Subject   Property   Object OtherInfo    SubInfo
#1242522  mesh:D011108 rdfs:label Polymers       @en IDs:mesh:D
#1906322 mesh:M0017208 rdfs:label Polymers       @en IDs:mesh:M
a2 <- a1$Subject
a2

Dat <- c(); x <- 1; Query <- a2
repeat{
print(x)
b1 <- MeshOthers_2021df[MeshOthers_2021df$Subject %in% Query,]
if(dim(b1)[1] == 0){break}
Dat <- rbind(Dat, b1)
Query <- b1$Object
x <- x + 1
if(x == 100){break}
}

x <- 1; Query <- a2
repeat{
print(x)
b2 <- MeshOthers_2021df[MeshOthers_2021df$Object %in% Query,]
if(dim(b2)[1] == 0){break}
Dat <- rbind(Dat, b2)
Query <- b2$Subject
x <- x + 1
if(x == 100){break}
}

head(Dat); dim(Dat)
rownames(Dat) <- 1:nrow(Dat)
colnames(Dat) <- c("subject", "property", "parentClass", "OtherInfo", "SubInfo", "ObjInfo")
Dat$triple <- paste0(Dat$subject, ".", Dat$property, ".", Dat$parentClass)
Dat <- Dat[as.numeric(rownames(unique(Dat["triple"]))),]
Dat <- Dat[,-ncol(Dat)]
head(Dat); dim(Dat)
length(unique(c(Dat$subject, Dat$parentClass)))

#Add labels
library(agGraphSearch)
Dat00 <- MergeMeshData(Data=Dat, Labels=MeshLabel_2021df)
FileName <- paste0("agVisNetwork_polymers_", format(Sys.time(), "%y%m%d-%H%M%S"),".html")

head(Dat00); dim(Dat00); table(Dat00$property)
table(Dat00$property)

if(F){
#All: English
agVisNetwork(Graph=Dat00,
             Selected=NULL, 
             Browse=TRUE, 
             Output=TRUE,
             FilePath=FileName)
}

########################################################################
#Jpn
########################################################################
head(Dat)
DatJpn <- Dat00

dim(DatJpn)
DatJpn$triple <- paste0(DatJpn$subject, ".", DatJpn$property, ".", DatJpn$parentClass)
rownames(DatJpn) <- 1:nrow(DatJpn)
DatJpn00 <- DatJpn[as.numeric(rownames(unique(DatJpn["triple"]))),]
DatJpn00 <- DatJpn00[,-ncol(DatJpn00)]
dim(DatJpn00)

DatJpn <- DatJpn00
table(DatJpn$property)
dim(DatJpn)
length(unique(c(DatJpn$subject, DatJpn$parentClass)))
length(unique(c(DatJpn$subjectLabel, DatJpn$parentClassLabel)))

DatJpn02 <- Label2Jpn(Data=DatJpn, Auth_Key="43725ffd-d3d3-a301-c92d-8d7e2070f71c:fx")
saveRDS(DatJpn02, "./02_Mesh_Out/DatJpn02.Rds")
FileName <- paste0("agVisNetwork_polymers_Jpn_", format(Sys.time(), "%y%m%d-%H%M%S"),".html")

DatJpn03 <- DatJpn02
DatJpn03 <- DatJpn03[DatJpn03$property != "meshv:preferredConcept",]
#DatJpn03 <- DatJpn03[DatJpn03$property != "meshv:preferredConceptR",]
head(DatJpn03); dim(DatJpn03)

#All
agVisNetwork(Graph=DatJpn03,
             Selected=NULL, 
             Browse=TRUE, 
             Output=TRUE,
             FilePath=FileName)

```

# Extract the upper classes

```{r echo=TRUE, eval=FALSE}
rm(list=ls())

if(F){
.rs.restartR()

proxy_url = "http://wwwproxy.osakac.ac.jp:8080"
Sys.setenv("http_proxy" = proxy_url)
Sys.setenv("https_proxy" = proxy_url)
Sys.setenv("ftp_proxy" = proxy_url)

#remove.packages("agGraphSearch")
devtools::install_github( "kumeS/agGraphSearch", force = T)
library(agGraphSearch)
}

#Read data
LabList00 <- readRDS("./01_Mesh_Out/LabList00.Rds")
head(LabList00); length(LabList00)
LabList00

MeshOthers_df <- readRDS("./00_Mesh_Input/mesh2021_others_df_RR.Rds")
head(MeshOthers_df); dim(MeshOthers_df)

#"meshv:broaderDescriptor", and "meshv:reverseConcept"
table(MeshOthers_df$Property)
(names(table(MeshOthers_df$Property)) -> a)[grepl("meshv:broaderDescriptor", a)]
(names(table(MeshOthers_df$Property)) -> a)[grepl("meshv:reverseConcept", a)]

#The upper graph
#broader <- c("meshv:broaderConcept", "meshv:broaderDescriptor", "meshv:broaderQualifier")
broader <- c("meshv:broaderDescriptor", "meshv:reverseConcept")
MeshOthers_broader <- MeshOthers_df[c(MeshOthers_df$Property %in% broader),]

head(MeshOthers_broader); dim(MeshOthers_broader)
table(MeshOthers_broader$Property)
unique(MeshOthers_broader$SubInfo)
unique(MeshOthers_broader$ObjInfo)

MeshLabels00 <- readRDS("./00_Mesh_Input/MeshLabels_D00.Rds")
MeshLabels01 <- MeshLabels00[,c(1,3)]
head(MeshLabels01)

#Perform All
library( agGraphSearch )
Dat <- extractUpperConcepts4Mesh(Lab_List=LabList00,
                                 Data=MeshOthers_broader,
                                 Labels=MeshLabels01,
                                 broaderProperty=broader)

head(Dat)
saveRDS(Dat, "./02_Mesh_Out/Dat.Rds")

# Visualize the relation network
FileName <- paste0("agVisNetwork_", format(Sys.time(), "%y%m%d-%H%M%S"),".html")
#All
agVisNetwork(Graph=Dat,
             Selected=NULL, 
             Browse=FALSE, 
             Output=TRUE,
             FilePath=paste1("Mesh2021_"))

```

# Visualize the relation network: Translate the node names to the Japanese names

```{r echo=TRUE, eval=FALSE}
#2021 + Jpn
Dat <- readRDS("./02_Mesh_Out/Dat.Rds")
Dat01 <- Dat[grepl("mesh[:]", Dat$subject),]
head(Dat01)

words <- Dat01
#table(grepl("[,][ ]", words$subjectLabel))
#table(grepl("[,][ ]", words$parentClassLabel))
#words$subjectLabel[grepl("[,][ ]", words$subjectLabel)]
#words$parentClassLabel[grepl("[,][ ]", words$parentClassLabel)]

words <- Label2Jpn(words, Auth_Key="43725ffd-d3d3-a301-c92d-8d7e2070f71c:fx")

Dat02 <- words
head(Dat02)

if(!dir.exists("02_Mesh_Out")){dir.create("02_Mesh_Out")}
saveRDS(Dat02, "./02_Mesh_Out/Dat02_UpperClass.Rds")
readr::write_excel_csv(Dat02, file="./02_Mesh_Out/Dat02_UpperClass.csv", col_names = T, append=F)

#node
length(unique(c(Dat02$subject, Dat02$parentClass)))

#edge
length(unique(paste0(Dat02$subject, ".", Dat02$parentClass)))

#2021
agVisNetwork(Graph=Dat02,
             Selected=NULL, 
             Browse=FALSE, 
             Output=TRUE,
             FilePath=paste1("Mesh2021JPN"))

```

# Run individually

```{r echo=TRUE, eval=FALSE}

rm(list=ls())

LabList00 <- readRDS("./01_Mesh_Out/LabList00.Rds")
head(LabList00)
length(LabList00)
LabList00

MeshOthers_df <- readRDS("./00_Mesh_Input/mesh2021_others_df_R.Rds")
head(MeshOthers_df)
dim(MeshOthers_df)

MeshOthers_df[MeshOthers_df$Subject == "mesh:D002623",]
MeshOthers_df[MeshOthers_df$Subject == "mesh:M0526832",]

#"meshv:broaderConcept", "meshv:broaderDescriptor", and "meshv:broaderQualifier" 
table(MeshOthers_df$Property)
table(MeshOthers_df$Property, MeshOthers_df$SubInfo)
head(MeshOthers_df)
table(MeshOthers_df[as.numeric(rownames(unique(MeshOthers_df["Subject"]))),]$SubInfo)

(names(table(MeshOthers_df$Property)) -> a)[grepl("broader", a)]
(names(table(MeshOthers_df$Property)) -> a)[grepl("narrower", a)]

#The upper graph
#broader <- c("meshv:broaderConcept", "meshv:broaderDescriptor", "meshv:broaderQualifier")
broader <- c("meshv:broaderDescriptor")
MeshOthers_broader <- MeshOthers_df[c(MeshOthers_df$Property %in% broader),]

broader <- c("meshv:broaderConcept")
MeshOthers_broader <- MeshOthers_df[c(MeshOthers_df$Property %in% broader),]
head(MeshOthers_broader)

dim(MeshOthers_broader)
head(MeshOthers_broader)
table(MeshOthers_broader$Property)
unique(MeshOthers_broader$SubInfo)
unique(MeshOthers_broader$ObjInfo)
#(names(table(MeshOthers_broader$Subject)) -> a)[grepl("D", a)]

#Perform each
library( agGraphSearch )
Dat <- c()

for(n in 1:length(LabList00)){
#n <- 2
print(LabList00[n])
Dat[[n]] <- extractUpperConcepts4Mesh(Lab_List=LabList00[n],
                                 Data=MeshOthers_broader,
                                 broaderProperty=broader)
names(Dat)[n] <- LabList00[n]
rownames(Dat[[n]]) <- 1:nrow(Dat[[n]])
colnames(Dat[[n]]) <- c("subject", "property", "parentClass", "OtherInfo")
}

head(Dat)
length(Dat)

#save
saveRDS(Dat,
        file = "./02_Mesh_Out/Individual_upGraph.Rds", compress = TRUE)

Dat <- readRDS("./02_Mesh_Out/Individual_upGraph.Rds")
#集計
##Graph data without the uplicates
#Number of entities
DatDF <- ListDF2DF(Dat)
head(DatDF)

(E01 <- length(unique(c(DatDF$subject, DatDF$parentClass))))
#Number of labels
(E02 <- length(unique(c(DatDF$subjectLabel, DatDF$parentClassLabel))))
#Number of Triples
(E03 <- length(unique(DatDF$triples)))

#Gathering the parent concepts
upEntity <- unlist(purrr::map(Dat, function(x){unique(x$parentClass)}), use.names = F)
head(upEntity)

#calculate the frequency of common entities
Count_upEntity_DF <- countCommonEntities(upEntity)
head(Count_upEntity_DF)

#Count and view table
agTableDT(Count_upEntity_DF, Transpose = F, AutoWidth = FALSE)

#Count Freq
table(Count_upEntity_DF$Freq)

#extarct parentClass & parentClassLabel from the merged dataset
Dat02 <- readRDS("./02_Mesh_Out/Dat02.Rds")
head(Dat02)
Dat02P <- data.frame(Dat02[,c(colnames(Dat02) == "parentClass" | 
              colnames(Dat02) == "parentClassLabel")])
head(Dat02P)

#Delete the deplicates
Dat02P0 <- Exclude_duplicates(Dat02P, 1)
head(Dat02P0)
dim(Dat); dim(Dat02P0)

#define the common upper-level entities
dim(Count_upEntity_DF); dim(Dat02P0)
head(Count_upEntity_DF); head(Dat02P0)
Count_upEntity_DF2 <- Cutoff_FreqNum(input1=Count_upEntity_DF, 
                                     input2=Dat02P0, 
                                     By="parentClass", 
                                     Sort="Freq", 
                                     FreqNum=2)

#check the results
head(Count_upEntity_DF2, n=10)
table(Count_upEntity_DF2$Freq)

#Translate to Japanese
Count_upEntity_DF2$parentClassLabelJpn <- Count_upEntity_DF2$parentClassLabel
words <- Count_upEntity_DF2
head(words)

for(n in 1:nrow(words)){
#n <- 1
#parentClassLabelJpn
print(n)
if(grepl("[,][ ]", words$parentClassLabelJpn[n]) & !grepl("[,][ ]and", words$parentClassLabelJpn[n])){
 aa <- strsplit(words$parentClassLabelJpn[n], split = ", ")[[1]]
 aa1 <- paste(aa[length(aa):1], collapse = " ")
 words$parentClassLabelJpn[n] <- DeePL(aa1, Auth_Key="43725ffd-d3d3-a301-c92d-8d7e2070f71c:fx")
}else{
 aa <-  words$parentClassLabelJpn[n]
 words$parentClassLabelJpn[n] <- DeePL(aa, Auth_Key="43725ffd-d3d3-a301-c92d-8d7e2070f71c:fx")
} 
}

Count_upEntity_DF3 <- words
head(Count_upEntity_DF3)

#save
saveRDS(Count_upEntity_DF3,
        file = "./02_Mesh_Out/Count_upEntity_DF3.Rds", compress = TRUE)
readr::write_excel_csv(Count_upEntity_DF3,
                       file="./02_Mesh_Out/Count_upEntity_DF3.csv")
#Count_upEntity_DF3 <- readRDS(file = "./02_Mesh_Out/Count_upEntity_DF3.Rds")

head(Count_upEntity_DF3)

```

# Calculation of the number of expansion steps

```{r echo=TRUE, eval=FALSE}
if(!dir.exists("03_Mesh_Out")){dir.create("03_Mesh_Out")}

rm(list=ls())

#Individual graphs
eachGraph <- readRDS("./02_Mesh_Out/Individual_upGraph.Rds")
head(eachGraph[[1]])
sapply(eachGraph, dim)

#Label information
Dat02 <- readRDS("./02_Mesh_Out/Dat02.Rds")
head(Dat02)

words <- Dat02
for(n in 1:nrow(words)){
#n <- 1
#subjectLabel
if(grepl("[,][ ]", words$subjectLabel[n]) & !grepl("[,][ ]and", words$subjectLabel[n])){
 aa <- strsplit(words$subjectLabel[n], split = ", ")[[1]]
 words$subjectLabel[n] <- paste(aa[length(aa):1], collapse = " ")
}else{
 aa <-  words$subjectLabel[n]
 words$subjectLabel[n] <- aa
}
#parentClassLabel
if(grepl("[,][ ]", words$parentClassLabel[n]) & !grepl("[,][ ]and", words$parentClassLabel[n])){
 aa <- strsplit(words$parentClassLabel[n], split = ", ")[[1]]
 words$parentClassLabel[n] <- paste(aa[length(aa):1], collapse = " ")
}else{
 aa <-  words$parentClassLabel[n]
 words$parentClassLabel[n] <- aa
} 
}
Dat02  <- words

for(n in 1:length(eachGraph)){
#n <- 1
a <- Dat02[Dat02$subject %in% eachGraph[[n]]$subject,c(1,5)]
a1 <- merge(eachGraph[[n]], a, by="subject", sort=F)
a2 <- Dat02[Dat02$parentClass %in% eachGraph[[n]]$parentClass,c(3,6)]
a3 <- merge(a1, a2, by="parentClass", sort=F)
a4 <- a3[,c("subject", "property", "parentClass", "OtherInfo",
            "subjectLabel", "parentClassLabel")]
a4$triple <- paste0(a4$subject, ".", a4$parentClass)
a5 <- a4[as.numeric(rownames(unique(a4["triple"]))),]
rownames(a5) <- 1:nrow(a5)
eachGraph[[n]] <- a5
}

#Search entities
list1a <- readRDS("./01_Mesh_Out/LabList00.Rds")
head(list1a)

#Common entities
list2a <- readRDS("./02_Mesh_Out/Count_upEntity_DF3.Rds")
head(list2a)
dim(list2a)
list2b <- unique(list2a$parentClass)

#Inclusion of list1a and list2b
table(list1a %in% list2b)
table(list2b %in% list1a)

```

# 下位探索のアルゴリズムの修正

段数ごとに、一気に下位概念を取得する。
だいぶ早くなる。


# Descriptor-Qualifier Pairs 

mesh:D000001Q000008 rdfs:label  Calcimycin/administration & dosage
↓↓↓↓↓
Calcimycin (administration & dosage)
に変更する






# 高分子辞典索引






