---
title: "Workflow to use agGraphSearch and Mesh RDF: WF-001"
shorttitle: "WF-001: load the search seeds"
author:
  - name: Satoshi Kume
date: "`r Sys.Date()`"
graphics: no
package: agGraphSearch, knitr, SPARQL
output:
  BiocStyle::html_document:
  toc_float: true
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{agGraphSearch}
  %\VignetteIndexEntry{Workflow to use agGraphSearch: WF-001}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r style, echo = FALSE, results = 'asis', message=FALSE}
BiocStyle::markdown()
```

**Last modified:** `r file.info("agGraphSearch-WF-001.Rmd")$mtime`<br />
**Compiled**: `r date()`

# Getting started

Once `r Rpackage("agGraphSearch")` is installed, it can be loaded by the following command.

```{r library, message=FALSE}
library("agGraphSearch")
```

This workflow can be skipped. The next workflow should be started. 

# Read the csv files from extdata

```{r echo=TRUE, eval=FALSE}
f <- system.file("extdata", "PoLyInfo_metadata_En_v01.csv", package="agGraphSearch")
words <- data.frame(readr::read_csv(f, col_names = TRUE))

```

# Check the data

```{r echo=TRUE, eval=FALSE}
head(words)
dim(words)

```

# Delete blanks

```{r echo=TRUE, eval=FALSE}
words.c <- unique(as.character(unlist(words)[unlist(words) != ""]))

#remove NA
words.c <- words.c[!is.na(words.c)]

#cehck NAs
table(is.na(words.c))

```

# combind the search seeds and delete the deplicates

```{r echo=TRUE, eval=FALSE}
agTableFM(data.frame(words.c))

```

# save file

```{r echo=TRUE, eval=FALSE}
#create a new folder
if(!dir.exists("00_Mesh_Input")){dir.create("00_Mesh_Input")}

#save to csv
readr::write_excel_csv(data.frame(words.c), file="./00_Mesh_Input/words.c.csv", col_names = F)
```

# Session information {.unnumbered}
```{r sessionInfo, echo=FALSE}
sessionInfo()
```
