---
title: "Workflow to use agGraphSearch and Mesh RDF: WF-002"
shorttitle: "WF-002: match labels to the Mesh data via SPARQL"
author:
  - name: Satoshi Kume
date: "`r Sys.Date()`"
graphics: no
package: agGraphSearch, knitr, SPARQL
output:
  BiocStyle::html_document:
  toc_float: true
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{agGraphSearch}
  %\VignetteIndexEntry{WF-002: match labels to the wikidata via SPARQL}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r style, echo = FALSE, results = 'asis', message=FALSE}
BiocStyle::markdown()
```

**Last modified:** `r file.info("agGraphSearch-WF-002.Rmd")$mtime`<br />
**Compiled**: `r date()`

# Getting started

Once `r Rpackage("agGraphSearch")` is installed, it can be loaded by the following command.

```{r library, message=FALSE}
#rm( list=ls() )
library( agGraphSearch )
library( magrittr )

#Re-build
if(TRUE){
system("rm -rf ./agGraphSearch/NAMESPACE")
roxygen2::roxygenise("./agGraphSearch")
system("cat ./agGraphSearch/NAMESPACE")
remove.packages("agGraphSearch", lib=.libPaths())
.rs.restartR()
}

if(TRUE){
system("R CMD INSTALL agGraphSearch")
Sys.sleep(1)
library(agGraphSearch)
}
```

This workflow can be skipped. The next workflow should be started. 

# Read the csv files

You should split compound words as a pre-processing.

```{r echo=TRUE, eval=FALSE}
words <- data.frame(readr::read_csv("./00_Mesh_Input/words.cR.csv", col_names = F))
words <- unlist(words, use.names = F)
words <- words[!is.na(words)]
```

if the WF-001 is skipped, start with the command as follows.

```{r echo=TRUE, eval=FALSE}
f <- system.file("extdata", "Mesh_words.cR.csv", package="agGraphSearch")
words <- data.frame(readr::read_csv(f, col_names = F))

```

# check the data

```{r echo=TRUE, eval=FALSE}
head(words)
dim(words)

#unique number
length(unique(words))

#table
head(words)
#agTableKB(words, Head = F, Align = 3)
```

# Downloads the Mesh files from the repository (Google Drive).

```{r, echo=TRUE, eval=FALSE}
#save
if(!dir.exists("00_Mesh_Input")){dir.create("00_Mesh_Input")}

#proxy <- 'export https_proxy="http://wwwproxy.osakac.ac.jp:8080"; export ftp_proxy="http://wwwproxy.osakac.ac.jp:8080"'
scr <- system.file("script", "gdrive_download.sh", package="agGraphSearch")

#mesh219_2020_2021_others2_df.Rds
File_ID <- "1Pf28EA4mRc59JeFi4VREcBuS-AcTqxQm"
File_Name <- "mesh219_2020_2021_others2_df.Rds"
system(paste0(proxy, "; source ", scr, "; gdrive_download ", File_ID, " ./00_Mesh_Input/", File_Name, " "))

#mesh219_2020_2021_Label_en_df.Rds
File_ID <- "1afoPL1xEJPxW7k72nD3ZWXEGMq94JMno"
File_Name <- "mesh219_2020_2021_Label_en_df.Rds"
system(paste0(proxy, "; source ", scr, "; gdrive_download '", File_ID, "' ./00_Mesh_Input/", File_Name, " "))

```

# Import Mesh data (2019-2021)

```{r, echo=TRUE, eval=TRUE}
MeshLabels <- readRDS("./00_Mesh_Input/mesh219_2020_2021_Label_en_df.Rds")
head(MeshLabels)

#check property
table(MeshLabels$Property)

MeshOthers <- readRDS("./00_Mesh_Input/mesh219_2020_2021_others_df.Rds")
head(MeshOthers)

#check property
table(MeshOthers$Property)

```

# remove other data

```{r}
#head(MeshLabels[!grepl("^A[0-9][0-9]|^B[0-9][0-9]", MeshLabels$Object),])
MeshLabels00 <- MeshLabels
MeshLabels00 <- MeshLabels00[!grepl("^[A-Z][0-9][0-9]|^[[]OBSOLETE", MeshLabels00$Object),]

#property
MeshLabels00 <- MeshLabels00[!grepl("meshv:scopeNote|meshv:thesaurusID|meshv:lexicalTag|meshv:lastActiveYear", MeshLabels00$Property),]
MeshLabels00 <- MeshLabels00[!grepl("meshv:historyNote|meshv:publicMeSHNote|meshv:previousIndexing|meshv:annotation|meshv:source|meshv:note|meshv:sortVersion|meshv:abbreviation|meshv:onlineNote|meshv:considerAlso|meshv:entryVersion", MeshLabels00$Property),]

#Order
MeshLabels00 <- MeshLabels00[order(MeshLabels00$Property),]

#check property
table(MeshLabels00$Property)

head(MeshLabels00)

#Extract D terms
table(grepl("[:]D", MeshLabels00$Subject))
head(MeshLabels00[grepl("[:]D", MeshLabels00$Subject),])
MeshLabels_D00 <- MeshLabels00[grepl("[:]D", MeshLabels00$Subject),]
#head(MeshLabels_D00)

#head(MeshLabels00)
#readr::write_csv(MeshLabels00, file="./00_Mesh_Input/MeshLabels00.csv", col_names = F, append=F)
saveRDS(MeshLabels00, "./00_Mesh_Input/MeshLabels00.Rds")
#readr::write_csv(MeshLabels_D00, file="./00_Mesh_Input/MeshLabels_D00.csv", col_names = F, append=F)
saveRDS(MeshLabels_D00, "./00_Mesh_Input/MeshLabels_D00.Rds")

```

# Linking of input words to the Mesh words

Input words in English are 428.

```{r echo=TRUE, eval=FALSE}
##restart
rm( list=ls() )
MeshLabels00 <- readRDS("./00_Mesh_Input/MeshLabels_D00.Rds")
head( MeshLabels00, n=10 )
dim(MeshLabels00)
length(unique(MeshLabels00$Object))

words <- unlist(data.frame(readr::read_csv("./00_Mesh_Input/words.cR.csv", col_names = F)), use.names = F)
words <- unlist(words, use.names = F)
words <- words[!is.na(words)]
words <- words[words != ""]
words <- unique(words)
head(words)
length(unique(words))

#小文字変換
head(MeshLabels00)
MeshLabels01 <- unique(tolower(MeshLabels00$Object))
head(MeshLabels01)
length(MeshLabels01)

head(words)
words00 <- unique(unlist(words)); words00 <- words00[!is.na(words00)]
words01 <- unique(tolower(words00))
head(words01)

#文字列距離実行
library( agGraphSearch )
Dat <- ComputeDistance(InputTerms=words01,
                       RDFterms=MeshLabels01,
                       q=2, nthread=4, TopWords=3)
  
head(Dat)
table(Dat$PerfectMatch > 0)
table(Dat$PartialMatch > 0)
table(Dat$cosine1 > 0)

if(!dir.exists("01_Mesh_Out")){dir.create("01_Mesh_Out")}
readr::write_csv(Dat, file="./01_Mesh_Out/DistanceDat_Out.csv", col_names = T, append=F)
saveRDS(Dat, "./01_Mesh_Out/DistanceDat_Out.Rds")

```

#O/Xをつけて、閾値を決める
#コサインが良いかも

```{r}
#options(digits=5) 
Thres <- data.frame(readr::read_csv("./01_Mesh_Out/Dat210610_v02.csv", col_names = T))

head(Thres)
tail(Thres)
Thres$Check0 <- NA
Thres$Check0[Thres$Check == 0] <- "X"
Thres$Check0[Thres$Check == 1] <- "O"
Thres$cosine3 <- as.integer(Thres$cosine3*10000)/10000

#Create the plot
library(ggplot2)
ggplot(Thres, aes(x = Check0, y = cosine3)) +
  geom_boxplot(outlier.colour = NA, width = .4) +
  geom_dotplot(binaxis = "y", binwidth = .005, stackdir = "center", fill = NA)

summary(Thres$cosine3[Thres$Check == 0])
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.0762  0.2417  0.3164  0.3138  0.3814  0.6087 
#厳し目基準なら、Thres = 0.075
head(Thres)
words02 <- Thres[Thres$cosine3 < 0.075, ]
head(words02)
dim(words02)
rownames(words02) <- 1:nrow(words02)

saveRDS(words02, "./01_Mesh_Out/words02.Rds")
```

# Translate English to Japanese

```{r}
rm(list=ls())
words02 <- readRDS("./01_Mesh_Out/words02.Rds")
head(words02)

words02$Lab00 <- NA
head(words02)

#ラベルを逆にする
head(words02)
words02$Lab00 <- tolower(words02$cosine2)
words02$Lab01 <- NA
head(words02)

table(grepl("[,][ ]", words02$Lab00))
for(n in 1:length(words02$Lab00)){
#n <- 5
if(grepl("[,][ ]", words02$Lab00[n])){
 aa <- strsplit(words02$Lab00[n], split = ", ")[[1]]
 words02$Lab01[n] <- paste(aa[length(aa):1], collapse = " ")
}else{
 aa <-  words02$Lab00[n]
 words02$Lab01[n] <- aa
}}
table(grepl("[,]", words02$Lab01))

words02$Jpn <- NA
head(words02, n=10)

#Translate to Jpn
if(T){
proxy_url = "http://wwwproxy.osakac.ac.jp:8080"
Sys.setenv("http_proxy" = proxy_url)
Sys.setenv("https_proxy" = proxy_url)
Sys.setenv("ftp_proxy" = proxy_url)
source("https://gist.githubusercontent.com/kumeS/26a7a602070365595a0b552e201079d5/raw/8c6e73a85dca7fddb08a360117c2e9e1501c3aad/DeePL.R")  
#Ex.
DeePL(Sentence="Hello", EN2JA=TRUE, Auth_Key="43725ffd-d3d3-a301-c92d-8d7e2070f71c:fx")
}

#Run
head(words02)
for(n in 1:length(words02$Lab01)){
#n <- 1
print(n)
Result <- DeePL(Sentence=words02$Lab01[n], Auth_Key="43725ffd-d3d3-a301-c92d-8d7e2070f71c:fx")
words02$Jpn[n] <- Result
}

head(words02)
tail(words02)

saveRDS(words02, "./01_Mesh_Out/words02_Jpn.Rds")
readr::write_excel_csv(words02, file="./01_Mesh_Out/words02_Jpn.csv", col_names = T, append=F)

```

# Linking to the Mesh

```{r echo=TRUE, eval=FALSE}
rm(list=ls())

#Match List
words02 <- readRDS("./01_Mesh_Out/words02_Jpn.Rds")
head(words02)
table(words02$cosine2 == words02$Lab00)
table(words02$cosine2 == words02$Lab01)

#Mesh D term List
MeshLabels00 <- readRDS("./00_Mesh_Input/MeshLabels_D00.Rds")
head( MeshLabels00 )

dim( MeshLabels00 )
length(unique(MeshLabels00$Subject))
length(unique(MeshLabels00$Property))
length(unique(MeshLabels00$Object))

#Check
library( magrittr )
#D01 <- MeshLabels00[grepl("mesh:D", MeshLabels00$Subject),]
#D02 <- MeshLabels00[grepl("mesh2019:D", MeshLabels00$Subject),]
#D03 <- MeshLabels00[grepl("mesh2020:D", MeshLabels00$Subject),]
#D04 <- MeshLabels00[grepl("mesh2021:D", MeshLabels00$Subject),]
#MeshLabels_D00 <- D01 %>% rbind(D02) %>% rbind(D03) %>% rbind(D04)
#head(MeshLabels_D00)

##########################
#Extract IDs
##########################
#一時的に小文字に変換してマッティング
MeshLabels01 <- MeshLabels00[c(tolower(MeshLabels00$Object) %in% tolower(words02$Lab00)),]

head(MeshLabels01)
dim(MeshLabels01)
length(unique(MeshLabels01$Subject))
length(unique(MeshLabels01$Property))
unique(MeshLabels01$Property)
length(unique(MeshLabels01$Object))

LabList00 <- unique(MeshLabels01$Subject)

head(LabList00)
saveRDS(LabList00, "./01_Mesh_Out/LabList00.Rds")

```

# Extract the upper classes

```{r}
rm(list=ls())
LabList00 <- readRDS("./01_Mesh_Out/LabList00.Rds")
head(LabList00)

MeshOthers_df <- readRDS("./00_Mesh_Input/mesh219_2020_2021_others_df.Rds")
head(MeshOthers_df)

#"meshv:broaderConcept", "meshv:broaderDescriptor", and "meshv:broaderQualifier" 
table(MeshOthers_df$Property)
(names(table(MeshOthers_df$Property)) -> a)[grepl("broader", a)]
(names(table(MeshOthers_df$Property)) -> a)[grepl("narrower", a)]

#The upper graph
broader <- c("meshv:broaderConcept", "meshv:broaderDescriptor", "meshv:broaderQualifier")
MeshOthers_broader <- MeshOthers_df[c(MeshOthers_df$Property %in% broader),]

dim(MeshOthers_broader)
head(MeshOthers_broader)
#(names(table(MeshOthers_broader$Subject)) -> a)[grepl("D", a)]

#Perform All
Dat <- extractUpperConcepts4Mesh(Lab_List=LabList00,
                                 Data=MeshOthers_broader,
                                 broaderProperty=broader)
  
head(Dat)
dim(Dat)
length(unique(Dat$Subject))
length(unique(Dat$Property))
unique(Dat$Property)
length(unique(Dat$Object))


```



# Convert them to rdfs:label.


```{r echo=TRUE, eval=FALSE}
Lab01 <- fm3$LABEL
agTableKB(data.frame(Lab01))

#Check Query
CkeckQuery_agWD_Alt_Wikidata(unlist(Lab01)[1])
#CkeckQuery_agWD_Alt_Wikidata(unlist(Lab01)[136])

#run SPARQL
furrr::plan(multisession(workers = 2))
Lab01_res <- furrr::future_map(unlist(Lab01), agWD_Alt_Wikidata, .progress = TRUE)

#check them
Lab01_res[[1]]
Lab01_res[[136]]
Lab01_res[[79]]
Lab01_res[[119]]

#check NA
agGraphSearch:::checkNA_af_agWD_Alt(Lab01_res)

#check nrow
agGraphSearch:::checkNrow_af_agWD_Alt(Lab01_res)

#gathering IDs
Lab02 <- ListDF2DF(Lab01_res, NA.omit=TRUE)
dim(Lab02)

#delete deplicates
QID <- unique(unlist(Lab02))
length(QID)

#save
if(!dir.exists("01_Out")){dir.create("01_Out")}
saveRDS(QID, file = "./01_Out/R01_QID.Rdata", compress = TRUE)

```

# Assigning Label information to QID

```{r echo=TRUE, eval=FALSE}
#view query
CkeckQuery_agQIDtoLabel_Wikidata(QID[1])

#do SPARQL
furrr::plan(multisession(workers = 2))
Label00 <- furrr::future_map(unlist(QID), agQIDtoLabel_Wikidata, .progress = TRUE)

#check nrow
checkNrow_af_agQIDtoLabel(Label00)
#checkNrow_af_agWD_Alt(Label00)

#convert list to data.frame
Label01 <- ListDF2DF(Label00)

#check it
head(Label01)
dim(Label01)
table(is.na(Label01))
table(is.na(Label01$entityNamej))
table(is.na(Label01$entityNamee))

#rows wit NA
Label01[is.na(Label01$entityNamee),]

#save
#if(!dir.exists("01_Out")){dir.create("01_Out")}
saveRDS(Label01, file = "./01_Out/R01_QID_rdfsLabel.Rdata", compress = TRUE)

```

# Retry SPARQL

```{r echo=TRUE, eval=FALSE}
#Data load 
Labs <- readRDS("./01_Out/R01_QID_rdfsLabel.Rdata")
head(Labs)
dim(Labs)

#View query
CkeckQuery_agCount_ID_Num_Wikidata_QID_P279_P31(Labs[1,1])

#Try SPARQL
furrr::plan(multisession(workers = 4))
#furrr::plan()

m_2 <- furrr::future_map(unlist(Labs$QID), agCount_ID_Num_Wikidata_QID_P279_P31, .progress = TRUE)

#convert list to data.frame
fm_2 <- ListDF2DF(m_2)

#check it
head(fm_2)
dim(fm_2)
colnames(fm_2)

#All
table(fm_2$Hit_All)
table(fm_2$Hit_All > 0)
table(fm_2$Hit_All_Parent > 0)
table(fm_2$Hit_All_Child > 0)


# check labels corresponding to ID
head(Labs)
dim(Labs)

Labs_B1 <- furrr::future_map(unlist(Labs$entityNamej), 
                             agCount_Label_Num_Wikidata_P279_P31, 
                             .progress = TRUE)
head(Labs_B1)

#check nrow
checkNrowVec_af_agQIDtoLabel(Labs_B1)
checkNrow_af_agQIDtoLabel(Labs_B1)

#check results
checkHitLabel_af_agCount_Label_Num(Labs_B1)
checkHitALL_af_agCount_Label_Num(Labs_B1)

#View the results
Labs_B2 <- ListDF2DF(Labs_B1)

agTableDT(Labs_B2, Width = "100px")

```





# Session information {.unnumbered}
```{r sessionInfo, echo=FALSE}
sessionInfo()
```
