---
title: "A workflow to use agGraphSearch and Wikidata with PolyInfo terms"
author:
  - name: Satoshi Kume
date: "`r Sys.Date()`"
graphics: no
package: agGraphSearch, knitr, SPARQL
output:
  BiocStyle::html_document:
  toc_float: true
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{agGraphSearch}
  %\VignetteIndexEntry{A workflow to use agGraphSearch and Wikidata with PolyInfo terms}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r style, echo=FALSE, message=FALSE, results='asis'}
BiocStyle::markdown()
```

**Last modified:** `r file.info("agGraphSearch-Wikidata-WF.Rmd")$mtime`<br />
**Compiled**: `r Sys.time()`

# Getting started

## Requirements

- macOSX 10.15 with 3.6GHz Intel Core i9 or similar specs
- RAM: 32GB
- Available storage: > 20GB

## Installation of agGraphSearch

Once `r Rpackage("agGraphSearch")` is installed, it can be loaded by the following command.

```{r library, echo=TRUE, eval=FALSE}
#Clean the enbironment
rm(list=ls())

#Install
install.packages("devtools")
devtools::install_github( "kumeS/agGraphSearch", force = TRUE)
library(agGraphSearch)
library(magrittr)
```

# Read the search terms obtained from PolyInfo databse.

In this tutorial, the Japanese terms obtained from PolyInfo Database will be used and the number of terms is total 510.

```{r echo=TRUE, eval=FALSE}
#Read Japanese terms
fp <- system.file("extdata", "PoLyInfo_terms_Jpn_v01.csv", package="agGraphSearch")
wordsj <- data.frame(readr::read_csv(fp, col_names = T, show_col_types = FALSE))

#Processing
words <- unique(unlist(wordsj, use.names = F))
words <- words[!is.na(words)]

#show the head
head(words)
length(words)
```

I also showed how to use the English terms obtained from PolyInfo Database (total 463 terms).

```{r echo=TRUE, eval=FALSE}
if(F){
#Read English terms
fp <- system.file("extdata", "PoLyInfo_terms_En_v01.csv", package="agGraphSearch")
wordse <- data.frame(readr::read_csv(fp, col_names = T, show_col_types = FALSE))

#Processing
words <- unique(unlist(wordse, use.names = F))
words <- words[!is.na(words)]

#show the head
head(words)
}
```

# Wikidata datasets (25th Sep 2021)

## Download the Wikidata datasets from Google Drive.

Download below files and save on the local environment.

```{r echo=TRUE, eval=FALSE}
## Download Class-related hierarchy dataset (Common to English and Japanese)
browseURL("https://drive.google.com/file/d/1YcUVgCShQOOSY0ckv1h-B4eu-4mBHLVz/view?usp=sharing")
# the modified version
browseURL("https://drive.google.com/file/d/1ir4_W0k8hFt7VZF38oA9whXbcHcmE7ZD/view?usp=sharing")

## Download Japanese labels
browseURL("https://drive.google.com/file/d/1NMJYwDjuAujxA6tdpqUwUBtxQxYzGZ8c/view?usp=sharing")

## Download English labels
#TBD

```

Then, I moved the files to your working directory. 
In this time, I manually moved their files to the "04_Wiki_PolyInfo_00" folder in the working directory .

## Import Wikidata datasets

```{r echo=TRUE, eval=FALSE}
#Generate directories
if(!dir.exists("04_Wiki_PolyInfo_01")){dir.create("04_Wiki_PolyInfo_01")}
if(!dir.exists("04_Wiki_PolyInfo_02")){dir.create("04_Wiki_PolyInfo_02")}
if(!dir.exists("04_Wiki_PolyInfo_03")){dir.create("04_Wiki_PolyInfo_03")}
if(!dir.exists("04_Wiki_PolyInfo_04")){dir.create("04_Wiki_PolyInfo_04")}
if(!dir.exists("04_Wiki_PolyInfo_05")){dir.create("04_Wiki_PolyInfo_05")}
if(!dir.exists("04_Wiki_PolyInfo_06")){dir.create("04_Wiki_PolyInfo_06")}
if(!dir.exists("04_Wiki_PolyInfo_XX")){dir.create("04_Wiki_PolyInfo_XX")}

#Do not run
if(F){
#Load the hierarchy dataset
ClassHi <- readRDS("./04_Wiki_PolyInfo_00/Relation_P279_P31_df.Rds")

#Check data
head(ClassHi)
#table(ClassHi$Property)

#Remove loops
table(ClassHi$Subject != ClassHi$Object)
ClassHi <- ClassHi[ClassHi$Subject != ClassHi$Object,]

saveRDS(ClassHi, "./04_Wiki_PolyInfo_00/ClassHiR.Rds")

#Load the label dataset
Labels01 <- readRDS("./04_Wiki_PolyInfo_00/Label_ja_rdfs_df.Rds")
Labels02 <- readRDS("./04_Wiki_PolyInfo_00/Label_ja_Altlabel_df.Rds")

#Bind, extract and check labels
Labels <- rbind(Labels01, Labels02)
head(Labels)
saveRDS(Labels, "./04_Wiki_PolyInfo_00/Label_ja_All_label_df.Rds")  
}

#Load the hierarchy dataset
ClassHi <- readRDS("./04_Wiki_PolyInfo_00/ClassHiR.Rds")

#Load the label dataset
Labels <- readRDS("./04_Wiki_PolyInfo_00/Label_ja_All_label_df.Rds")

```

# Linking of input terms to the wikidata labels

Input are 510 terms in Japanese.

```{r echo=TRUE, eval=FALSE}
#Show data
head(words)
head(Labels)

#Linking to the wikidata entities
LabelsR <- Labels[Labels$Object %in% words,]
LabelsR <- LabelsR[LabelsR$Subject %in% unique(ClassHi$Subject),]

#Check data
dim(LabelsR)
head(LabelsR)

#rename row
rownames(LabelsR) <- 1:nrow(LabelsR)
dim(LabelsR)

#Obtain the subject QID
QID.d <- data.frame(QID=unique(LabelsR$Subject))
```

# Check relations via SPARQL query

This program executes SPARQL with a for-loop.

Input entities are 247.

## excluding the adjacent entity

```{r echo=TRUE, eval=FALSE}
#proxy setting if you need.
#proxy_url = "http://wwwproxy.osakac.ac.jp:8080"
#ProxySet(proxy_url)

#Temp Function for excluding the adjacent entity
Tem00 <- function(Entity_ID0, Object0, Property0="?p", Count0="?p"){
Val00 <- wikiCount_QID_Property_Object(Entity_ID=Entity_ID0, Property=Property0, Object=Object0, Count=Count0)
return(Val00)
}

#set parameters
ExcluQ <- c("Q101352", "Q16521", "Q11424", "Q6256", 
            "Q12308941", "Q11879590", "Q5", "Q5327369", 
            "Q577", "Q4167410", "Q3305213", "Q13406463", 
            "Q35120", "Q3695082", "Q131257", "Q80071", 
            "Q4830453", "Q482994", "Q20202269", "Q2996394")
NumQ <- length(ExcluQ)

#run
for(n in seq_len(NumQ)){
#n <- 1
message(n, ": ", ExcluQ[n])
DatA <- QID.d$QID; DatB <- rep(paste0("wd:", ExcluQ[n]), length(DatA))
a <- furrr::future_map2(unlist(DatA), unlist(DatB), Tem00, .progress = TRUE)
eval(parse(text=paste0("QID.d$", ExcluQ[n], " <- c(unlist(a) > 0)")))

readr::write_excel_csv(QID.d, 
                       paste0(paste0(tempDIR, "/", "Wiki_01_Out"), 
                              "/ExcluQ_", formatC(n, width = 3, flag = "0"), "_", ExcluQ[n], ".csv"), col_names = T)
#show hits
print(eval(parse(text=paste0("QID.d[QID.d$", ExcluQ[n], " == TRUE,c(1, ncol(QID.d))]"))))
#remove hits
QID.d <- QID.d[unlist(a, use.names = F) == 0,]
print(dim(QID.d))
}

#show results
dim(QID.d)
head(QID.d)

```

## excluding the particular property

```{r echo=TRUE, eval=FALSE}
#Temp Function for excluding the particular property
Tem01 <- function(Entity_ID0, Property0, Object0="?o", Count0="?o"){
Val01 <- wikiCount_QID_Property_Object(Entity_ID=Entity_ID0, Property=Property0, Object=Object0, Count=Count0)
return(Val01)
}

#set parameters
ExcluP <- c("P131","P21","P747","P4743","P577")
NumP <- length(ExcluP)

#run
for(n in seq_len(NumP)){
#n <- 1
message(n, ": ", ExcluP[n])
DatA <- QID.d$QID; DatB <- rep(paste0("wdt:", ExcluP[n]), length(DatA))
a <- furrr::future_map2(unlist(DatA), unlist(DatB), Tem01, .progress = TRUE)
eval(parse(text=paste0("QID.d$", ExcluP[n], " <- c(unlist(a) > 0)")))

readr::write_excel_csv(QID.d, 
                       paste0(paste0(tempDIR, "/", "Wiki_01_Out"), 
                              "/ExcluP_", formatC(n, width = 3, flag = "0"), "_", ExcluP[n], ".csv"), col_names = T)
#show hits
print(eval(parse(text=paste0("QID.d[QID.d$", ExcluP[n], " == TRUE,c(1, ncol(QID.d))]"))))
#remove hits
QID.d <- QID.d[unlist(a, use.names = F) == 0,]
print(dim(QID.d))
}

#show results
dim(QID.d)
head(QID.d)

#saveRDS(QID.d, "./QID.d.Rds")
#QID.d <- readRDS("./QID.d.Rds")
```

## post-processing

```{r echo=TRUE, eval=FALSE}
#renames rows
rownames(QID.d) <- 1:nrow(QID.d)
QID.d01 <- QID.d[,-c(2:ncol(QID.d))]

#the number of QID
length(QID.d01)
head(QID.d01)
```

# Seaching upper concepts from the search entities

```{r echo=TRUE, eval=FALSE}
#show labels
SearchEntity <- Labels[Labels$Subject %in% QID.d01 & Labels$Property == "rdfs:label",]
head(SearchEntity); dim(SearchEntity)
#readr::write_excel_csv(SearchEntity, "./04_Wiki_PolyInfo_XX/SearchEntity.csv")

##################################################################
#Upper search up to 30 steps
##################################################################
#set parameters
QID.list <- QID.d01
QID.dat <- NULL

#Run
for(n in 1:length(QID.list)){
#n <- 1
message("No.", n, ": ", QID.list[n])
Dat <- c(); x <- 0; Query <- QID.list[n]

repeat{
x <- x + 1
message("x: ", x)

#Both wdt:P279 and wdt:P31 when x = 1
b1 <- ClassHi[ClassHi$Subject %in% Query,]

#Only wdt:P279 when x >= 2
if(x >= 2){
  b1 <- b1[b1$Property == "wdt:P279",]
}

if(nrow(b1) == 0){
  rownames(Dat) <- 1:nrow(Dat)
  Dat$triple <- paste0(Dat$Subject, ".", Dat$Property, ".", Dat$Object)
  Dat <- Dat[as.numeric(rownames(unique(Dat["triple"]))),-c(ncol(Dat))]
  rownames(Dat) <- 1:nrow(Dat)
  #head(Dat)
  QID.dat[[n]] <- Dat
  names(QID.dat)[n] <- QID.list[n]
  break
  }
Dat <- rbind(Dat, b1)
Query <- b1$Object
if(x == 30){
  rownames(Dat) <- 1:nrow(Dat)
  Dat$triple <- paste0(Dat$Subject, ".", Dat$Property, ".", Dat$Object)
  Dat <- Dat[as.numeric(rownames(unique(Dat["triple"]))),-c(ncol(Dat))]
  rownames(Dat) <- 1:nrow(Dat)
  #head(Dat)
  QID.dat[[n]] <- Dat
  names(QID.dat)[n] <- QID.list[n]
  break
}
}}

#length(QID.dat)
#saveRDS(QID.dat, "./04_Wiki_PolyInfo_XX/QID.dat.Rds")
#QID.dat <- readRDS("./04_Wiki_PolyInfo_XX/QID.dat.Rds")
```

## Visualize Individual network diagrams.

```{r echo=TRUE, eval=FALSE}
library(agGraphSearch)

for(n in 1:length(QID.dat)){
#n <- 1
message(n)
#head(QID.dat[[1]]); head(Labels)
Lab <- names(QID.dat)[n]; Lab00 <- paste(unlist(Labels[Labels$Subject == Lab & Labels$Property == "rdfs:label",c("Object", "Subject")]), collapse = ".")
Lab00

#Merge labels
QID.datR <- MergeWikiData(Data=QID.dat[[n]], 
                          Labels=Labels)
QID.datR <- QID.datR[QID.datR$subject != QID.datR$parentClass,]
QID.datR$subjectLabel <- paste0(QID.datR$subjectLabel, ".", QID.datR$subject)
QID.datR$parentClassLabel <- paste0(QID.datR$parentClassLabel, ".", QID.datR$parentClass)
head(QID.datR)

agGraphSearch:::agVisNetwork_cr(Graph=QID.datR,
                                NodeColorRandom=F, Count=2, 
                                Size=10, SmallSize=5, StarSize=10, 
                                FontSize=7, HeightSclale = "750px", 
                                WidthSclale = "110%", SEED=123, Selected=Lab00, 
                                Browse=F, output=T, file=paste0("./agVisNetwork_", formatC(n, flag="0", width=4), "_", Lab00, ".html"))
suppressMessages(filesstrings::file.move(files = paste0("./agVisNetwork_", formatC(n, flag="0", width=4), "_", Lab00, ".html"),
                        destinations = "./04_Wiki_PolyInfo_01", overwrite = T))

}


```

## Calculate the common upper entities

```{r echo=TRUE, eval=FALSE}
library(magrittr)
#QID.dat <- readRDS("./04_Wiki_PolyInfo_XX/QID.dat.Rds")
#Labels <- readRDS("./04_Wiki_PolyInfo_00/Label_ja_All_label_df.Rds")
#str(QID.dat)

#################################################
#Calculate the common upper entities
#################################################
QID.dat_02 <- c()
CUcounts00 <- c()

for(n in seq_len(length(QID.dat))){
  #n <- 1
  a <- QID.dat[[n]]
  a$triple <- paste0(a$Subject, ".", a$Property, ".", a$Object)
  b <- a[as.numeric(rownames(unique(a["triple"]))),]
  
  #Remove loops
  b <- b[b$Subject != b$Object,]
  QID.dat_02 <- QID.dat_02 %>% rbind(b)
  
  #CU counts
  CUcounts00 <- c(CUcounts00, unique(b$Object))
}

head(QID.dat_02)
dim(QID.dat_02)
rownames(QID.dat_02) <- 1:nrow(QID.dat_02)

##Check NA
table(is.na(QID.dat_02))
table(is.na(QID.dat_02$Subject))
table(is.na(QID.dat_02$Object))

#################################################
## Visualize entire network diagrams
#################################################
#Merge labels
head(QID.dat_02)
QID.datR <- MergeWikiData(Data=QID.dat_02, 
                          Labels=Labels)
QID.datR <- QID.datR[QID.datR$subject != QID.datR$parentClass,]
QID.datR$subjectLabel <- paste0(QID.datR$subjectLabel, ".", QID.datR$subject)
QID.datR$parentClassLabel <- paste0(QID.datR$parentClassLabel, ".", QID.datR$parentClass)
head(QID.datR)

agGraphSearch:::agVisNetwork(Graph=QID.datR,
                             NodeColorRandom=F, Count=2, 
                             Size=10, SmallSize=5, StarSize=10, 
                             FontSize=7, 
                             Output=T, Browse=F,
                             FilePath= paste0("./agVisNetwork_entire.html"))
if(!dir.exists("04_Wiki_PolyInfo_02")){dir.create("04_Wiki_PolyInfo_02")}
suppressMessages(filesstrings::file.move(files = paste0("./agVisNetwork_entire.html"),
                        destinations = "./04_Wiki_PolyInfo_02", overwrite = T))

#################################################
#Count entities and triples
#################################################
#entities
E01 <- length(unique(c(QID.dat_02$Subject, QID.dat_02$Object)))
E01
#[1] 763

#triples
E02 <- length(unique(QID.dat_02$triple))
E02
#[1] 1292

#################################
#Calculate CU entities
#################################
CUcounts00
cu_table <- table(CUcounts00)
cu_table <- cu_table[rev(order(cu_table))]
cu_table1 <- data.frame(parentClass=names(cu_table),
                        Freq=as.numeric(cu_table), 
                        row.names = 1:length(cu_table),
                        stringsAsFactors = F)

head(cu_table1)
cu_table2 <- merge(cu_table1, 
                   Labels[Labels$Property == "rdfs:label",],
                   by.x = "parentClass", by.y = "Subject", 
                   all.x = T, all.y = F, sort=F)
cu_table3 <- cu_table2[cu_table2$Freq > 1,]
head(cu_table3)
tail(cu_table3)

#CU entities
dim(cu_table3)
#[1] 346   5
```

## Graph analysis algorism

```{r echo=TRUE, eval=FALSE}
library(agGraphSearch)
library(magrittr)
library(igraph)
#QID.dat <- readRDS("./04_Wiki_PolyInfo_XX/QID.dat.Rds")
#Labels <- readRDS("./04_Wiki_PolyInfo_00/Label_ja_All_label_df.Rds")
#str(QID.dat)

QID.datRR <- NULL
for(n in 1:length(QID.dat)){
  #n <- 1
  message(n)
  datR <- MergeWikiData(Data=QID.dat[[n]], 
                        Labels=Labels)
  print(head(datR))
  QID.datRR[[n]] <- datR
  names(QID.datRR)[n] <- names(QID.dat)[n]
}

#set parameters
graph_List <- QID.datRR
search_List <- QID.list
CU_List <- cu_table3$parentClass
#QID.d <- readRDS("./04_Wiki_PolyInfo_XX/QID.d.Rds")
#saveRDS(graph_List, "./04_Wiki_PolyInfo_XX/graph_List.Rds")
#saveRDS(search_List, "./04_Wiki_PolyInfo_XX/search_List.Rds")
#saveRDS(CU_List, "./04_Wiki_PolyInfo_XX/CU_List.Rds")

#re-load
#graph_List <- readRDS("./04_Wiki_PolyInfo_XX/graph_List.Rds")
#search_List <- readRDS("./04_Wiki_PolyInfo_XX/search_List.Rds")
#CU_List <- readRDS("./04_Wiki_PolyInfo_XX/CU_List.Rds")

#Calculation
SearchRnage <- agGraphAnalysis(graphList=graph_List,
                               search_List=search_List,
                               CU_List=CU_List)
#system("mv -f ./Results_* ./04_Wiki_PolyInfo_02")

#Levels
SearchRnage00 <- SearchRnage[!is.na(SearchRnage$Levels),]
SearchRnage00 <- SearchRnage00[order(SearchRnage00$Levels),]
rownames(SearchRnage00) <- 1:nrow(SearchRnage00)
head(SearchRnage00)
tail(SearchRnage00)

#Merge labels
SearchRnage01 <- merge(SearchRnage00,
                   Labels[Labels$Property == "rdfs:label",],
                   by.x = "CommonEntity", by.y = "Subject", 
                   all.x = T, all.y = F, sort=F)
SearchRnage01 <- SearchRnage01[order(SearchRnage01$Levels),]
rownames(SearchRnage01) <- 1:nrow(SearchRnage01)
SearchRnage01$Property <- "rdfs:label"
SearchRnage01$Object[is.na(SearchRnage01$Object)] <- SearchRnage01$CommonEntity[is.na(SearchRnage01$Object)]
head(SearchRnage01, n=15)
tail(SearchRnage01, n=15)

#saveRDS(SearchRnage01, "./04_Wiki_PolyInfo_XX/SearchRnage01.Rds")
#SearchRnage01 <- readRDS("./04_Wiki_PolyInfo_XX/SearchRnage01.Rds")
#readr::write_excel_csv(SearchRnage01, "./04_Wiki_PolyInfo_XX/SearchRnage01.csv")

```

# Subordinate search

```{r echo=TRUE, eval=FALSE}
ECU.list <- SearchRnage01

#Run
for(n in 1:nrow(ECU.list)){
#n <- 1
message("No.", n, ": ", ECU.list$CommonEntity[n], " ", ECU.list$Object[n])
Dat <- c(); x <- 0; Query <- ECU.list$CommonEntity[n]

repeat{
x <- x + 1
message("x: ", x)

#Both wdt:P279 and wdt:P31
b1 <- ClassHi[ClassHi$Object %in% Query,]

#Only wdt:P279 when x = Levels
if(x != ECU.list$Levels[n]){
  b1 <- b1[b1$Property == "wdt:P279",]
}

if(nrow(b1) == 0){
  rownames(Dat) <- 1:nrow(Dat)
  Dat$triple <- paste0(Dat$Subject, ".", Dat$Property, ".", Dat$Object)
  Dat <- Dat[as.numeric(rownames(unique(Dat["triple"]))),-c(ncol(Dat))]
  rownames(Dat) <- 1:nrow(Dat)
  #head(Dat); dim(Dat)
  break
  }
Dat <- rbind(Dat, b1)
Query <- b1$Subject
if(x == ECU.list$Levels[n]){
  rownames(Dat) <- 1:nrow(Dat)
  Dat$triple <- paste0(Dat$Subject, ".", Dat$Property, ".", Dat$Object)
  Dat <- Dat[as.numeric(rownames(unique(Dat["triple"]))),-c(ncol(Dat))]
  rownames(Dat) <- 1:nrow(Dat)
  #head(Dat); dim(Dat)
  break
}
}
#head(Dat); dim(Dat)
print(dim(Dat))
saveRDS(Dat,
        paste0("./04_Wiki_PolyInfo_03/", 
               formatC(n, width = 4, flag = "0"),
                "_L", ECU.list$Levels[n], "_",
               ECU.list$CommonEntity[n],
               ".Rds"))
}

```

# Calucation & Evaluation for all candidates

```{r echo=TRUE, eval=FALSE}
#rm(list=ls())
#SearchRnage01 <- readRDS("./04_Wiki_PolyInfo_XX/SearchRnage01.Rds")
dim(SearchRnage01)

#01 Barplot
SearchRnage02 <- data.frame(No=names(table(SearchRnage01$Levels)),
                each_entity=as.numeric(table(SearchRnage01$Levels)))
head(SearchRnage02)

##02 
ECU.list <- SearchRnage01
ECU.list$UniTripleNum <- NA
ECU.list$UniEntityNum <- NA
TotalData <- NULL

for(n in 1:nrow(ECU.list)){
#n <- 1
message(n)
b <- readRDS(paste0("./04_Wiki_PolyInfo_03/", 
               formatC(n, width = 4, flag = "0"),
                "_L", ECU.list$Levels[n], "_",
               ECU.list$CommonEntity[n], ".Rds"))

#head(b)
b$triple <- paste0(b$Subject, ".",
                    b$Property, ".",
                    b$Object)
ECU.list$UniTripleNum[n] <- length(unique(b$triple))
ECU.list$UniEntityNum[n] <- length(unique(c(b$Subject, b$Object)))
#head(ECU.list)
#head(b); head(b[,-4])
TotalData[[n]] <- b
}

#str(TotalData)
#saveRDS(TotalData, "./04_Wiki_PolyInfo_XX/TotalData.Rds")
#saveRDS(ECU.list, "./04_Wiki_PolyInfo_XX/ECU.list.Rds")
#readr::write_excel_csv(ECU.list, "./04_Wiki_PolyInfo_XX/ECU.list.csv", append=F, col_names=T)

##step 01
head(ECU.list)
rownames(ECU.list) <- 1:nrow(ECU.list)
#str(TotalData)
TotalDataECU <- NULL
k <- max(ECU.list$Levels)

for(m in 1:k){
  #m <- 1
  message("m: ", m)
  d <- ECU.list[ECU.list$Levels == m,]
  d1 <- as.numeric(rownames(d))
  temp <- NULL
  system(paste0("rm -rf ./04_Wiki_PolyInfo_06/TotalData_OutTriples_L", m, ".csv"))
  for(n in d1){
    #n <- 1
    message("n: ", n)
    readr::write_csv(TotalData[[n]], 
                     paste0("./04_Wiki_PolyInfo_06/TotalData_OutTriples_L", m, ".csv"), 
                     append=T, col_names=F)
}
temp <- data.frame(readr::read_csv(paste0("./04_Wiki_PolyInfo_06/TotalData_OutTriples_L", m, ".csv"),
                        show_col_types = FALSE, col_names=F))
colnames(temp) <- c("Subject", "Property", "Object", "triple")
rownames(temp) <- 1:nrow(temp)
temp <- temp[as.numeric(rownames(unique(temp["triple"]))),]
#head(temp)
readr::write_csv(temp, paste0("./04_Wiki_PolyInfo_06/TotalData_OutTriples_L", m, "R.csv"), 
                 append=F, col_names=F)
}

#Remove
if(length(dir(path = "./04_Wiki_PolyInfo_06", pattern = "R_Acc.csv")) != 0){
  system("rm -rf TotalData_OutTriples_L*R_Acc.csv")
}

for(m in 1:k){
#m <- 1
message("m: ", m)
temp <- data.frame(readr::read_csv(paste0("./04_Wiki_PolyInfo_06/TotalData_OutTriples_L", m, "R.csv"),
                        show_col_types = FALSE, col_names=F))
for(l in m:k){
#l <- 1
message("l: ", l)
readr::write_csv(temp,
                 paste0("./04_Wiki_PolyInfo_06/TotalData_OutTriples_L", l, "R_Acc.csv"), 
                 append=T, col_names=F)  
}}

```

# For Evaluation

```{r echo=TRUE, eval=FALSE}
#ECU.list <- readRDS("./04_Wiki_PolyInfo_XX/ECU.list.Rds")
#k <- max(ECU.list$Levels)
str(ECU.list)
CountDat <- data.frame(No=1:k,
                       UniEntityNum=NA,
                       UniTripleNum=NA,
                       UniJpnLab=NA,
                       AccEntityNum=NA,
                       AccTripleNum=NA,
                       AccJpnLab=NA,
                       ExtractedNum=NA,
                       RateAccEntity=NA,
                       TotalAnswerNum=NA)

##Evaluation
#Labels <- readRDS("./04_Wiki_PolyInfo_00/Label_ja_All_label_df.Rds")
#OCR <- unlist(readr::read_csv("./高分子辞典OCR/高分子辞典OCR_2column_jpn_RRR.csv", col_names=F, show_col_types = FALSE), use.names = F)
OCR.eva <- OCR[OCR %in% Labels$Object]
length(OCR.eva)

#step 03
#Evaluation
for(n in 1:k){
  #n <- 1
  message("n: ", n)
  #Uni
  temp <- data.frame(readr::read_csv(paste0("./04_Wiki_PolyInfo_06/TotalData_OutTriples_L", n, "R.csv"),
                                     show_col_types = FALSE, col_names=F))
  colnames(temp) <- c("Subject", "Property", "Object", "triple")
  rownames(temp) <- 1:nrow(temp)
  temp <- temp[as.numeric(rownames(unique(temp["triple"]))),]
  #head(temp)
  message("Uni")
  CountDat$UniEntityNum[n]  <- length(unique(c(temp$Subject, temp$Object)))
  CountDat$UniTripleNum[n] <- length(unique(temp$triple))
  
  #Jpn
  UniEntity <- unique(c(temp$Subject, temp$Object))
  #head(Labels)
  LabelsNum <- Labels[Labels$Subject %in% UniEntity, ]
  CountDat$UniJpnLab[n] <- length(unique(LabelsNum$Subject))
  
  #Acc
  temp <- data.frame(readr::read_csv(paste0("./04_Wiki_PolyInfo_06/TotalData_OutTriples_L", n, "R_Acc.csv"),
                                     show_col_types = FALSE, col_names=F))
  colnames(temp) <- c("Subject", "Property", "Object", "triple")
  rownames(temp) <- 1:nrow(temp)
  temp <- temp[as.numeric(rownames(unique(temp["triple"]))),]
  
  #head(temp)
  message("Acc")
  CountDat$AccEntityNum[n]  <- length(unique(c(temp$Subject, temp$Object)))
  CountDat$AccTripleNum[n] <- length(unique(temp$triple))
  
  #Jpn
  UniEntity <- unique(c(temp$Subject, temp$Object))
  #head(Labels)
  LabelsNum <- Labels[Labels$Subject %in% UniEntity, ]
  CountDat$AccJpnLab[n] <- length(unique(LabelsNum$Subject))

  message("OCR")
  Eva00 <- unique(c(temp$Subject, temp$Object))
  #head(Labels)
  Eva01 <- unique(Labels[Labels$Subject %in% Eva00,]$Object)
  #Eva01
  Eva02 <- round(sum(Eva01 %in% OCR.eva)/length(OCR.eva)*100, 3)
  CountDat$ExtractedNum[n] <- sum(Eva01 %in% OCR.eva)
  CountDat$RateAccEntity[n] <- Eva02
  CountDat$TotalAnswerNum[n] <- length(OCR.eva)
  
  print(CountDat)

}

SearchRnage01 <- readRDS("./04_Wiki_PolyInfo_XX/SearchRnage01.Rds")
dim(SearchRnage01)

#01 Barplot
SearchRnage02 <- data.frame(No=names(table(SearchRnage01$Levels)),
each_entity=as.numeric(table(SearchRnage01$Levels)))
head(SearchRnage02)

#ECU 
CountDat$RateAccEntityPrec <- round((CountDat$ExtractedNum / CountDat$AccEntityNum)*100, 5)
CountDat$RateAccEntityPrecLog <- round(logb((CountDat$ExtractedNum / CountDat$AccEntityNum)*100), 5)
CountDat$RateAccJpnPrec <- round((CountDat$ExtractedNum / CountDat$AccJpnLab)*100, 5)
CountDat$RateAccJpnPrecLog <- round(logb((CountDat$ExtractedNum / CountDat$AccJpnLab)*100), 5)

CountDat$each_entity <- SearchRnage02$each_entity
CountDat$sum_entity <- cumsum(SearchRnage02$each_entity)
CountDat

readr::write_csv(CountDat, "./04_Wiki_PolyInfo_XX/CountDat.csv", append=F, col_names=T)

```

# Refinement for the ontology candidate

```{r echo=TRUE, eval=FALSE}
#rm(list=ls())
library(igraph)

SearchRnage01 <- readRDS("./04_Wiki_PolyInfo_XX/SearchRnage01.Rds")
ClassHi <- readRDS("./04_Wiki_PolyInfo_00/ClassHiR.Rds")
b1 <- SearchRnage01
head(b1)

QID.d <- readRDS("./04_Wiki_PolyInfo_XX/QID.d.Rds")$QID
head(QID.d)

CU_List <- readRDS("./04_Wiki_PolyInfo_XX/CU_List.Rds")
head(CU_List)

#Refinement: get the direction of the search entity
for(n in 1:nrow(b1)){
#n <- 1
#n <- 44
#n <- 49
#n <- 52
#n <- 56
#n <- 66
#head(b1)

print(n)
d <- readRDS(paste0("./04_Wiki_PolyInfo_03/",
                    formatC(n, width = 4, flag = "0"),
                    "_L", b1$Levels[n], "_",
                    b1$CommonEntity[n], ".Rds"))
head(d)
message("All: ", dim(d)[1])

g <- simplify(graph_from_edgelist(as.matrix(d[,c(1,3)]), directed = T))
V(g)$color <- "lightyellow"

f1 <- names(V(g)) %in% unique(QID.d)
V(g)$color[f1] <- "skyblue"

f2 <- names(V(g)) %in% unique(b1$CommonEntity)
V(g)$color[f2] <- "pink"

f3 <- names(V(g)) %in% CU_List[!(CU_List %in% unique(b1$CommonEntity))]
V(g)$color[f3] <- "lightgreen"

f <- names(V(g)) %in% b1$CommonEntity[n]
V(g)$color[f] <- "blue"

len <- length(V(g)$color)
len1 <- length(V(g)$color[f1])
len2 <- length(V(g)$color[f2])
len3 <- length(V(g)$color[f3])

if(length(names(V(g))) < 100){
V(g)$size <- 3
V(g)$size[f] <- 6
V(g)$size[f1] <- 4
V(g)$size[f2] <- 4
E(g)$width <- 0.75
V(g)$label.cex <- 0.1
CEX=0.2
}else{
if(length(names(V(g))) < 500){
V(g)$size <- 2
V(g)$size[f] <- 5
V(g)$size[f1] <- 3
V(g)$size[f2] <- 3
E(g)$width <- 0.5
V(g)$label.cex <- 0.05
CEX=0.1
}else{
V(g)$size <- 0.5
V(g)$size[f] <- 3
V(g)$size[f1] <- 1.5
V(g)$size[f2] <- 1.5
E(g)$width <- 0.1
V(g)$label.cex <- 0
CEX=0.01
}}

E(g)$lty <- 1

##########################################
#Pathway
##########################################
h1 <- c(1:length(names(V(g))))[names(V(g)) %in% b1$CommonEntity[n]]
h2 <- c(1:length(names(V(g))))[names(V(g)) %in% QID.d]
h2 <- h2[!c(h2 %in% h1)]

i <- c()
if(identical(h2, integer(0))){
i[[1]] <- NA
}else{
for(m in 1:length(h2)){
#m <- 1
suppressMessages(h3 <- names(get.shortest.paths(g,
                                                from=h1,
                                                to=h2[m],
                                                mode = "in")$vpath[[1]]))
if(length(h3) == 2){
if(b1$Levels[n] == 1){
i[[m]] <- NA
}else{
#low-level entities from search entity
i[[m]] <- h3
}
}else{
i[[m]] <- c(h3)
}
} 
}

if(all(is.na(unlist(i)))){
V(g)$color[V(g)$color == "lightyellow"] <- "firebrick2"
saveRDS(d,
        paste0("./04_Wiki_PolyInfo_05/",
               formatC(n, width = 4, flag = "0"),
               "_L", b1$Levels[n], "_",
               b1$CommonEntity[n], "_refine.Rds"))
message("No Refine: ", dim(d)[1])

}else{
ii <- c()
for(l in 1:length(i)){
#l <- 1
#l <- 2
if(!all(is.na(unlist(i[[l]])))){
if(length(i[[l]]) == 2){
i0 <- i[[l]]
for(k in 1:length(i0)){
#k <- 1
if(i0[k] == b1$CommonEntity[n]){
  ii <- c(ii, names(neighbors(g, v=b1$CommonEntity[n], mode = "in")))
}else{
  ii <- c(ii, names(subcomponent(g, c(1:length(names(V(g))))[names(V(g)) %in% i0[k]], "in")))
}}
}else{
i0 <- i[[l]]
i0 <- i0[!c(i0 %in% b1$CommonEntity[n])]

if(length(i0) < 4){
for(k in 1:length(i0)){
#k <- 1
ii <- c(ii, names(subcomponent(g, c(1:length(names(V(g))))[names(V(g)) %in% i0[k]], "in")))
}  
}else{
kk <- length(i0) - 2
for(k in kk:length(i0)){
#k <- 1
ii <- c(ii, names(subcomponent(g, c(1:length(names(V(g))))[names(V(g)) %in% i0[k]], "in")))
}
}
}
}else{
ii <- c(ii, names(neighbors(g, v=b1$CommonEntity[n], mode = "in")))
}
}

ii <- ii[!(ii %in% b1$CommonEntity[n])]
ii <- ii[!(ii %in% QID.d)]
V(g)$color[names(V(g)) %in% unique(ii)] <- "firebrick2"

#head(d)
Ex <- unique(names(V(g))[V(g)$color == "lightyellow"])

#head(d)
d1 <- d[!(d$Subject %in% Ex),]
d1 <- d1[!(d1$Object %in% Ex),]
#dim(d1)
saveRDS(d1,
        paste0("./04_Wiki_PolyInfo_05/",
               formatC(n, width = 4, flag = "0"),
               "_L", b1$Levels[n], "_",
               b1$CommonEntity[n], "_refine.Rds"))
message("Refine: ", dim(d1)[1])
}

if(nrow(d) < 100000){
##plot 1
set.seed(123)
system.time(layout03 <- layout_with_fr(g))
el <- data.table::as.data.table(as_edgelist(g)) %>%
  data.table::setnames(c("x","y"))

d_layout <- data.table::data.table(x_coord = layout03[,1], y_coord = layout03[,2], id = names(V(g)))
el_w_layout <- merge(el, d_layout, by.x = "x", by.y = "id", all.x = TRUE) %>%
        data.table::setnames( c("x_coord", "y_coord"), c("x1", "y1") ) %>%
        merge( d_layout, by.x = "y", by.y = "id", all.x = TRUE ) %>%
        data.table::setnames( c("x_coord", "y_coord"), c("x2", "y2") )

#head(d_layout)
quartz(width=7.5, height=7.5)
par(bg="white", cex.main=0.5, family="HiraKakuProN-W3", mgp=c(2.5, 1, 0), mai=c(0.5, 0.5, 0.5, 0.5))
plot(d_layout[,1:2], axes = F, type = "n", xlab = NA, ylab = NA,
  xlim=c(c(range(d_layout$x_coord)) + c(-diff(range(d_layout$x_coord))*0.05, diff(range(d_layout$x_coord))*0.05)),
  ylim=c(c(range(d_layout$y_coord)) + c(-diff(range(d_layout$y_coord))*0.05, diff(range(d_layout$y_coord))*0.05)))
segments(x0  = el_w_layout$x1, x   = el_w_layout$x2,
         y0  = el_w_layout$y1, y   = el_w_layout$y2,
         col = scales::alpha("grey", .3))
points(d_layout$x_coord, d_layout$y_coord, pch = 21, col="grey", lwd=0.2, cex = V(g)$size, bg=V(g)$color,
       main=paste0( b1$Label.j[n], "\nTotal: ", len, ", Search: ", len1, ", Common: ", len2, ", both: ", len3))
if(len < 10000){
text(d_layout$x_coord, d_layout$y_coord, labels=d_layout$id, cex=CEX)
}

quartz.save(file = paste0("./04_Wiki_PolyInfo_05/",
            formatC(n, width = 4, flag = "0"),
            "_L", b1$Levels[n], "_",
            b1$CommonEntity[n], "_refine1.png"),
            type = "png", dpi=300); dev.off()
}

##plot 2
if(!all(is.na(unlist(i)))){
g <- simplify(graph_from_edgelist(as.matrix(d1[,c(1,3)]), directed = T))
V(g)$color <- "lightyellow"

f1 <- names(V(g)) %in% unique(QID.d)
V(g)$color[f1] <- "skyblue"

f2 <- names(V(g)) %in% unique(b1$CommonEntity)
V(g)$color[f2] <- "pink"

f3 <- names(V(g)) %in% CU_List[!(CU_List %in% unique(b1$CommonEntity))]
V(g)$color[f3] <- "lightgreen"

f <- names(V(g)) %in% b1$CommonEntity[n]
V(g)$color[f] <- "blue"

V(g)$color[names(V(g)) %in% unique(ii)] <- "firebrick2"

len <- length(V(g)$color)
len1 <- length(V(g)$color[f1])
len2 <- length(V(g)$color[f2])
len3 <- length(V(g)$color[f3])

if(length(names(V(g))) < 100){
V(g)$size <- 3
V(g)$size[f] <- 6
V(g)$size[f1] <- 4
V(g)$size[f2] <- 4
E(g)$width <- 0.75
V(g)$label.cex <- 0.1
CEX=0.1
}else{
if(length(names(V(g))) < 500){
V(g)$size <- 2
V(g)$size[f] <- 5
V(g)$size[f1] <- 3
V(g)$size[f2] <- 3
E(g)$width <- 0.5
V(g)$label.cex <- 0.05
CEX=0.05
}else{
V(g)$size <- 0.5
V(g)$size[f] <- 3
V(g)$size[f1] <- 1.5
V(g)$size[f2] <- 1.5
E(g)$width <- 0.1
V(g)$label.cex <- 0
CEX=0.01
}}

E(g)$lty <- 1

if(nrow(d) < 100000){
set.seed(123)
system.time(layout03 <- layout_with_fr(g))
el <- data.table::as.data.table(as_edgelist(g)) %>%
  data.table::setnames(c("x","y"))

d_layout <- data.table::data.table(x_coord = layout03[,1], y_coord = layout03[,2], id = names(V(g)))
el_w_layout <- merge(el, d_layout, by.x = "x", by.y = "id", all.x = TRUE) %>%
        data.table::setnames( c("x_coord", "y_coord"), c("x1", "y1") ) %>%
        merge( d_layout, by.x = "y", by.y = "id", all.x = TRUE ) %>%
        data.table::setnames( c("x_coord", "y_coord"), c("x2", "y2") )

head(d_layout)
quartz(width=7.5, height=7.5)
par(bg="white", cex.main=0.5, family="HiraKakuProN-W3", mgp=c(2.5, 1, 0), mai=c(0.5, 0.5, 0.5, 0.5))
plot(d_layout[,1:2], axes = F, type = "n", xlab = NA, ylab = NA,
  xlim=c(c(range(d_layout$x_coord)) + c(-diff(range(d_layout$x_coord))*0.05, diff(range(d_layout$x_coord))*0.05)),
  ylim=c(c(range(d_layout$y_coord)) + c(-diff(range(d_layout$y_coord))*0.05, diff(range(d_layout$y_coord))*0.05)))
segments(x0  = el_w_layout$x1, x   = el_w_layout$x2,
         y0  = el_w_layout$y1, y   = el_w_layout$y2,
         col = scales::alpha("grey", .3))
points(d_layout$x_coord, d_layout$y_coord, pch = 21, col="grey", lwd=0.2, cex = V(g)$size, bg=V(g)$color,
       main=paste0( b1$Label.j[n], "\nTotal: ", len, ", Search: ", len1, ", Common: ", len2, ", both: ", len3))
if(len < 10000){
text(d_layout$x_coord, d_layout$y_coord, labels=d_layout$id, cex=CEX)
}
quartz.save(file = paste0("./04_Wiki_PolyInfo_05/",
            formatC(n, width = 4, flag = "0"),
            "_L", b1$Levels[n], "_",
            b1$CommonEntity[n], "_refine2.png"),
            type = "png", dpi=300); dev.off()
}



#Num
d.len <- length(unique(c(d$Subject, d$Object)))
d1.len <- length(unique(c(d1$Subject, d1$Object)))
d2 <- paste0("Delete: ", d.len, " => ", d1.len)

#
readr::write_csv(data.frame(d2),
                file = paste0("./04_Wiki_PolyInfo_05/",
                              formatC(n, width = 4, flag = "0"),
                              "_L", b1$Levels[n], "_",
                              b1$CommonEntity[n], "_Delete.csv"),
                append=F, col_names=F)

#Save Delete_all.csv 
readr::write_csv(data.frame(X=paste0("No: ", n), Y=d2),
                file = paste0("./04_Wiki_PolyInfo_05/Delete_all.csv"),
                append=T, col_names=F)

}
}


```

# Evaluation after the refinement

```{r echo=TRUE, eval=FALSE}
#system(paste0("rm -rf ./04_Wiki_PolyInfo_06/*"))
#ECU.list <- readRDS("./04_Wiki_PolyInfo_XX/ECU.list.Rds")
head(ECU.list)
k <- max(ECU.list$Levels)

##step 01
for(m in 1:k){
  #m <- 1
  message("m: ", m)
  d <- ECU.list[ECU.list$Levels == m,]
  d1 <- as.numeric(rownames(d))
  temp <- NULL
  system(paste0("rm -rf ", "./04_Wiki_PolyInfo_06/Refinement_OutTriples_L", m, ".csv"))
  for(n in d1){
    #n <- 1
    message("n: ", n)
    Dat <- readRDS(paste0("./04_Wiki_PolyInfo_05/",
                          formatC(n, width = 4, flag = "0"),
                          "_L", ECU.list$Levels[n], "_",
                          ECU.list$CommonEntity[n], "_refine.Rds"))
    readr::write_csv(Dat, 
                     paste0("./04_Wiki_PolyInfo_06/Refinement_OutTriples_L", m, ".csv"), 
                     append=T, col_names=F)
}
#getwd()
temp <- data.frame(readr::read_csv(paste0("./04_Wiki_PolyInfo_06/Refinement_OutTriples_L", m, ".csv"),
                   show_col_types = FALSE, col_names=F))
colnames(temp) <- c("Subject", "Property", "Object")
temp$triple <- paste0(temp$Subject, ".", temp$Property, ".", temp$Object)
rownames(temp) <- 1:nrow(temp)
temp <- temp[as.numeric(rownames(unique(temp["triple"]))),]
#head(temp)
readr::write_csv(temp, paste0("./04_Wiki_PolyInfo_06/Refinement_OutTriples_L", m, "R.csv"), append=F, col_names=F)
}

#Remove
if(length(dir(path = "./04_Wiki_PolyInfo_06", pattern = "R_Acc.csv")) != 0){
  system("rm -rf ./04_Wiki_PolyInfo_06/Refinement_OutTriples_L*R_Acc.csv")
}

##step 02
for(j in 1:k){
#j <- 1
message("j: ", j)
temp <- data.frame(readr::read_csv(paste0("./04_Wiki_PolyInfo_06/Refinement_OutTriples_L", j, "R.csv"),
                        show_col_types = FALSE, col_names=F))
for(l in j:k){
#l <- 1
message("l: ", l)
readr::write_csv(temp,
                 paste0("./04_Wiki_PolyInfo_06/Refinement_OutTriples_L", l, "R_Acc.csv"), 
                 append=T, col_names=F)  
}}
```

# For Evaluation

```{r echo=TRUE, eval=FALSE}
#rm(list=ls())
#ECU.list <- readRDS("./04_Wiki_PolyInfo_XX/ECU.list.Rds")
head(ECU.list)
k <- max(ECU.list$Levels)

CountDatRefine <- data.frame(No=1:k,
                       UniEntityNum=NA,
                       UniTripleNum=NA,
                       UniJpnLab=NA,
                       AccEntityNum=NA,
                       AccTripleNum=NA,
                       AccJpnLab=NA,
                       ExtractedNum=NA,
                       RateAccEntity=NA,
                       TotalAnswerNum=NA)

#Labels <- readRDS("./04_Wiki_PolyInfo_00/Label_ja_All_label_df.Rds")
#OCR <- unlist(readr::read_csv("./高分子辞典OCR/高分子辞典OCR_2column_jpn_RRR.csv", col_names=F, show_col_types = FALSE), use.names = F)
OCR.eva <- OCR[OCR %in% Labels$Object]
length(OCR.eva)

##step 03
for(n in 1:k){
  #n <- 1
  message("n: ", n)
  
  #Uni
  temp <- data.frame(readr::read_csv(paste0("./04_Wiki_PolyInfo_06/Refinement_OutTriples_L", n, "R.csv"),
                                     show_col_types = FALSE, col_names=F))
  colnames(temp) <- c("Subject", "Property", "Object", "triple")
  rownames(temp) <- 1:nrow(temp)
  temp <- temp[as.numeric(rownames(unique(temp["triple"]))),]
  
  #head(temp)
  message("Uni")
  CountDatRefine$UniEntityNum[n]  <- length(unique(c(temp$Subject, temp$Object)))
  CountDatRefine$UniTripleNum[n] <- length(unique(temp$triple))
  
  #Jpn
  UniEntity <- unique(c(temp$Subject, temp$Object))
  #head(Labels)
  LabelsNum <- Labels[Labels$Subject %in% UniEntity, ]
  CountDatRefine$UniJpnLab[n] <- length(unique(LabelsNum$Subject))
  
  #Acc
  temp <- data.frame(readr::read_csv(paste0("./04_Wiki_PolyInfo_06/Refinement_OutTriples_L", n, "R_Acc.csv"),
                                     show_col_types = FALSE, col_names=F))
  colnames(temp) <- c("Subject", "Property", "Object", "triple")
  rownames(temp) <- 1:nrow(temp)
  temp <- temp[as.numeric(rownames(unique(temp["triple"]))),]
  
  readr::write_csv(temp,
                   paste0("./04_Wiki_PolyInfo_06/Refinement_OutTriples_L", n, "R_Acc_Uni.csv"), 
                   append=F, col_names=F)  
  
  #head(temp)
  message("Acc")
  CountDatRefine$AccEntityNum[n]  <- length(unique(c(temp$Subject, temp$Object)))
  CountDatRefine$AccTripleNum[n] <- length(unique(temp$triple))
  
  #Jpn
  UniEntity <- unique(c(temp$Subject, temp$Object))
  #head(Labels)
  LabelsNum <- Labels[Labels$Subject %in% UniEntity, ]
  CountDatRefine$AccJpnLab[n] <- length(unique(LabelsNum$Subject))
 
  message("OCR")
  Eva00 <- unique(c(temp$Subject, temp$Object))
  
  #head(Labels)
  Eva01 <- unique(Labels[Labels$Subject %in% Eva00,]$Object)
  
  #Eva01
  Eva02 <- round(sum(Eva01 %in% OCR.eva)/length(OCR.eva)*100, 3)
  
  CountDatRefine$ExtractedNum[n] <- sum(Eva01 %in% OCR.eva)
  CountDatRefine$RateAccEntity[n] <- Eva02
  CountDatRefine$TotalAnswerNum[n] <- length(OCR.eva)
  print(CountDatRefine)

}

SearchRnage01 <- readRDS("./04_Wiki_PolyInfo_XX/SearchRnage01.Rds")
dim(SearchRnage01)

#01 Barplot
SearchRnage02 <- data.frame(No=names(table(SearchRnage01$Levels)),
                each_entity=as.numeric(table(SearchRnage01$Levels)))
head(SearchRnage02)

#ECU 
CountDatRefine$RateAccEntityPrec <- round((CountDatRefine$ExtractedNum / CountDatRefine$AccEntityNum)*100, 5)
CountDatRefine$RateAccEntityPrecLog <- round(logb((CountDatRefine$ExtractedNum / CountDatRefine$AccEntityNum)*100), 5)
CountDatRefine$RateAccJpnPrec <- round((CountDatRefine$ExtractedNum / CountDatRefine$AccJpnLab)*100, 5)
CountDatRefine$RateAccJpnPrecLog <- round(logb((CountDatRefine$ExtractedNum / CountDatRefine$AccJpnLab)*100), 5)

CountDatRefine$each_entity <- SearchRnage02$each_entity[1:k]
CountDatRefine$sum_entity <- cumsum(SearchRnage02$each_entity)[1:k]

readr::write_csv(CountDatRefine, 
                 "./04_Wiki_PolyInfo_XX/CountDatRefine.csv", append=F, col_names=T)

```

# Plots of results

```{r echo=TRUE, eval=FALSE}
library(magrittr); library(plotly)
CountDat <- data.frame(readr::read_csv("./04_Wiki_PolyInfo_XX/CountDat.csv", show_col_types = FALSE, col_names=T))
CountDat
CountDatRefine <- data.frame(readr::read_csv("./04_Wiki_PolyInfo_XX/CountDatRefine.csv", show_col_types = FALSE, col_names=T))
CountDatRefine

######################################################
#Barplot 01
######################################################
fig <- plotly::plot_ly(CountDat, x = ~No, y = ~each_entity, type = 'bar', name = '',
               hovertemplate = paste0('%{y}'),
               marker = list(color = 'rgb(158,202,225)', line = list(color = 'rgb(8,48,107)', width = 0.25)))
fig <- fig %>% plotly::layout(title = paste0("Number of ECU entities"),
                      yaxis = list(title = 'Entity number', linewidth = 1),
                      xaxis = list(title = "NES", ticks = "outside", linewidth = 0,
                                     tick0 = 1, dtick = 1),
                      margin = list(l=50, r=10, b=50, t=50, pad=4))
fig

if(!dir.exists("04_Wiki_PolyInfo_04")){dir.create("04_Wiki_PolyInfo_04")}
Filename <- paste0("./Results_", format(Sys.time(), "%y%m%d"),"_01.html")
htmlwidgets::saveWidget(plotly::as_widget(fig), file=Filename)
system(paste0("mv ", Filename, " ./04_Wiki_PolyInfo_04"))

######################################################
#Barplot 02
######################################################
fig <- plotly::plot_ly(CountDat, x = ~No, y = ~UniEntityNum, type = 'bar', name = '',
               hovertemplate = paste0('%{y}'),
               marker = list(color = 'rgb(158,202,225)', line = list(color = 'rgb(8,48,107)', width = 0.25)))
fig <- fig %>% plotly::layout(title = paste0("Number of concepts per ENS (with dup.)"),
                      yaxis = list(title = 'Entity number', linewidth = 1,
                                   range=c(0,70000000)),
                      xaxis = list(title = "NES", ticks = "outside", linewidth = 0,
                                     tick0 = 1, dtick = 1),
                      margin = list(l=50, r=10, b=50, t=50, pad=4))
fig

Filename <- paste0("./Results_", format(Sys.time(), "%y%m%d"),"_02.html")
htmlwidgets::saveWidget(plotly::as_widget(fig), file=Filename)
system(paste0("mv ", Filename, " ./04_Wiki_PolyInfo_04"))

######################################################
#Barplot 03
######################################################
fig <- plotly::plot_ly(CountDat, x = ~No, y = ~AccEntityNum, type = 'bar', name = '',
               hovertemplate = paste0('%{y}'),
               marker = list(color = 'rgb(158,202,225)', line = list(color = 'rgb(8,48,107)', width = 0.25)))
fig <- fig %>% plotly::layout(title = paste0("Unique cumulative number of concepts"),
                      yaxis = list(title = 'Entity number', linewidth = 1,
                                   range=c(0,70000000)),
                      xaxis = list(title = "NES", ticks = "outside", linewidth = 0,
                                     tick0 = 1, dtick = 1),
                      margin = list(l=50, r=10, b=50, t=50, pad=4))
fig

Filename <- paste0("./Results_", format(Sys.time(), "%y%m%d"),"_03.html")
htmlwidgets::saveWidget(plotly::as_widget(fig), file=Filename)
system(paste0("mv ", Filename, " ./04_Wiki_PolyInfo_04"))

######################################################
#Plot 01: Recall
######################################################
CountDat$Refine.RateAccEntity <- CountDatRefine$RateAccEntity
CountDat$Refine.RateAccJpnPrec <- CountDatRefine$RateAccJpnPrec

fig <- plotly::plot_ly(CountDat, x = ~No, y = ~RateAccEntity, 
                       type = 'scatter', mode = 'lines+markers', name = 'All candidates',
               hovertemplate = paste0('%{y}'),
               marker = list(color = 'rgb(158,202,225)', 
                             size=8,
                             line = list(color = 'rgb(8,48,107)', width = 0.5)))
fig <- fig %>% add_trace(CountDat, y = ~Refine.RateAccEntity, name = 'Refinement', 
                         mode = 'lines+markers',
                         marker = list(color = 'rgb(255,128,0)', 
                                       size=8,
                                       line = list(color = 'rgb(8,48,107)', width = 0.5))) 
fig <- fig %>% plotly::layout(title = paste0(""),
                      yaxis = list(title = 'Recall rate (%)', linewidth = 1,
                                   tick0 = 0, dtick = 10, range=c(0,80), zeroline = F),
                      xaxis = list(title = "NES range", ticks = "outside", linewidth = 1,
                                     tick0 = 0, dtick = 1),
                      margin = list(l=50, r=10, b=50, t=50, pad=4))
fig

Filename <- paste0("./Results_", format(Sys.time(), "%y%m%d"),"_04R.html")
htmlwidgets::saveWidget(plotly::as_widget(fig), file=Filename)
system(paste0("mv ", Filename, " ./04_Wiki_PolyInfo_04"))

######################################################
#Plot 02: Precision
######################################################
fig <- plotly::plot_ly(CountDat, x = ~No, y = ~RateAccJpnPrec, 
                       type = 'scatter', mode = 'lines+markers', name = 'All candidates',
                       hovertemplate = paste0('%{y}'),
                       marker = list(color = 'rgb(158,202,225)', 
                                     size=8,
                                     line = list(color = 'rgb(8,48,107)', width = 0.5)))
fig <- fig %>% add_trace(CountDat, y = ~Refine.RateAccJpnPrec, name = 'Refinement', 
                         mode = 'lines+markers',
                         marker = list(color = 'rgb(255,128,0)', 
                                       size=8,
                                       line = list(color = 'rgb(8,48,107)', width = 0.5))) 
fig <- fig %>% plotly::layout(title = paste0(""),
                      yaxis = list(title = 'Precision rate (%)', linewidth = 1,
                                   tick0 = 0, dtick = 1, type = "log"),
                      xaxis = list(title = "NES range", ticks = "outside", linewidth = 1,
                                     tick0 = 0, dtick = 1),
                      margin = list(l=50, r=10, b=50, t=50, pad=4))
fig

Filename <- paste0("./Results_", format(Sys.time(), "%y%m%d"),"_05R.html")
htmlwidgets::saveWidget(plotly::as_widget(fig), file=Filename)
system(paste0("mv ", Filename, " ./04_Wiki_PolyInfo_04"))

######################################################
#CountDatRefine: Barplot 02
######################################################
fig <- plotly::plot_ly(CountDatRefine, x = ~No, y = ~UniEntityNum, type = 'bar', name = '',
               hovertemplate = paste0('%{y}'),
               marker = list(color = 'rgb(255,158,72)', line = list(color = 'rgb(8,48,107)', width = 0.25)))
fig <- fig %>% plotly::layout(title = paste0("Number of concepts per ENS (with dup.)"),
                      yaxis = list(title = 'Entity number', linewidth = 1,
                                   range=c(0,70000000)),
                      xaxis = list(title = "NES", ticks = "outside", linewidth = 0,
                                     tick0 = 1, dtick = 1),
                      margin = list(l=50, r=10, b=50, t=50, pad=4))
fig

Filename <- paste0("./Results_", format(Sys.time(), "%y%m%d"),"_06R.html")
htmlwidgets::saveWidget(plotly::as_widget(fig), file=Filename)
system(paste0("mv ", Filename, " ./04_Wiki_PolyInfo_04"))

######################################################
#CountDatRefine: Barplot 03
######################################################
fig <- plotly::plot_ly(CountDatRefine, x = ~No, y = ~AccEntityNum, type = 'bar', name = '',
                       hovertemplate = paste0('%{y}'),
                       marker = list(color = 'rgb(255,158,72)', line = list(color = 'rgb(8,48,107)', width = 0.25)))
fig <- fig %>% plotly::layout(title = paste0("Unique cumulative number of concepts"),
                              yaxis = list(title = 'Entity number', linewidth = 1, range=c(0,70000000)),
                              xaxis = list(title = "NES", ticks = "outside", linewidth = 0, tick0 = 1, dtick = 1),
                              margin = list(l=50, r=10, b=50, t=50, pad=4))
fig

Filename <- paste0("./Results_", format(Sys.time(), "%y%m%d"),"_07R.html")
htmlwidgets::saveWidget(plotly::as_widget(fig), file=Filename)
system(paste0("mv ", Filename, " ./04_Wiki_PolyInfo_04"))

######################################################
#Barplot 04
######################################################
CountDat$Refine.each_entity <- CountDatRefine$each_entity
CountDat$Refine.UniEntityNum <- CountDatRefine$UniEntityNum
CountDat$Refine.AccEntityNum <- CountDatRefine$AccEntityNum

fig <- plotly::plot_ly(CountDat, x = ~No, y = ~each_entity, type = 'bar', name = 'All candidates',
               hovertemplate = paste0('%{y}'),
               marker = list(color = 'rgb(158,202,225)', line = list(color = 'rgb(8,48,107)', width = 0.25)))
fig <- fig %>% add_trace(y = ~Refine.each_entity, name = 'Refinement', 
                         type = 'bar', marker = list(color = 'rgb(255,128,0)', size=8, line = list(color = 'rgb(8,48,107)', width = 0.5))) 
fig <- fig %>% plotly::layout(title = paste0("Number of ECU entities"),
                              bargap = 0.1, bargroupgap = 0.1,
                              yaxis = list(title = 'Entity number', linewidth = 1),
                              xaxis = list(title = "NES", ticks = "outside", linewidth = 0, tick0 = 1, dtick = 1),
                              margin = list(l=50, r=10, b=50, t=50, pad=4))
fig

if(!dir.exists("04_Wiki_PolyInfo_04")){dir.create("04_Wiki_PolyInfo_04")}
Filename <- paste0("./Results_", format(Sys.time(), "%y%m%d"),"_01R.html")
htmlwidgets::saveWidget(plotly::as_widget(fig), file=Filename)
system(paste0("mv ", Filename, " ./04_Wiki_PolyInfo_04"))

######################################################
#Barplot 05
######################################################
fig <- plotly::plot_ly(CountDat, x = ~No, y = ~UniEntityNum, type = 'bar', name = 'All candidates',
               hovertemplate = paste0('%{y}'),
               marker = list(color = 'rgb(158,202,225)', line = list(color = 'rgb(8,48,107)', width = 0.25)))
fig <- fig %>% add_trace(y = ~Refine.UniEntityNum, name = 'Refinement', 
                         type = 'bar', marker = list(color = 'rgb(255,128,0)', size=8, line = list(color = 'rgb(8,48,107)', width = 0.5))) 
fig <- fig %>% plotly::layout(title = paste0("Number of concepts per ENS (with dup.)"),
                              bargap = 0.1, bargroupgap = 0.1,
                              yaxis = list(title = 'Entity number', linewidth = 1, range=c(0,70000000)),
                              xaxis = list(title = "NES", ticks = "outside", linewidth = 0, tick0 = 1, dtick = 1),
                              margin = list(l=50, r=10, b=50, t=50, pad=4))
fig

Filename <- paste0("./Results_", format(Sys.time(), "%y%m%d"),"_02R.html")
htmlwidgets::saveWidget(plotly::as_widget(fig), file=Filename)
system(paste0("mv ", Filename, " ./04_Wiki_PolyInfo_04"))

######################################################
#Barplot 06
######################################################
fig <- plotly::plot_ly(CountDat, x = ~No, y = ~AccEntityNum, type = 'bar', name = 'All candidates',
               hovertemplate = paste0('%{y}'),
               marker = list(color = 'rgb(158,202,225)', line = list(color = 'rgb(8,48,107)', width = 0.25)))
fig <- fig %>% add_trace(y = ~Refine.AccEntityNum, name = 'Refinement', 
                         type = 'bar', marker = list(color = 'rgb(255,128,0)', size=8, line = list(color = 'rgb(8,48,107)', width = 0.5))) 
fig <- fig %>% plotly::layout(title = paste0("Unique cumulative number of concepts"),
                              bargap = 0.1, bargroupgap = 0.1,
                              yaxis = list(title = 'Entity number', linewidth = 1, range=c(0,70000000)),
                              xaxis = list(title = "NES", ticks = "outside", linewidth = 0, tick0 = 1, dtick = 1),
                              margin = list(l=50, r=10, b=50, t=50, pad=4))
fig

Filename <- paste0("./Results_", format(Sys.time(), "%y%m%d"),"_03R.html")
htmlwidgets::saveWidget(plotly::as_widget(fig), file=Filename)
system(paste0("mv ", Filename, " ./04_Wiki_PolyInfo_04"))

```

# Convert them to RDF format

In this step, the results extracted from Wikidata are converted to RDF.

Unnecessary strings were removed.

```{r echo=TRUE, eval=FALSE}
#File No
N <- 7

#Read All data after refinement
Dat <- data.frame(readr::read_csv(paste0("./04_Wiki_PolyInfo_06/Refinement_OutTriples_L", N, "R_Acc.csv"),
                                  show_col_types = FALSE, col_names=F))
colnames(Dat) <- c("Subject", "Property", "Object", "triple")
rownames(Dat) <- 1:nrow(Dat)
Dat <- Dat[as.numeric(rownames(unique(Dat["triple"]))),]

#remove the column of triple
head(Dat)
Dat00 <- Dat[,-4]
head(Dat00)
Dat00entity <- unique(c(Dat00$Subject, Dat00$Object))
head(Dat00entity)

#Labels
Labels <- readRDS("./04_Wiki_PolyInfo_00/Label_ja_All_label_df.Rds")
head(Labels)
Labels00 <- Labels[Labels$Subject %in% Dat00entity,]
head(Labels00)





```










