---
title: "Introduction to agGraphSearch"
author:
  - name: Satoshi Kume
date: "`r Sys.Date()`"
graphics: no
package: agGraphSearch, knitr, SPARQL
output:
  BiocStyle::html_document:
  toc_float: true
vignette: >
  %\VignetteIndexEntry{Introduction to agGraphSearch}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{agGraphSearch}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r style, echo = FALSE, results = 'asis', message=FALSE}
BiocStyle::markdown()
```

**Last modified:** `r file.info("agGraphSearch-introduction.Rmd")$mtime`<br />
**Compiled**: `r date()`

# Getting started

`r Rpackage("agGraphSearch")` is an R package distributed in kumeS's GitHub site.
To install the package, start R and enter:

```{r installation, echo=TRUE, eval=FALSE}
install.packages( "devtools" )
devtools::install_github( "kumeS/agGraphSearch" )
library( "agGraphSearch" )
```

Once `r Rpackage("agGraphSearch")` is installed, it can be loaded by the following command.

```{r library, echo=TRUE, eval=FALSE, message=FALSE}
library("agGraphSearch")
```

# Basic functions

- agCount_ID_Num

- agCount_ID_Prop_Obj

- agCount_Label_Num

- agIDtoLabel

- agWD_Alt

- agWD_ID_Prop_Obj

- PropertyPath

- agTableDT

- agVisNetwork

# Session information {.unnumbered}
```{r sessionInfo, echo=FALSE}
sessionInfo()
```
