---
title: "Workflow to use agGraphSearch and Mesh RDF: WF-002"
shorttitle: "WF-002: match labels to the Mesh data via SPARQL"
author:
  - name: Satoshi Kume
date: "`r Sys.Date()`"
graphics: no
package: agGraphSearch, knitr, SPARQL
output:
  BiocStyle::html_document:
  toc_float: true
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{agGraphSearch}
  %\VignetteIndexEntry{WF-002: match labels to the wikidata via SPARQL}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r style, echo=FALSE, message=FALSE, results='asis'}
BiocStyle::markdown()
```

**Last modified:** `r file.info("agGraphSearch-WF-002.Rmd")$mtime`<br />
**Compiled**: `r date()`

# Getting started

Once `r Rpackage("agGraphSearch")` is installed, it can be loaded by the following command.

```{r library, echo=TRUE, eval=FALSE}
#rm( list=ls() )
library(agGraphSearch)
library(magrittr)
#install.packages(c("knitr", "DT", "formattable", "filesstrings", "visNetwork", "networkD3", "igraph", "jsTree", "WikidataQueryServiceR"))
#BiocManager::install("BiocStyle")
#install.packages(c("stringdist"))

#Re-build
rm(list=ls())

if(F){
system("rm -rf ./agGraphSearch/NAMESPACE")
roxygen2::roxygenise("./agGraphSearch")
system("cat ./agGraphSearch/NAMESPACE")
remove.packages("agGraphSearch", lib=.libPaths())
.rs.restartR()
}
#install.packages(c("SPARQL", "franc", "formattable"))

if(F){
system("R CMD INSTALL agGraphSearch")
Sys.sleep(1)
library(agGraphSearch)
}

if(F){
proxy_url = "http://wwwproxy.osakac.ac.jp:8080"
Sys.setenv("http_proxy" = proxy_url)
Sys.setenv("https_proxy" = proxy_url)
Sys.setenv("ftp_proxy" = proxy_url)
}

if(F){
proxy_url = "http://wwwproxy.osakac.ac.jp:8080"
Sys.setenv("http_proxy" = proxy_url)
Sys.setenv("https_proxy" = proxy_url)
Sys.setenv("ftp_proxy" = proxy_url)
devtools::install_github( "kumeS/agGraphSearch" )
library(agGraphSearch)
}

if(F){
devtools::install_github( "kumeS/agGraphSearch" )
library(agGraphSearch)
}

if(!dir.exists("03_Mesh_OCR_00")){dir.create("03_Mesh_OCR_00")}
if(!dir.exists("03_Mesh_OCR_01_Out")){dir.create("03_Mesh_OCR_01_Out")}
if(!dir.exists("03_Mesh_OCR_02_Out")){dir.create("03_Mesh_OCR_02_Out")}
if(!dir.exists("03_Mesh_OCR_03_Out")){dir.create("03_Mesh_OCR_03_Out")}
if(!dir.exists("03_Mesh_OCR_04_Jpn")){dir.create("03_Mesh_OCR_04_Jpn")}
if(!dir.exists("03_Mesh_OCR_05_RDF")){dir.create("03_Mesh_OCR_05_RDF")}

```

# Read the csv files

You should split compound words as a pre-processing.

```{r echo=TRUE, eval=FALSE}
words <- data.frame(readr::read_csv("./03_Mesh_OCR_00/高分子辞典OCR_2column_en.csv", col_names = F, show_col_types = F))
words <- unlist(words, use.names = F)
words <- data.frame(X1=words[!is.na(words)])
dim(words)
```

# check the data

```{r echo=TRUE, eval=FALSE}
head(words)
dim(words)

#unique number
length(unique(words))

#table
head(words)
```

# Import Mesh data (2021)

```{r, echo=TRUE, eval=FALSE}

if(F){
MeshLabels <- readRDS("./03_Mesh_OCR_00/mesh_Label_en_dfR.Rds")
head(MeshLabels)
table(MeshLabels$Property)

MeshOthers <- readRDS("./03_Mesh_OCR_00/Mesh_othersR.Rds")
head(MeshOthers)
table(MeshOthers$Property)

MeshLabelsR <- MeshLabels[MeshLabels$Subject %in% unique(c(MeshOthers$Subject, MeshOthers$Object)),]
dim(MeshLabelsR)
saveRDS(MeshLabelsR, "./03_Mesh_OCR_00/MeshLabelsR.Rds")
}

```

# Linking of input words to the Mesh words

Input words in English are 408.

```{r echo=TRUE, eval=FALSE}
words <- unlist(words, use.names = F)
words <- words[!is.na(words)]
words <- words[words != ""]
words <- unique(words)

head(words)
length(unique(words))
words00 <- unique(unlist(words)); words00 <- words00[!is.na(words00)]
words01 <- unique(tolower(words00))
head(words01)

#小文字変換
MeshLabelsR <- readRDS("./03_Mesh_OCR_00/MeshLabelsR.Rds")
head(MeshLabelsR)
MeshLabels01 <- unique(tolower(MeshLabelsR$Object))
head(MeshLabels01)
length(MeshLabels01)

#文字列距離実行
library( agGraphSearch )
Dat <- ComputeDistance(InputTerms=words01,
                       RDFterms=MeshLabels01,
                       q=2, nthread=4, TopWords=3)
  
head(Dat)
#Dat[is.na(Dat)] <- 0
table(Dat$PerfectMatch > 0)
table(Dat$PartialMatch > 0)
table(Dat$cosine1 > 0)
table(Dat$cosine3 < 0.075)
#saveRDS(Dat, "./03_Mesh_OCR_01_Out/Dat_OCR_en_match.Rds")

```

#閾値0.075で切る

```{r echo=TRUE, eval=FALSE}
head(Dat)
words02 <- Dat[Dat$cosine3 < 0.075, ]
head(words02)
dim(words02)
rownames(words02) <- 1:nrow(words02)
#saveRDS(words02, "./03_Mesh_OCR_01_Out/Dat_OCR_en_words02.Rds")

```

# Translate English to Japanese

```{r echo=TRUE, eval=FALSE}
#rm(list=ls())
words02 <- readRDS("./03_Mesh_OCR_01_Out/Dat_OCR_en_words02.Rds")
head(words02)
dim(words02)

words02$Lab00 <- NA
head(words02)

#ラベルを逆にする
head(words02)
words02$Lab00 <- tolower(words02$cosine2)
words02$Lab01 <- NA
head(words02)

table(grepl("[,][ ]", words02$Lab00))
table(grepl("[,][ ]and", words02$Lab00))

for(n in 1:length(words02$Lab00)){
#n <- 5
if(grepl("[,][ ]", words02$Lab00[n])){
 aa <- strsplit(words02$Lab00[n], split = ", ")[[1]]
 words02$Lab01[n] <- paste(aa[length(aa):1], collapse = " ")
}else{
 aa <-  words02$Lab00[n]
 words02$Lab01[n] <- aa
}}
table(grepl("[,]", words02$Lab01))

words02$Jpn <- NA
head(words02, n=10)

#proxy at OECU
#rm( list=ls() )
if(T){
library(agGraphSearch)
library(magrittr)

proxy_url = "http://wwwproxy.osakac.ac.jp:8080"
Sys.setenv("http_proxy" = proxy_url)
Sys.setenv("https_proxy" = proxy_url)
Sys.setenv("ftp_proxy" = proxy_url)
}

##################################################################
#Translate to Jpn Labels
##################################################################
head(words02)
wordsTerms <- unique(words02$Terms)
str(wordsTerms)
for(n in 1:length(wordsTerms)){
#n <- 1
Result <- DeePL(Sentence=wordsTerms[n], Auth_Key="43725ffd-d3d3-a301-c92d-8d7e2070f71c:fx")
words02$Jpn[words02$Terms == wordsTerms[n]] <- Result
message(colourise(paste("  No.: ", n), fg = "green", bg = NULL))
message(colourise(paste("  ", wordsTerms[n], "=>", Result), fg = "green", bg = NULL))
}

head(words02, n=10)
tail(words02, n=10)
words02[is.na(words02)] <- 0

#PerfectMatch
a <- words02$PerfectMatch > 0
unique(words02$Terms[a])
sum(a)
#[1] 266

#PartialMatch
a <- words02$PartialMatch > 0
unique(words02$Terms[a])
sum(a)
#[1] 454

#cosine3
a <- words02$cosine3 < 0.075
unique(words02$Terms[a])
sum(a)
#[1] 493

##################################################################
#Save
#saveRDS(words02, "./03_Mesh_OCR_01_Out/OCR_en2jpn_words02.Rds")
#readr::write_excel_csv(words02, file="./03_Mesh_OCR_01_Out/OCR_en2jpn_words02.csv", col_names = T, append=F)
##################################################################
```

# Linking to the Mesh

```{r echo=TRUE, eval=FALSE}
#rm(list=ls())

#Match List
MeshLabelR <- readRDS("./03_Mesh_OCR_00/MeshLabelsR.Rds")
words02 <- readRDS("./03_Mesh_OCR_01_Out/OCR_en2jpn_words02.Rds")
head(words02)
dim(words02)

table(words02$cosine2 == words02$Lab00)
table(words02$cosine2 == words02$Lab01)

#Mesh D term List
MeshLabels00 <- MeshLabelR
head( MeshLabels00 )

dim( MeshLabels00 )
length(unique(MeshLabels00$Subject))
length(unique(MeshLabels00$Property))
length(unique(MeshLabels00$Object))

#Check
library( magrittr )

##################################################################
#Extract IDs
##################################################################
#一時的に小文字に変換してマッティング
##################################################################
MeshLabels01 <- MeshLabels00[c(tolower(MeshLabels00$Object) %in% tolower(words02$Lab00)),]

head(MeshLabels01)
dim(MeshLabels01)
length(unique(MeshLabels01$Subject))
length(unique(MeshLabels01$Property))
unique(MeshLabels01$Property)
length(unique(MeshLabels01$Object))
#491words/entities

MeshLabels01
LabList00 <- unique(MeshLabels01$Subject)
head(LabList00)
length(LabList00)
#saveRDS(LabList00, "./03_Mesh_OCR_01_Out/OCR_en_LabList00.Rds")

```

# Obtain all class hierarchy

```{r echo=TRUE, eval=FALSE}
#修正版の読み込み
#rm(list=ls())

#words
LabList00 <- readRDS("./03_Mesh_OCR_01_Out/OCR_en_LabList00.Rds")
LabList00
str(LabList00)

#MeshLabelsR.Rds
MeshLabelR <- readRDS("./03_Mesh_OCR_00/MeshLabelsR.Rds")

head(MeshLabelR); dim(MeshLabelR)
table(MeshLabelR$OtherInfo == "BLANK")
table(MeshLabelR$Property)
table(MeshLabelR$SubInfo)

#Mesh_othersR.Rds
MeshOthers <- readRDS("./03_Mesh_OCR_00/Mesh_othersR.Rds")

head(MeshOthers); dim(MeshOthers)
table(MeshOthers$OtherInfo == "BLANK")
table(MeshOthers$Property)
table(MeshOthers$SubInfo)
table(MeshOthers$ObjInfo)

##################################################################
#Trial 01
##################################################################
txt <- unique(LabList00)
a1 <- MeshLabelR[MeshLabelR$Subject %in% txt,]
a1
#              Subject   Property   Object OtherInfo    SubInfo
#1242522  mesh:D011108 rdfs:label Polymers       @en IDs:mesh:D
#1906322 mesh:M0017208 rdfs:label Polymers       @en IDs:mesh:M
a2 <- unique(a1$Subject)
a2

table(txt %in% a2)
##################################################################
#上位探索
##################################################################
Dat <- c(); x <- 1; Query <- a2
repeat{
message(x)
b1 <- MeshOthers[MeshOthers$Subject %in% Query,]
if(dim(b1)[1] == 0){break}
Dat <- rbind(Dat, b1)
Query <- b1$Object
x <- x + 1
if(x == 100){break}
}

##################################################################
#重複を除く
##################################################################
head(Dat); dim(Dat)
rownames(Dat) <- 1:nrow(Dat)
colnames(Dat) <- c("subject", "property", "parentClass", "OtherInfo", "SubInfo", "ObjInfo")
Dat$triple <- paste0(Dat$subject, ".", Dat$property, ".", Dat$parentClass)
Dat <- Dat[as.numeric(rownames(unique(Dat["triple"]))),]
Dat <- Dat[,-ncol(Dat)]
head(Dat); dim(Dat)
length(unique(c(Dat$subject, Dat$parentClass)))

##################################################################
#最上位
##################################################################
a3 <- unique(Dat$parentClass)[!(unique(Dat$parentClass) %in% unique(Dat$subject))]
str(a3)
a3

##################################################################
#Add labels
##################################################################
MeshLabelR <- readRDS("./03_Mesh_OCR_00/MeshLabelsR.Rds")

library(agGraphSearch)
library(magrittr)
DatX <- MergeMeshData(Data=Dat, Labels=MeshLabelR)
head(DatX)
dim(DatX)
length(unique(c(DatX$subject, DatX$parentClass)))
##################################################################
try(agVisNetwork(Graph=DatX,
             Selected=NULL, 
             Browse=TRUE, 
             Output=TRUE,
             ColoredSeed=LabList00,
             ColoredTopClass=a3,
             Physics=T,
             Smooth=T,
             FilePath="upClass_v01.html"))
filesstrings::move_files("upClass_v01.html", "./03_Mesh_OCR_02_Out")
##################################################################
for(n in 1:length(a3)){
print(n)
try(agJsTree(Data=DatX, 
         TopClass=a3[n], 
         Brouse=TRUE, 
         SaveHtmlFile=TRUE, 
         ExcludeQID=TRUE,
         FileName=paste0("agVisNetwork_upClass_", a3[n], ".html"), 
         Output="./03_Mesh_OCR_03_Out"))
}

##################################################################
#下位探索: 最上位から全部取得
##################################################################
Dat <- c(); x <- 1; Query <- a3
repeat{
message(x)
b2 <- MeshOthers[MeshOthers$Object %in% Query,]
if(dim(b2)[1] == 0){break}
Dat <- rbind(Dat, b2)
Query <- b2$Subject
x <- x + 1
if(x == 100){break}
}

#重複を除く
head(Dat); dim(Dat)
rownames(Dat) <- 1:nrow(Dat)
colnames(Dat) <- c("subject", "property", "parentClass", "OtherInfo", "SubInfo", "ObjInfo")
Dat$triple <- paste0(Dat$subject, ".", Dat$property, ".", Dat$parentClass)
Dat <- Dat[as.numeric(rownames(unique(Dat["triple"]))),]
Dat <- Dat[,-ncol(Dat)]

head(Dat); dim(Dat)
length(unique(c(Dat$subject, Dat$parentClass)))
#saveRDS(Dat, "./03_Mesh_OCR_01_Out/OCR_en_downClass.Rds")

##################################################################
#Bind data
##################################################################
#rm(list=ls())
MeshLabelR <- readRDS("./03_Mesh_OCR_00/MeshLabelsR.Rds")
upClass <- readRDS("./03_Mesh_OCR_01_Out/OCR_en_upClass.Rds")
downClass <- readRDS("./03_Mesh_OCR_01_Out/OCR_en_downClass.Rds")
Dat <- readRDS("./03_Mesh_OCR_01_Out/OCR_en_downClass.Rds")

#Add labels
#library(agGraphSearch)
Dat00 <- MergeMeshData(Data=Dat, Labels=MeshLabelR)

head(Dat00); dim(Dat00); table(Dat00$property)
table(Dat00$property)
#saveRDS(Dat00, "./03_Mesh_OCR_01_Out/OCR_Dat02.Rds")

##################################################################
##################################################################
#Jpn
##################################################################
##################################################################
head(Dat00)
DatJpn <- Dat00
dim(DatJpn)
colnames(DatJpn)

DatJpn$triple <- paste0(DatJpn$subject, ".", DatJpn$property, ".", DatJpn$parentClass)
rownames(DatJpn) <- 1:nrow(DatJpn)
DatJpn00 <- DatJpn[as.numeric(rownames(unique(DatJpn["triple"]))),]
DatJpn00 <- DatJpn00[,-ncol(DatJpn00)]
dim(DatJpn00)

DatJpn <- DatJpn00
table(DatJpn$property)
dim(DatJpn)
length(unique(c(DatJpn$subject, DatJpn$parentClass)))
length(unique(c(DatJpn$subjectLabel, DatJpn$parentClassLabel)))

#Translate to Jpn
if(F){
#proxy at OECU
#rm( list=ls() )
if(T){
library(agGraphSearch)
library(magrittr)

proxy_url = "http://wwwproxy.osakac.ac.jp:8080"
Sys.setenv("http_proxy" = proxy_url)
Sys.setenv("https_proxy" = proxy_url)
Sys.setenv("ftp_proxy" = proxy_url)
}

##################################################################
##################################################################
a <- readRDS("./03_Mesh_OCR_01_Out/OCR_DatJpn02.Rds")
head(a)
aa <- data.frame(IDs=c(a$subject, a$parentClass), Jpn=c(a$subjectLabel, a$parentClassLabel))
head(aa)
aa1 <- aa[as.numeric(rownames(unique(aa["IDs"]))),]
head(aa1); dim(aa1)
bb3_a <- readRDS("./bb3_a.Rds")
##################################################################
##################################################################
head(DatJpn); dim(DatJpn)
table(DatJpn$property)
length(unique(c(DatJpn$subject, DatJpn$parentClass)))
bb <- data.frame(IDs=c(DatJpn$subject, DatJpn$parentClass), Jpn=c(DatJpn$subjectLabel, DatJpn$parentClassLabel))
rownames(bb) <- 1:nrow(bb)
bb1 <- bb[as.numeric(rownames(unique(bb["IDs"]))),]
head(bb1); dim(bb1)

bb2 <- bb1[!(bb1$IDs %in% unique(c(aa1$IDs, bb3_a$IDs))),]

str(bb2)
dim(bb2)
length(unique(bb2$IDs))
head(bb2)

bb4 <- bb2
rownames(bb4) <- 1:nrow(bb4)
dim(bb4)
length(bb2$IDs)

##################################################################
#日本語訳
##################################################################
for(k in 7645:length(bb2$IDs)){
#k <- 1
wordsList <- bb2[k,2]
message(colourise(paste(k, "/", length(bb2$IDs)), fg = "blue", bg = NULL))
if(grepl("[,][ ]", wordsList) & !grepl("[,][ ]and", wordsList)){
a1 <- strsplit(wordsList, split = ", ")[[1]]
aa <- paste(a1[length(a1):1], collapse = " ")
}else{
aa <-  wordsList
}

#43725ffd-d3d3-a301-c92d-8d7e2070f71c:fx
#7a2cdd89-60a7-d251-8090-2f6f40293dd6:fx
Jpn <- DeePL(aa, Auth_Key="7a2cdd89-60a7-d251-8090-2f6f40293dd6:fx")
bb4[k,2] <- Jpn
message(colourise(paste("  ", wordsList, "=>", Jpn), fg = "green", bg = NULL))
}

#23439から家で
#saveRDS(bb4, "./bb4_jpn.Rds")
##################################################################
##################################################################
#日本語リスト
##################################################################
head(aa1);dim(aa1)
head(bb4);dim(bb4)

bb3_a <- readRDS("./bb3_a.Rds")
dd <- aa1 %>% rbind(bb3_a) %>% rbind(bb4)

rownames(dd) <- 1:nrow(dd)
head(dd);dim(dd)
length(unique(dd$IDs))
##################################################################
##################################################################
#代入
##################################################################
DatJpn01 <- DatJpn
head(DatJpn01); dim(DatJpn01)
head(dd); dim(dd)
length(unique(c(DatJpn01$subject, DatJpn01$parentClass)))

for(n in 1:nrow(dd)){
  #n <- 1
  DatJpn01$subjectLabel[DatJpn01$subject == dd$IDs[n]] <- dd$Jpn[n]
  DatJpn01$parentClassLabel[DatJpn01$parentClass == dd$IDs[n]] <- dd$Jpn[n]
}
#head(DatJpn01)
DatJpn03 <- DatJpn01
DatJpn03 <- DatJpn03[DatJpn03$property != "meshv:preferredConcept",]
#DatJpn03 <- DatJpn03[DatJpn03$property != "meshv:preferredConceptR",]
head(DatJpn03); dim(DatJpn03)
length(unique(c(DatJpn03$subject, DatJpn03$parentClass)))
#Save
#saveRDS(DatJpn03, "./03_Mesh_OCR_01_Out/OCR_DatJpn03_new.Rds")
}

##################################################################
#個別にグラフ化
##################################################################
#rm( list=ls() )
DatJpn03 <- readRDS("./03_Mesh_OCR_01_Out/OCR_DatJpn03_new.Rds")
topClass <- unique(DatJpn03$parentClass)[!(unique(DatJpn03$parentClass) %in% unique(DatJpn03$subject))]
LabList00 <- readRDS("./03_Mesh_OCR_01_Out/OCR_en_LabList00.Rds")

for(k in 1:length(topClass)){
#k <- 1
Dat <- c(); x <- 1; Query <- topClass[k]

repeat{
b2 <- DatJpn03[DatJpn03$parentClass %in% Query,]
if(dim(b2)[1] == 0){break}
Dat <- rbind(Dat, b2)
Query <- b2$subject
message(x)
x <- x + 1
if(x == 100){break}
}

head(Dat)
rownames(Dat) <- 1:nrow(Dat)
Dat$triple <- paste0(Dat$subject, ".", Dat$property, ".", Dat$parentClass)
Dat00 <- Dat[as.numeric(rownames(unique(Dat["triple"]))),]
Dat <- Dat00[,-ncol(Dat00)]
dim(Dat)

a <- DatJpn03[DatJpn03$parentClass %in% topClass[k],]
FileName <- paste0("agVisNetwork_OCR_Jpn_", topClass[k], "_",
                   a$parentClassLabel[1], "_", format(Sys.time(), "%y%m%d-%H%M%S"),".html")

##################################################################
#All: 検索エンティティをyellowに
##################################################################
try(agVisNetwork(Graph=Dat,
             Selected=NULL, 
             Browse=TRUE, 
             Output=TRUE,
             ColoredSeed=LabList00,
             ColoredTopClass=topClass,
             FilePath=FileName))
#table(LabList00 == "mesh:D000937")
suppressMessages(filesstrings::move_files(FileName, "./03_Mesh_OCR_04_Jpn"))
}

##################################################################
#ツリー可視化
##################################################################
head(DatJpn03)
agJsTreeR(Data=DatJpn03,
          TopClass=topClass,
          Brouse=TRUE,
          SaveHtmlFile=TRUE,
          FileName="ExtractedMesh_tree.html",
          Output=NULL,
          ExcludeQID=TRUE)

```

# Convert to RDF

Meshから抽出した結果のRDF変換

```{r echo=TRUE, eval=FALSE}
#rm(list=ls())
Dat02 <- readRDS("./03_Mesh_OCR_01_Out/OCR_Dat02.Rds")
DatJpn03 <- readRDS("./03_Mesh_OCR_01_Out/OCR_DatJpn03_new.Rds")
topClass <- unique(DatJpn03$parentClass)[!(unique(DatJpn03$parentClass) %in% unique(DatJpn03$subject))]
LabList00 <- readRDS("./03_Mesh_OCR_01_Out/OCR_en_LabList00.Rds")

#SPARQL結果をN-triplesに変換

if(T){
#クラス階層
a <- DatJpn03
b <- Dat02
  
##NA対応
table(is.na(a))

#ループ消す
head(a)
table(a$subject != a$parentClass)
a <- a[a$subject != a$parentClass, ]

#table(grepl("mesh[:]", a$subject))
#table(grepl("mesh[:]", a$parentClass))

nt <- paste("<", sub("mesh[:]", "http://id.nlm.nih.gov/mesh/", a$subject), "> ",
            "<http://www.w3.org/2000/01/rdf-schema#subClassOf> ",
            "<", sub("mesh[:]", "http://id.nlm.nih.gov/mesh/", a$parentClass), "> .",
            sep="")
nt <- unique(nt)

write.table(nt, "./03_Mesh_OCR_05_RDF/RDF_from_mesh_v01.nt", sep="",
             row.names = F, col.names = F, append=F, quote = F)

colnames(a)

#Labels: a
nt <- paste('<', sub("mesh[:]", "http://id.nlm.nih.gov/mesh/", a$subject), '> ',
            '<http://www.w3.org/2000/01/rdf-schema#label> ',
            '"', a$subjectLabel, '"@ja.',
            sep="")
nt <- unique(nt)
write.table(nt, "./03_Mesh_OCR_05_RDF/RDF_from_mesh_v01.nt", sep="",
             row.names = F, col.names = F, append=T, quote = F)

nt <- paste('<', sub("mesh[:]", "http://id.nlm.nih.gov/mesh/", a$parentClass), '> ',
            '<http://www.w3.org/2000/01/rdf-schema#label> ',
            '"', a$parentClassLabel, '"@ja.',
            sep="")
nt <- unique(nt)
write.table(nt, "./03_Mesh_OCR_05_RDF/RDF_from_mesh_v01.nt", sep="",
             row.names = F, col.names = F, append=T, quote = F)

#Labels: b
#head(b)
nt <- paste('<', sub("mesh[:]", "http://id.nlm.nih.gov/mesh/", b$subject), '> ',
            '<http://www.w3.org/2000/01/rdf-schema#label> ',
            '"', b$subjectLabel, '"@en.',
            sep="")
nt <- unique(nt)
write.table(nt, "./03_Mesh_OCR_05_RDF/RDF_from_mesh_v01.nt", sep="",
             row.names = F, col.names = F, append=T, quote = F)

nt <- paste('<', sub("mesh[:]", "http://id.nlm.nih.gov/mesh/", b$parentClass), '> ',
            '<http://www.w3.org/2000/01/rdf-schema#label> ',
            '"', b$parentClassLabel, '"@en.',
            sep="")
nt <- unique(nt)
write.table(nt, "./03_Mesh_OCR_05_RDF/RDF_from_mesh_v01.nt", sep="",
             row.names = F, col.names = F, append=T, quote = F)
}

if(T){
#検索エンティティ
cc <- LabList00
nt <- paste('<', sub("mesh[:]", "http://id.nlm.nih.gov/mesh/", cc), '> ',
            '<http://www.w3.org/1999/02/22-rdf-syntax-ns#type> <http://class/search> .',
            sep="")
nt <- unique(nt)
write.table(nt, "./03_Mesh_OCR_05_RDF/RDF_from_mesh_v01.nt", sep="",
             row.names = F, col.names = F, append=T, quote = F)


#最上位エンティティ
d <- topClass
nt <- paste('<', sub("mesh[:]", "http://id.nlm.nih.gov/mesh/", d), '> ',
            '<http://www.w3.org/1999/02/22-rdf-syntax-ns#type> <http://class/top> .',
            sep="")
nt <- unique(nt)
write.table(nt, "./03_Mesh_OCR_05_RDF/RDF_from_mesh_v01.nt", sep="",
             row.names = F, col.names = F, append=T, quote = F)

}

##################################################################
#集計・重複除去
e <- readLines("./03_Mesh_OCR_05_RDF/RDF_from_mesh_v01.nt")
str(e)
length(unique(e))
##################################################################
#保存
write.table(data.frame(X=unique(e)), 
            "./03_Mesh_OCR_05_RDF/RDF_from_mesh_v01R.nt", sep="",
             row.names = F, col.names = F, append=F, quote = F)
##################################################################

```

## Summary

Mesh RDFからクラス階層を抽出した結果

1. 高分子辞典のOCR語彙を使用

初期入力語彙: 4520語彙（高分子辞典 英語の語彙のみ）

2. Mesh RDFの語彙(英語)とエンティティリンキング(コサイン類似度)

エンティティリンキング後: 491 エンティティ

上位展開して、最上位エンティティ: 69 エンティティ

下位展開した結果: 49127 エンティティ / 57359トリプル

```{r echo=TRUE, eval=FALSE}
#dim(DatJpn03)
#length(unique(c(DatJpn03$subject, DatJpn03$parentClass)))
#table(topClass %in% a3)


```


