---
title: "A workflow to use agGraphSearch and ChEBI RDF"
shorttitle: "Application to the class hierarchy of ChEBI RDF"
author:
  - name: Satoshi Kume
date: "`r Sys.Date()`"
graphics: no
package: agGraphSearch, knitr, SPARQL
output:
  BiocStyle::html_document:
  toc_float: true
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{agGraphSearch}
  %\VignetteIndexEntry{A workflow to use agGraphSearch and ChEBI RDF}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r style, echo=FALSE, message=FALSE, results='asis'}
BiocStyle::markdown()
```

**Last modified:** `r file.info("agGraphSearch-ChEBI-WF-PolymerDic.Rmd")$mtime`<br />
**Compiled**: `r Sys.time()`

# Getting started

Once `r Rpackage("agGraphSearch")` is installed, it can be loaded by the following command.

```{r library, echo=TRUE, eval=FALSE}
#rm( list=ls() )
library(agGraphSearch)
library(magrittr)

#Re-build
rm(list=ls())

if(F){
system("rm -rf ./agGraphSearch/NAMESPACE")
roxygen2::roxygenise("./agGraphSearch")
system("cat ./agGraphSearch/NAMESPACE")
remove.packages("agGraphSearch", lib=.libPaths())
.rs.restartR()
}
#install.packages(c("SPARQL", "franc", "formattable"))

if(F){
system("R CMD INSTALL agGraphSearch")
Sys.sleep(1)
library(agGraphSearch)
}

if(F){
devtools::install_github( "kumeS/agGraphSearch" )
library(agGraphSearch)
}

if(!dir.exists("05_ChEBI_OCR_00")){dir.create("05_ChEBI_OCR_00")}
if(!dir.exists("05_ChEBI_OCR_01_Out")){dir.create("05_ChEBI_OCR_01_Out")}
if(!dir.exists("05_ChEBI_OCR_02_Out")){dir.create("05_ChEBI_OCR_02_Out")}
if(!dir.exists("05_ChEBI_OCR_03_Out")){dir.create("05_ChEBI_OCR_03_Out")}
if(!dir.exists("05_ChEBI_OCR_04_Jpn")){dir.create("05_ChEBI_OCR_04_Jpn")}
if(!dir.exists("05_ChEBI_OCR_05_RDF")){dir.create("05_ChEBI_OCR_05_RDF")}

```

# Read the csv files

You should split compound words as a pre-processing.

```{r echo=TRUE, eval=FALSE}
words <- data.frame(readr::read_csv("./05_ChEBI_OCR_00/高分子辞典OCR_2column_en.csv", col_names = F, show_col_types = F))
words <- unlist(words, use.names = F)
words <- data.frame(X1=words[!is.na(words)])
dim(words)
```

# check the data

```{r echo=TRUE, eval=FALSE}
head(words)
dim(words)

#unique number
length(unique(words))

#table
head(words)
```

# Import ChEBI data (2021)

```{r, echo=TRUE, eval=FALSE}
if(F){
ChEBILabels <- readRDS("./05_ChEBI_OCR_00/ChEBI_Label_en_rdfs_df.Rds")
head(ChEBILabels)
table(ChEBILabels$Property)
dim(ChEBILabels)
#[1] 147547      4
length(unique(ChEBILabels$Object))
#ChEBILabels[ChEBILabels$Subject == "owl:Thing",]

ChEBIrelation <- readRDS("./05_ChEBI_OCR_00/ChEBI_Relation_subClassOf_df.Rds")
head(ChEBIrelation)
table(ChEBIrelation$Property)
dim(ChEBIrelation)
#[1] 216757      3
length(unique(c(ChEBILabels$Subject, ChEBILabels$Object)))
#[1] 295094

#Remove owl:Thing class
ChEBIrelationR <- ChEBIrelation[ChEBIrelation$Subject %in% unique(ChEBILabels$Subject),]
ChEBIrelationR[!ChEBIrelationR$Object %in% unique(ChEBILabels$Subject),]
#               Subject        Property    Object
#59996  obo:CHEBI_50906 rdfs:subClassOf owl:Thing
#115628 obo:CHEBI_36342 rdfs:subClassOf owl:Thing
#146360 obo:CHEBI_24431 rdfs:subClassOf owl:Thing
ChEBIrelationR <- ChEBIrelationR[ChEBIrelationR$Object %in% unique(ChEBILabels$Subject),]
saveRDS(ChEBIrelationR, "./05_ChEBI_OCR_00/ChEBIrelationR.Rds")

ChEBILabelsR <- ChEBILabels[ChEBILabels$Subject %in% unique(c(ChEBIrelation$Subject, ChEBIrelation$Object)),]
head(ChEBILabelsR)
dim(ChEBILabelsR)
#[1] 147458      4

saveRDS(ChEBILabelsR, "./05_ChEBI_OCR_00/ChEBILabelsR.Rds")

}

```

# Linking of input words to the ChEBI words

Input words in English are 4520

```{r echo=TRUE, eval=FALSE}
words <- unlist(words, use.names = F)
words <- words[!is.na(words)]
words <- words[words != ""]
words <- unique(words)

head(words)
length(unique(words))
words00 <- unique(unlist(words)); words00 <- words00[!is.na(words00)]
words01 <- unique(tolower(words00))
head(words01)
length(unique(words01))

#Lower-case conversion
ChEBILabelsR <- readRDS("./05_ChEBI_OCR_00/ChEBILabelsR.Rds")
head(ChEBILabelsR)
ChEBILabels01 <- unique(tolower(ChEBILabelsR$Object))
head(ChEBILabels01)
length(ChEBILabels01)

#String distance execution
library( agGraphSearch )
Dat <- ComputeDistance(InputTerms=words01,
                       RDFterms=ChEBILabels01,
                       q=2, nthread=4, TopWords=3)
  
head(Dat)
#Dat[is.na(Dat)] <- 0
table(Dat$PerfectMatch > 0)
table(Dat$PartialMatch > 0)
table(Dat$cosine1 > 0)
table(Dat$cosine3 < 0.075)
#saveRDS(Dat, "./05_ChEBI_OCR_01_Out/Dat_OCR_en_match.Rds")

```

```{r echo=TRUE, eval=TRUE}
library(agGraphSearch)
a <- readRDS("../..//05_ChEBI_OCR_01_Out/Dat_OCR_en_match.Rds")
agGraphSearch::agTableDT(a, Output=F)
```

# Set the threshold at 0.075

```{r echo=TRUE, eval=FALSE}
head(Dat)
words02 <- Dat[Dat$cosine3 < 0.075, ]
head(words02)
dim(words02)
rownames(words02) <- 1:nrow(words02)
#saveRDS(words02, "./05_ChEBI_OCR_01_Out/Dat_OCR_en_words02.Rds")

```

# Translate English to Japanese

```{r echo=TRUE, eval=FALSE}
#rm(list=ls())
words02 <- readRDS("./05_ChEBI_OCR_01_Out/Dat_OCR_en_words02.Rds")
head(words02)
dim(words02)

#proxy at OECU
if(F){
library(agGraphSearch)
library(magrittr)

proxy_url = "http://wwwproxy.osakac.ac.jp:8080"
Sys.setenv("http_proxy" = proxy_url)
Sys.setenv("https_proxy" = proxy_url)
Sys.setenv("ftp_proxy" = proxy_url)

}

##################################################################
#Translate to Jpn Labels
##################################################################
head(words02)
source(system.file("inst/script/DeePL.R", package="agGraphSearch"))
words03 <- Trans2Jpn(words02)

head(words03, n=10)
tail(words03, n=10)
table(is.na(words03))
words03[is.na(words03)] <- 0

#PerfectMatch
a <- words03$PerfectMatch > 0
unique(words03$Terms[a])
sum(a)
#[1] 198

#PartialMatch
a <- words03$PartialMatch > 0
unique(words03$Terms[a])
sum(a)
#[1] 202

#cosine3
a <- words03$cosine3 < 0.075
unique(words03$Terms[a])
sum(a)
#[1] 242

##################################################################
#Save
#saveRDS(words03, "./05_ChEBI_OCR_01_Out/OCR_en2jpn_words03.Rds")
#readr::write_excel_csv(words03, file="./05_ChEBI_OCR_01_Out/OCR_en2jpn_words03.csv", col_names = T, append=F)
##################################################################
```

```{r echo=TRUE, eval=TRUE}
library(agGraphSearch)
a <- readRDS("../../05_ChEBI_OCR_01_Out/OCR_en2jpn_words03.Rds")
#a <- readRDS("./05_ChEBI_OCR_01_Out/OCR_en2jpn_words03.Rds")
agGraphSearch::agTableFM(a, Output=F)
```

# Linking to the ChEBI

```{r echo=TRUE, eval=FALSE}
#rm(list=ls())

#Match List
ChEBILabelR <- readRDS("./05_ChEBI_OCR_00/ChEBILabelsR.Rds")
words03 <- readRDS("./05_ChEBI_OCR_01_Out/OCR_en2jpn_words03.Rds")
head(words03)
dim(words03)

#ChEBI term List
ChEBILabels00 <- ChEBILabelR
head( ChEBILabels00 )

dim( ChEBILabels00 )
length(unique(ChEBILabels00$Subject))
length(unique(ChEBILabels00$Property))
length(unique(ChEBILabels00$Object))

#Check
library( magrittr )

##################################################################
#Extract IDs
##################################################################
#Temporarily converted to lowercase and then matched
##################################################################
ChEBILabels01 <- ChEBILabels00[c(tolower(ChEBILabels00$Object) %in% tolower(words03$cosine2)),]

head(ChEBILabels01)
dim(ChEBILabels01)
length(unique(ChEBILabels01$Subject))
#[1] 237
length(unique(ChEBILabels01$Property))
#[1] 1
unique(ChEBILabels01$Property)
#[1] "rdfs:label"
length(unique(ChEBILabels01$Object))
#237 words / all entities

head(ChEBILabels01)
LabList00 <- unique(ChEBILabels01$Subject)
head(LabList00)
#[1] "obo:CHEBI_59827" "obo:CHEBI_29365" "obo:CHEBI_35366" "obo:CHEBI_7044"  "obo:CHEBI_16412"
#[6] "obo:CHEBI_16646"
length(LabList00)
#[1] 237
#saveRDS(LabList00, "./05_ChEBI_OCR_01_Out/OCR_en_LabList00.Rds")

```

# Obtain all class hierarchy

```{r echo=TRUE, eval=FALSE}
#rm(list=ls())

#words
LabList00 <- readRDS("./05_ChEBI_OCR_01_Out/OCR_en_LabList00.Rds")
LabList00
str(LabList00)

#ChEBILabelsR.Rds
ChEBILabelR <- readRDS("./05_ChEBI_OCR_00/ChEBILabelsR.Rds")

head(ChEBILabelR); dim(ChEBILabelR)
table(ChEBILabelR$OtherInfo == "BLANK")
table(ChEBILabelR$Property)
table(ChEBILabelR$OtherInfo)

#ChEBIrelationR.Rds
ChEBIrelation <- readRDS("./05_ChEBI_OCR_00/ChEBIrelationR.Rds")

head(ChEBIrelation); dim(ChEBIrelation)
table(ChEBIrelation$Property)

##################################################################
#Trial 01
##################################################################
txt <- unique(LabList00)
a1 <- ChEBILabelR[ChEBILabelR$Subject %in% txt,]
head(a1, n=3)
#             Subject   Property         Object  OtherInfo
#1732 obo:CHEBI_59827 rdfs:label silsesquioxane xsd:string
#1735 obo:CHEBI_29365 rdfs:label       phosgene xsd:string
#1988 obo:CHEBI_35366 rdfs:label     fatty acid xsd:string
a2 <- unique(a1$Subject)
a2

table(txt %in% a2)
##################################################################
#Search for superordinate concepts
##################################################################
source(system.file("inst/script/searchChEBI.R", package="agGraphSearch"))
Dat <- searchSuperordinate(a2=a2, ChEBIrelation=ChEBIrelation)
head(Dat)
#saveRDS(Dat, "./05_ChEBI_OCR_01_Out/OCR_en_upClass.Rds")

##################################################################
#Find the top-level entities
##################################################################
a3 <- unique(Dat$parentClass)[!(unique(Dat$parentClass) %in% unique(Dat$subject))]
str(a3)
a3
#[1] "obo:CHEBI_50906" "obo:CHEBI_24431"

##################################################################
#Add labels
##################################################################
ChEBILabelR <- readRDS("./05_ChEBI_OCR_00/ChEBILabelsR.Rds")

library(agGraphSearch)
library(magrittr)

DatX <- MergeChEBIData(Data=Dat, Labels=ChEBILabelR)
head(DatX)
dim(DatX)
length(unique(c(DatX$subject, DatX$parentClass)))

##################################################################
try(agVisNetwork(Graph=DatX,
                 Selected=NULL, 
                 Browse=TRUE, 
                 Output=TRUE,
                 ColoredSeed=LabList00,
                 ColoredTopClass=a3,
                 Physics=T,
                 Smooth=T,
                 FilePath="upClass_v01.html"))
filesstrings::move_files("upClass_v01.html", "./05_ChEBI_OCR_02_Out")
##################################################################
for(n in 1:length(a3)){
print(n)
try(agJsTree(Data=DatX, 
         TopClass=gsub(" ", "_", paste0(DatX[DatX$parentClass %in% a3[n],]$parentClassLabel[1], ".", DatX[DatX$parentClass %in% a3[n],]$parentClass[1])), 
         Brouse=TRUE, 
         SaveHtmlFile=TRUE, 
         ExcludeQID=TRUE,
         FileName=paste0("agVisNetwork_upClass_", a3[n], ".html"), 
         Output="./05_ChEBI_OCR_03_Out"))
}

##################################################################
#Search for lower-level concepts: get everything from the top level
##################################################################
Dat <- searchSubordinate(a3=a3, ChEBIrelation=ChEBIrelation)
head(Dat)
dim(Dat)
#saveRDS(Dat, "./05_ChEBI_OCR_01_Out/OCR_en_downClass.Rds")
```

```{r echo=TRUE, eval=TRUE}
library(agGraphSearch)
library(magrittr)
##################################################################
Dat <- readRDS("../../05_ChEBI_OCR_01_Out/OCR_en_upClass.Rds")
ChEBILabelR <- readRDS("../../05_ChEBI_OCR_00/ChEBILabelsR.Rds")
LabList00 <- readRDS("../../05_ChEBI_OCR_01_Out/OCR_en_LabList00.Rds")
DatX <- MergeChEBIData(Data=Dat, Labels=ChEBILabelR)
##################################################################
try(agVisNetwork(Graph=DatX,
                 Selected=NULL, 
                 Browse=TRUE, 
                 Output=FALSE,
                 ColoredSeed=LabList00,
                 ColoredTopClass="",
                 Physics=T,
                 Smooth=T,
                 FilePath="upClass_v01.html"))
```

# Bind data

```{r echo=TRUE, eval=FALSE}
#rm(list=ls())
ChEBILabelR <- readRDS("./05_ChEBI_OCR_00/ChEBILabelsR.Rds")
upClass <- readRDS("./05_ChEBI_OCR_01_Out/OCR_en_upClass.Rds")
downClass <- readRDS("./05_ChEBI_OCR_01_Out/OCR_en_downClass.Rds")
#head(upClass); head(downClass)
Dat <- rbind(upClass, downClass)

#Add labels
library(agGraphSearch)
Dat00 <- MergeChEBIData(Data=Dat, Labels=ChEBILabelR)

head(Dat00); dim(Dat00); table(Dat00$property)
table(Dat00$property)
table(is.na(Dat00))

#saveRDS(Dat00, "./05_ChEBI_OCR_01_Out/OCR_Dat02.Rds")
#hist(table(nchar(Dat00$subjectLabel)))

Dat00 <- readRDS("./05_ChEBI_OCR_01_Out/OCR_Dat02.Rds")
head(Dat00)

#entity number
length(unique(c(Dat00$subject, Dat00$parentClass)))
#[1] 147421

#triple number
table(Dat00$property)
#rdfs:subClassOf 
#        216709

```

# Convert to RDF (N-triples)

ChEBIから抽出した結果(ほぼ全て)をRDF(N-triples)に変換する

ラベル数が多くて、日本語変換はできない。

今後、Wikidataのやり方をChEBIに用いる予定。

```{r echo=TRUE, eval=FALSE}
#rm(list=ls())
Dat02 <- readRDS("./05_ChEBI_OCR_01_Out/OCR_Dat02.Rds")
LabList00 <- readRDS("./05_ChEBI_OCR_01_Out/OCR_en_LabList00.Rds")

#Convert the extracted results to N-triples

if(T){
#class hierarchy
b <- Dat02
head(b)

##Check NA
table(is.na(b))

#Remove the loops
head(b)
table(b$subject != b$parentClass)
b <- b[b$subject != b$parentClass, ]

#table(grepl("obo[:]", b$subject))
#table(grepl("obo[:]", b$parentClass))

nt <- paste("<", sub("mesh[:]", "http://id.nlm.nih.gov/mesh/", a$subject), "> ",
            "<http://www.w3.org/2000/01/rdf-schema#subClassOf> ",
            "<", sub("mesh[:]", "http://id.nlm.nih.gov/mesh/", a$parentClass), "> .",
            sep="")
nt <- unique(nt)

write.table(nt, "./03_Mesh_OCR_05_RDF/RDF_from_mesh_v01.nt", sep="",
             row.names = F, col.names = F, append=F, quote = F)

colnames(a)


#Labels: b
nt <- paste0('<', sub("obo[:]", "http://purl.obolibrary.org/obo/", b$subject), '> ',
            '<http://www.w3.org/2000/01/rdf-schema#label> ',
            '"', b$subjectLabel, '"@en.')
nt <- unique(nt)
write.table(nt, "./05_ChEBI_OCR_05_RDF/RDF_from_ChEBI_v01.nt", sep="",
             row.names = F, col.names = F, append=T, quote = F)

nt <- paste0('<', sub("obo[:]", "http://purl.obolibrary.org/obo/", b$parentClass), '> ',
            '<http://www.w3.org/2000/01/rdf-schema#label> ',
            '"', b$parentClassLabel, '"@en.')
nt <- unique(nt)
write.table(nt, "./05_ChEBI_OCR_05_RDF/RDF_from_ChEBI_v01.nt", sep="",
             row.names = F, col.names = F, append=T, quote = F)
}

if(T){
#検索エンティティ
cc <- LabList00
nt <- paste('<', sub("ChEBI[:]", "http://id.nlm.nih.gov/ChEBI/", cc), '> ',
            '<http://www.w3.org/1999/02/22-rdf-syntax-ns#type> <http://class/search> .',
            sep="")
nt <- unique(nt)
write.table(nt, "./05_ChEBI_OCR_05_RDF/RDF_from_ChEBI_v01.nt", sep="",
             row.names = F, col.names = F, append=T, quote = F)


#最上位エンティティ
d <- topClass
nt <- paste('<', sub("ChEBI[:]", "http://id.nlm.nih.gov/ChEBI/", d), '> ',
            '<http://www.w3.org/1999/02/22-rdf-syntax-ns#type> <http://class/top> .',
            sep="")
nt <- unique(nt)
write.table(nt, "./05_ChEBI_OCR_05_RDF/RDF_from_ChEBI_v01.nt", sep="",
             row.names = F, col.names = F, append=T, quote = F)

}

##################################################################
#集計・重複除去
e <- readLines("./05_ChEBI_OCR_05_RDF/RDF_from_ChEBI_v01.nt")
str(e)
length(unique(e))
##################################################################
#保存
write.table(data.frame(X=unique(e)), 
            "./05_ChEBI_OCR_05_RDF/RDF_from_ChEBI_v01R.nt", sep="",
             row.names = F, col.names = F, append=F, quote = F)
##################################################################

```

## Summary

ChEBI RDFからクラス階層を抽出した結果

1. 高分子辞典のOCR語彙を使用

初期入力語彙: 4520語彙（高分子辞典 英語の語彙のみ）

2. ChEBI RDFの語彙(英語)とエンティティリンキング(コサイン類似度)

エンティティリンキング後: 237 エンティティ

上位展開して、最上位エンティティ: 2 エンティティ

下位展開した結果: 147421 エンティティ / 57359トリプル

```{r echo=TRUE, eval=FALSE}
#dim(DatJpn03)
#length(unique(c(DatJpn03$subject, DatJpn03$parentClass)))
#table(topClass %in% a3)


```


