---
title: "Introduction to agGraphSearch"
author:
  - name: Satoshi Kume
date: "`r Sys.Date()`"
graphics: no
package: agGraphSearch, knitr, SPARQL
output:
  BiocStyle::html_document:
  toc_float: true
vignette: >
  %\VignetteIndexEntry{Introduction to agGraphSearch}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{agGraphSearch}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r style, echo = FALSE, results = 'asis', message=FALSE}
BiocStyle::markdown()
```

**Last modified:** `r file.info("agGraphSearch-installation.Rmd")$mtime`<br/>
**Compiled**: `r date()`

# Getting started

`r Rpackage("agGraphSearch")` is an R package distributed in kumeS's GitHub site.
To install the package, start R and enter:

```{r installation, echo=TRUE, eval=FALSE}
#Still can not be installation (14 May 2021)
install.packages( "devtools" )
devtools::install_github( "kumeS/agGraphSearch" )
library( "agGraphSearch" )
```

Once `r Rpackage("agGraphSearch")` is installed, it can be loaded by the following command.

```{r library, echo=TRUE, eval=FALSE, message=FALSE}
library("agGraphSearch")
```

Optionally, you use the following command if you want to use the docker environment.

```sh
# On Terminal
docker run \
       -d \
       --name RStudio \
       -v $(pwd)/XXX:/home/rstudio/XXX \
       -e ROOT=TRUE \
       -e PASSWORD=PassWord \
       -p 8787:8787 \
       rocker/rstudio:4.0.5
```

```r
# On R
system("docker run \\
        -d \\
        --name RStudio \\
        -v $(pwd)/XXX:/home/rstudio/XXX \\
        -e ROOT=TRUE \\
        -e PASSWORD=PassWord \\
        -p 8787:8787 \\
       rocker/rstudio:4.0.5")
```

See DockerHub if you want to know details to the docker image.

https://hub.docker.com/r/rocker/rstudio

Then, browse the GitHub page (`http://localhost:8787`).

```r
## run first on the terminal windows
#sudo apt-get update
#sudo apt-get install libxml2-dev libglpk-dev

install.packages("BiocManager")
BiocManager::install("BiocStyle")

devtools::install_github( "kumeS/agGraphSearch" )
#will get something error, then

system( "git clone https://github.com/kumeS/agGraphSearch.git" )
system( "R CMD INSTALL agGraphSearch" )
library( "agGraphSearch" )

```

- memo: Remove All packages

  - remove.packages( installed.packages( priority = "NA" )[,1] )

# Basic functions

- Generation functions for SPARQL Query 

  - agCount_ID_Num

    - agCount_ID_Num_Wikidata_QID_P279_P31.R
    
  - agCount_ID_Prop_Obj

    - agCount_ID_Prop_Obj_Wikidata_vO
    
    - agCount_ID_Prop_Obj_Wikidata_vP
  
  - agWD_Alt_Wikidata
  
    - agWD_ID_Prop_Obj_Wikidata_vO

  - agCount_Label_Num

    - agCount_Label_Num_Wikidata_P279_P31
    
  - agIDtoLabel
  
    - agIDtoLabel_Wikidata

  - agWD_ID_Prop_Obj

    - agWD_ID_Prop_Obj_Wikidata_vO
    
  - agWD_Alt
  
    - agWD_Alt_Wikidata
    
  - PropertyPath
  
    - PropertyPath_GraphUp_Wikidata

- Analytical functions for SPARQL results

  - pc_plot

- Analytical functions for Graph Data 

  - agGraphAnalysis

- Generation functions for Table-type Visualization

  - agTableDT

  - agTableFM
  
  - agTableKB
  
- Generation functions for Network Graph Visualization

  - agVisNetwork

  - agNetwork3d
  
- Generation functions for Data processing

  - PurseNT
  
    - ...


# Session information {.unnumbered}
```{r sessionInfo, echo=FALSE}
sessionInfo()
```
