---
title: "Workflow to use agGraphSearch"
shorttitle: "WF-002: match labels to the wikidata via SPARQL"
author:
  - name: Satoshi Kume
date: "`r Sys.Date()`"
graphics: no
package: agGraphSearch, knitr, SPARQL
output:
  BiocStyle::html_document:
  toc_float: true
vignette: >
  %\VignetteIndexEntry{WF-002: match labels to the wikidata via SPARQL}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{agGraphSearch}
---

```{r style, echo = FALSE, results = 'asis', message=FALSE}
BiocStyle::markdown()
```

**Last modified:** `r file.info("agGraphSearch-WF-002.Rmd")$mtime`<br />
**Compiled**: `r date()`

# Getting started

Once `r Rpackage("agGraphSearch")` is installed, it can be loaded by the following command.

```{r library, message=FALSE}
library("agGraphSearch")
```

This workflow can be skipped. The next workflow should be started. 

# Read the csv files

```{r echo=TRUE, eval=FALSE}
lab <- data.frame(readr::read_csv("./00_Input/words.lab.csv", col_names = F))
```

if the WF-001 is skipped, start with the command as follows.

```{r echo=TRUE, eval=FALSE}
f <- system.file("extdata", "words.lab.csv", package="agGraphSearch")
lab <- data.frame(readr::read_csv(f, col_names = F))
```

# check the data

```{r echo=TRUE, eval=FALSE}
head(lab)
dim(lab)

#unique number
length(unique(lab$X1))

#table
agTableKB(lab)
```

# Check SPARQL query and run SPARQL
```{r echo=TRUE, eval=FALSE}
lab00 <- lab$X1[1]

#check Query
CkeckQuery_agCount_Label_Num_Wikidata_P279_P31(Entity_Name = lab00)

#Endpoint
agGraphSearch::KzLabEndPoint_Wikidata$EndPoint
#Graph id
agGraphSearch::KzLabEndPoint_Wikidata$FROM

#run SPARQL
#library(SPARQL)
res <- agCount_Label_Num_Wikidata_P279_P31(Entity_Name = lab00)
res

agTableDT(res, Width = "100px")

```

# Executing SPARQL 

This program executes SPARQL with a for-loop.

Input words are 515.

```{r echo=TRUE, eval=FALSE}
m <- c()
for(n in 1:nrow(lab)){
message(n)
m[[n]] <-agCount_Label_Num_Wikidata_P279_P31(Entity_Name = lab$X1[n])
}

#convert list to data.frame
fm <- ListDF2DF(m)

#view the data
agTableDT(fm)
```

In an alternative way, this executes SPARQL with a multisession of furrr::future_map function.

```{r echo=TRUE, eval=FALSE}
furrr::plan(multisession(workers = 4))
furrr::plan()

#Do SPARQL
mm <- furrr::future_map(as.character(unlist(lab)), 
                        agGraphSearch:::agCount_Label_Num_Wikidata_P279_P31, 
                        .progress=T)

#convert list to data.frame
fmm <- ListDF2DF(mm)

#view the data
agTableDT(fmm)

#pre-check
#table(fmm$Hit_Label > 0)
#FALSE  TRUE 
#  306   209 

#need to change it to fm
#fm <- fmm
```
# Aggregating search results 

```{r echo=TRUE, eval=FALSE}
fm1 <- fm

#colnames
colnames(fm1)

#Hit_Label
table(fm1$Hit_Label > 0)

#Hit_ALL
table(fm1$Hit_ALL > 0)
table(fm1$Hit_upClass_All > 0)
table(fm1$Hit_downClass_All > 0)

#New column: Relation
fm1$Relation <- fm1$Hit_upClass_All + fm1$Hit_downClass_All
table(fm1$Hit_ALL == fm1$Relation)

```

# Extract only results with label hits

```{r echo=TRUE, eval=FALSE}
fm2 <- fm1[c(fm1$Hit_Label > 0),]
dim(fm2)
```

# Extract only results with upper classes

```{r echo=TRUE, eval=FALSE}
fm3 <- fm2[c(fm2$Hit_ALL > 0),]
dim(fm3)

agTableDT(fm3)
```

# Convert them to rdfs:label.

The input words are 193 words.

This imply the deletion of wd:P entity.

```{r echo=TRUE, eval=FALSE}
Lab01 <- fm3$LABEL
agTableKB(data.frame(Lab01))

#Check Query
CkeckQuery_agWD_Alt_Wikidata(unlist(Lab01)[1])
#CkeckQuery_agWD_Alt_Wikidata(unlist(Lab01)[136])

#run SPARQL
furrr::plan(multisession(workers = 2))
Lab01_res <- furrr::future_map(unlist(Lab01), agWD_Alt_Wikidata, .progress = TRUE)

#check them
Lab01_res[[1]]
Lab01_res[[136]]
Lab01_res[[79]]
Lab01_res[[119]]

#check NA
agGraphSearch:::checkNA_af_agWD_Alt(Lab01_res)

#check nrow
agGraphSearch:::checkNrow_af_agWD_Alt(Lab01_res)

#gathering IDs
Lab02 <- ListDF2DF(Lab01_res, NA.omit=TRUE)
dim(Lab02)

#delete deplicates
QID <- unique(unlist(Lab02))
length(QID)

#save
if(!dir.exists("01_Out")){dir.create("01_Out")}
saveRDS(QID, file = "./01_Out/R01_QID.Rdata", compress = TRUE)

```

# Assigning Label information to QID

```{r echo=TRUE, eval=FALSE}
#view query
CkeckQuery_agQIDtoLabel_Wikidata(QID[1])

#do SPARQL
furrr::plan(multisession(workers = 2))
Label00 <- furrr::future_map(unlist(QID), agQIDtoLabel_Wikidata, .progress = TRUE)

#check nrow
checkNrow_af_agQIDtoLabel(Label00)
#checkNrow_af_agWD_Alt(Label00)

#convert list to data.frame
Label01 <- ListDF2DF(Label00)

#check it
head(Label01)
dim(Label01)
table(is.na(Label01))
table(is.na(Label01$entityNamej))
table(is.na(Label01$entityNamee))

#rows wit NA
Label01[is.na(Label01$entityNamee),]

#save
#if(!dir.exists("01_Out")){dir.create("01_Out")}
saveRDS(Label01, file = "./01_Out/R01_QID_rdfsLabel.Rdata", compress = TRUE)

```

# Retry SPARQL

```{r echo=TRUE, eval=FALSE}
#Data load 
Labs <- readRDS("./01_Out/R01_QID_rdfsLabel.Rdata")
head(Labs)
dim(Labs)

#View query
CkeckQuery_agCount_ID_Num_Wikidata_QID_P279_P31(Labs[1,1])

#Try SPARQL
furrr::plan(multisession(workers = 4))
#furrr::plan()

m_2 <- furrr::future_map(unlist(Labs$QID), agCount_ID_Num_Wikidata_QID_P279_P31, .progress = TRUE)

#convert list to data.frame
fm_2 <- ListDF2DF(m_2)

#check it
head(fm_2)
dim(fm_2)
colnames(fm_2)

#All
table(fm_2$Hit_All)
table(fm_2$Hit_All > 0)
table(fm_2$Hit_All_Parent > 0)
table(fm_2$Hit_All_Child > 0)


# check labels corresponding to ID
head(Labs)
dim(Labs)

Labs_B1 <- furrr::future_map(unlist(Labs$entityNamej), 
                             agCount_Label_Num_Wikidata_P279_P31, 
                             .progress = TRUE)
head(Labs_B1)

#check nrow
checkNrowVec_af_agQIDtoLabel(Labs_B1)
checkNrow_af_agQIDtoLabel(Labs_B1)

#check results
checkHitLabel_af_agCount_Label_Num(Labs_B1)
checkHitALL_af_agCount_Label_Num(Labs_B1)

#View the results
Labs_B2 <- ListDF2DF(Labs_B1)

agTableDT(Labs_B2, Width = "100px")

```





# Session information {.unnumbered}
```{r sessionInfo, echo=FALSE}
sessionInfo()
```
