---
title: "Workflow to use agGraphSearch and Mesh RDF: WF-002"
shorttitle: "WF-002: match labels to the Mesh data via SPARQL"
author:
  - name: Satoshi Kume
date: "`r Sys.Date()`"
graphics: no
package: agGraphSearch, knitr, SPARQL
output:
  BiocStyle::html_document:
  toc_float: true
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{agGraphSearch}
  %\VignetteIndexEntry{WF-002: match labels to the wikidata via SPARQL}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r style, echo=FALSE, message=FALSE, results='asis'}
BiocStyle::markdown()
```

**Last modified:** `r file.info("agGraphSearch-WF-002.Rmd")$mtime`<br />
**Compiled**: `r date()`

# Getting started

Once `r Rpackage("agGraphSearch")` is installed, it can be loaded by the following command.

```{r library, echo=TRUE, eval=FALSE}
#rm( list=ls() )
library(agGraphSearch)
library(magrittr)

#Re-build
rm( list=ls() )

if(F){
system("rm -rf ./agGraphSearch/NAMESPACE")
roxygen2::roxygenise("./agGraphSearch")
system("cat ./agGraphSearch/NAMESPACE")
remove.packages("agGraphSearch", lib=.libPaths())
.rs.restartR()
}

#install.packages(c("SPARQL", "franc", "formattable"))

if(F){
system("R CMD INSTALL agGraphSearch")
Sys.sleep(1)
library(agGraphSearch)
}

if(F){
proxy_url = "http://wwwproxy.osakac.ac.jp:8080"
Sys.setenv("http_proxy" = proxy_url)
Sys.setenv("https_proxy" = proxy_url)
Sys.setenv("ftp_proxy" = proxy_url)
}

if(F){
proxy_url = "http://wwwproxy.osakac.ac.jp:8080"
Sys.setenv("http_proxy" = proxy_url)
Sys.setenv("https_proxy" = proxy_url)
Sys.setenv("ftp_proxy" = proxy_url)
devtools::install_github( "kumeS/agGraphSearch" )
library(agGraphSearch)
}

if(F){
devtools::install_github( "kumeS/agGraphSearch" )
library(agGraphSearch)
}

```

# Read the csv files

You should split compound words as a pre-processing.

```{r echo=TRUE, eval=FALSE}
words <- data.frame(readr::read_csv("./00_Mesh_Input/words.cR.csv", col_names = F, show_col_types = F))
words <- unlist(words, use.names = F)
words <- data.frame(X1=words[!is.na(words)])
```

if the WF-001 is skipped, start with the command as follows.

```{r echo=TRUE, eval=FALSE}
f <- system.file("extdata", "Mesh_words.cR.csv", package="agGraphSearch")
words <- data.frame(readr::read_csv(f, col_names = F, show_col_types = F))
```

# check the data

```{r echo=TRUE, eval=FALSE}
head(words)
dim(words)

#unique number
length(unique(words))

#table
head(words)
#agTableKB(words, Head = F, Align = 3)
```

# Downloads the Mesh files from the repository (Google Drive).

```{r, echo=TRUE, eval=FALSE}
#save
if(!dir.exists("00_Mesh_Input")){dir.create("00_Mesh_Input")}

#file path
proxy <- 'export https_proxy="http://wwwproxy.osakac.ac.jp:8080"; export ftp_proxy="http://wwwproxy.osakac.ac.jp:8080"'
scr <- system.file("script", "gdrive_download.sh", package="agGraphSearch")

#Mesh_othersR.Rds

#mesh_Label_en_dfR.Rds

```

# Import Mesh data (2021)

```{r, echo=TRUE, eval=FALSE}
MeshLabels <- readRDS("./00_Mesh_Input/mesh_Label_en_dfR.Rds")
head(MeshLabels)
table(MeshLabels$Property)

MeshOthers <- readRDS("./00_Mesh_Input/Mesh_othersR.Rds")
head(MeshOthers)
table(MeshOthers$Property)

MeshLabelsR <- MeshLabels[MeshLabels$Subject %in% unique(c(MeshOthers$Subject, MeshOthers$Object)),]
dim(MeshLabelsR)
saveRDS(MeshLabelsR, "./00_Mesh_Input/MeshLabelsR.Rds")
```

# Linking of input words to the Mesh words

Input words in English are 408.

```{r echo=TRUE, eval=FALSE}
words <- unlist(words, use.names = F)
words <- words[!is.na(words)]
words <- words[words != ""]
words <- unique(words)

head(words)
length(unique(words))

#小文字変換
head(MeshLabelsR)
MeshLabels01 <- unique(tolower(MeshLabelsR$Object))
head(MeshLabels01)
length(MeshLabels01)

head(words)
words00 <- unique(unlist(words)); words00 <- words00[!is.na(words00)]
words01 <- unique(tolower(words00))
head(words01)

#文字列距離実行
library( agGraphSearch )
Dat <- ComputeDistance(InputTerms=words01,
                       RDFterms=MeshLabels01,
                       q=2, nthread=4, TopWords=3)
  
head(Dat)
table(Dat$PerfectMatch > 0)
table(Dat$PartialMatch > 0)
table(Dat$cosine1 > 0)

```

#O/Xをつけて、閾値を決める
#コサインが良いかも

```{r echo=TRUE, eval=FALSE}
#rm( list=ls() )

#options(digits=5) 
Thres <- data.frame(readr::read_csv("./01_Mesh_Out/Dat210610_v02.csv", col_names = T))

head(Thres)
tail(Thres)
Thres$Check0 <- NA
Thres$Check0[Thres$Check == 0] <- "X"
Thres$Check0[Thres$Check == 1] <- "O"
Thres$cosine3 <- as.integer(Thres$cosine3*10000)/10000

#Create the plot
library(ggplot2)
ggplot(Thres, aes(x = Check0, y = cosine3)) +
  geom_boxplot(outlier.colour = NA, width = .4) +
  geom_dotplot(binaxis = "y", binwidth = .005, stackdir = "center", fill = NA)

summary(Thres$cosine3[Thres$Check == 0])
#   Min. 1st Qu.  Median    Mean 3rd Qu.    Max. 
# 0.0762  0.2417  0.3164  0.3138  0.3814  0.6087 
#厳し目基準なら、Thres = 0.075

head(Thres)
words02 <- Thres[Thres$cosine3 < 0.075, ]
head(words02)
dim(words02)
rownames(words02) <- 1:nrow(words02)

#saveRDS(words02, "./01_Mesh_Out/words02.Rds")
```

# Translate English to Japanese

```{r echo=TRUE, eval=FALSE}
rm(list=ls())

words02 <- readRDS("./01_Mesh_Out/words02.Rds")
head(words02)

words02$Lab00 <- NA
head(words02)

#ラベルを逆にする
head(words02)
words02$Lab00 <- tolower(words02$cosine2)
words02$Lab01 <- NA
head(words02)

table(grepl("[,][ ]", words02$Lab00))
table(grepl("[,][ ]and", words02$Lab00))

for(n in 1:length(words02$Lab00)){
#n <- 5
if(grepl("[,][ ]", words02$Lab00[n])){
 aa <- strsplit(words02$Lab00[n], split = ", ")[[1]]
 words02$Lab01[n] <- paste(aa[length(aa):1], collapse = " ")
}else{
 aa <-  words02$Lab00[n]
 words02$Lab01[n] <- aa
}}
table(grepl("[,]", words02$Lab01))

words02$Jpn <- NA
head(words02, n=10)

#Translate to Jpn
if(F){
proxy_url = "http://wwwproxy.osakac.ac.jp:8080"
Sys.setenv("http_proxy" = proxy_url)
Sys.setenv("https_proxy" = proxy_url)
Sys.setenv("ftp_proxy" = proxy_url)
}

head(words02)
for(n in 1:length(words02$Lab01)){
#n <- 1
print(n)
Result <- DeePL(Sentence=words02$Lab01[n], Auth_Key="43725ffd-d3d3-a301-c92d-8d7e2070f71c:fx")
words02$Jpn[n] <- Result
}

head(words02, n=10)
tail(words02, n=10)
words02[is.na(words02)] <- 0

#PerfectMatch
a <- words02$PerfectMatch > 0
unique(words02$Terms[a])
sum(a)
#[1] 54

#PartialMatch
a <- words02$PartialMatch > 0
unique(words02$Terms[a])
sum(a)
#[1] 57

#cosine3
a <- words02$cosine3 < 0.075
unique(words02$Terms[a])
sum(a)
#[1] 101

#######################################
#Save
#saveRDS(words02, "./01_Mesh_Out/words02_Jpn.Rds")
#readr::write_excel_csv(words02, file="./01_Mesh_Out/words02_Jpn.csv", col_names = T, append=F)
#######################################
```

# Linking to the Mesh

Use the below propertys for researching the class hierarchy.
- meshv:broaderDescriptor
- meshv:concept

```{r echo=TRUE, eval=FALSE}
#Match List
words02 <- readRDS("./01_Mesh_Out/words02_Jpn.Rds")
head(words02)

table(words02$cosine2 == words02$Lab00)
table(words02$cosine2 == words02$Lab01)

#Mesh D term List
MeshLabels00 <- MeshLabelsR
head( MeshLabels00 )

dim( MeshLabels00 )
length(unique(MeshLabels00$Subject))
length(unique(MeshLabels00$Property))
length(unique(MeshLabels00$Object))

#Check
library( magrittr )

####################################################
#Extract IDs
####################################################
#一時的に小文字に変換してマッティング
MeshLabels01 <- MeshLabels00[c(tolower(MeshLabels00$Object) %in% tolower(words02$Lab00)),]

head(MeshLabels01)
dim(MeshLabels01)
length(unique(MeshLabels01$Subject))
length(unique(MeshLabels01$Property))
unique(MeshLabels01$Property)
length(unique(MeshLabels01$Object))

LabList00 <- unique(MeshLabels01$Subject)

head(LabList00)
saveRDS(LabList00, "./01_Mesh_Out/LabList00.Rds")

```

# Check structures of Polymers

```{r echo=TRUE, eval=FALSE}
#修正版の読み込み
rm(list=ls())

#MeshLabelsR.Rds
MeshLabelR <- readRDS("./00_Mesh_Input/MeshLabelsR.Rds")

head(MeshLabelR); dim(MeshLabelR)
table(MeshLabelR$OtherInfo == "BLANK")
table(MeshLabelR$Property)
table(MeshLabelR$SubInfo)

#Mesh_othersR.Rds
MeshOthers <- readRDS("./00_Mesh_Input/Mesh_othersR.Rds")

head(MeshOthers); dim(MeshOthers)
table(MeshOthers$OtherInfo == "BLANK")
table(MeshOthers$Property)
table(MeshOthers$SubInfo)
table(MeshOthers$ObjInfo)

##############################################
#Trial 01
##############################################
txt <- "Polymers"
a1 <- MeshLabelR[MeshLabelR$Object == txt,]

a1
#              Subject   Property   Object OtherInfo    SubInfo
#1242522  mesh:D011108 rdfs:label Polymers       @en IDs:mesh:D
#1906322 mesh:M0017208 rdfs:label Polymers       @en IDs:mesh:M
a2 <- a1$Subject
a2

Dat <- c(); x <- 1; Query <- a2
repeat{
print(x)
b1 <- MeshOthers[MeshOthers$Subject %in% Query,]
if(dim(b1)[1] == 0){break}
Dat <- rbind(Dat, b1)
Query <- b1$Object
x <- x + 1
if(x == 100){break}
}

x <- 1; Query <- a2
repeat{
print(x)
b2 <- MeshOthers[MeshOthers$Object %in% Query,]
if(dim(b2)[1] == 0){break}
Dat <- rbind(Dat, b2)
Query <- b2$Subject
x <- x + 1
if(x == 100){break}
}

head(Dat); dim(Dat)
rownames(Dat) <- 1:nrow(Dat)
colnames(Dat) <- c("subject", "property", "parentClass", "OtherInfo", "SubInfo", "ObjInfo")
Dat$triple <- paste0(Dat$subject, ".", Dat$property, ".", Dat$parentClass)
Dat <- Dat[as.numeric(rownames(unique(Dat["triple"]))),]
Dat <- Dat[,-ncol(Dat)]
head(Dat); dim(Dat)
length(unique(c(Dat$subject, Dat$parentClass)))

#Add labels
library(agGraphSearch)
Dat00 <- MergeMeshData(Data=Dat, Labels=MeshLabelR)
FileName <- paste0("agVisNetwork_polymers_", format(Sys.time(), "%y%m%d-%H%M%S"),".html")

head(Dat00); dim(Dat00); table(Dat00$property)
table(Dat00$property)

########################################################################
#Jpn
########################################################################
head(Dat)
DatJpn <- Dat00

dim(DatJpn)
DatJpn$triple <- paste0(DatJpn$subject, ".", DatJpn$property, ".", DatJpn$parentClass)
rownames(DatJpn) <- 1:nrow(DatJpn)
DatJpn00 <- DatJpn[as.numeric(rownames(unique(DatJpn["triple"]))),]
DatJpn00 <- DatJpn00[,-ncol(DatJpn00)]
dim(DatJpn00)

DatJpn <- DatJpn00
table(DatJpn$property)
dim(DatJpn)
length(unique(c(DatJpn$subject, DatJpn$parentClass)))
length(unique(c(DatJpn$subjectLabel, DatJpn$parentClassLabel)))

#Translate to Jpn
if(F){
proxy_url = "http://wwwproxy.osakac.ac.jp:8080"
Sys.setenv("http_proxy" = proxy_url)
Sys.setenv("https_proxy" = proxy_url)
Sys.setenv("ftp_proxy" = proxy_url)
}

DatJpn02 <- Label2Jpn(Data=DatJpn, Auth_Key="43725ffd-d3d3-a301-c92d-8d7e2070f71c:fx")
saveRDS(DatJpn02, "./02_Mesh_Out/DatJpn02.Rds")
FileName <- paste0("agVisNetwork_polymers_Jpn_", format(Sys.time(), "%y%m%d-%H%M%S"),".html")

DatJpn03 <- DatJpn02
DatJpn03 <- DatJpn03[DatJpn03$property != "meshv:preferredConcept",]
#DatJpn03 <- DatJpn03[DatJpn03$property != "meshv:preferredConceptR",]
head(DatJpn03); dim(DatJpn03)

#All
agVisNetwork(Graph=DatJpn03,
             Selected=NULL, 
             Browse=TRUE, 
             Output=TRUE,
             FilePath=FileName)

```

# Extract the upper classes

```{r echo=TRUE, eval=FALSE}
rm(list=ls())
#Read data
LabList00 <- readRDS("./01_Mesh_Out/LabList00.Rds")
head(LabList00)

#MeshLabelsR.Rds
MeshLabelR <- readRDS("./00_Mesh_Input/MeshLabelsR.Rds")

head(MeshLabelR); dim(MeshLabelR)
table(MeshLabelR$OtherInfo == "BLANK")
table(MeshLabelR$Property)
table(MeshLabelR$SubInfo)

#Mesh_othersR.Rds
MeshOthers <- readRDS("./00_Mesh_Input/Mesh_othersR.Rds")

#Perform All
library( agGraphSearch )
Dat <- extractUpperConcepts4Mesh(Lab_List=LabList00,
                                 Data=MeshOthers,
                                 Labels=MeshLabelR,
                                 Property="subClassOf")

head(Dat)
length(Dat)
Dat00 <- c()
for(n in seq_len(length(Dat))){
#n <- 1
Dat00 <- c(Dat00, Dat[[n]][[2]])
}

table(Dat00)
Dat01 <- data.frame(Name=names(table(Dat00)), Count=as.numeric(table(Dat00)), row.names = seq_len(length(table(Dat00))))
Dat01
head(MeshLabelR)
Dat02 <- merge(Dat01, MeshLabelR, by.x = "Name", by.y = "Subject", all.x = T, all.y = F)[,c(1:4)]
Dat03 <- Dat02[order(-Dat02$Count),]
rownames(Dat03) <- 1:nrow(Dat03)
saveRDS(Dat03, "./00_Mesh_Input/Mesh_Dat02.Rds")
```

# Visualize the relation network

```{r echo=TRUE, eval=FALSE}

Dat03
#MeshLabelsR.Rds
MeshLabelR <- readRDS("./00_Mesh_Input/MeshLabelsR.Rds")
#Mesh_othersR.Rds
MeshOthers <- readRDS("./00_Mesh_Input/Mesh_othersR.Rds")
ADD <- data.frame(Name=c("mesh:D008420", "mesh:D055641"),
           Count=0,
           Property =NA,
           Object=c("Manufactured Materials", "Mathematical Concepts"))
Dat03 <- rbind(Dat03, ADD)
head(Dat03)
tail(Dat03)

DepN <- 4
for(n in seq_len(nrow(Dat03))){
#n <- 1
a <- Dat03[n,1]
b <- Dat03[n,4]

#下位探索
DatSubClassOfDown <- c(); x <- 1; Query <- a

tim <- format(Sys.time(), "%y%m%d-%H%M%S")
FileName <- paste0("agVisNetwork_", formatC(n, flag = "0", width = 3), "_下位探索_Depth", formatC(DepN, flag = "0", width = 2), "_", gsub(" ", "", b), "_", tim, ".html")
OutName <- paste0("agVisNetwork_", formatC(n, flag = "0", width = 3), "_下位探索_Depth", formatC(DepN, flag = "0", width = 2), "_", gsub(" ", "", b), "_", tim, ".Rds")

repeat{
print(x)
b1 <- MeshOthers[MeshOthers$Object %in% Query,]
b1 <- b1[b1$Property == "subClassOf",]
if(dim(b1)[1] == 0){break}
b1$Depth <- paste0("down", formatC(x, flag = "0", width = "2"))
DatSubClassOfDown <- rbind(DatSubClassOfDown, b1)
Query <- b1$Subject
if(x == DepN){break}
x <- x + 1
}

rownames(DatSubClassOfDown) <- 1:nrow(DatSubClassOfDown)
DatSubClassOfDown$triple <- paste0(DatSubClassOfDown$Subject, ".", 
                                   DatSubClassOfDown$Property, ".", 
                                   DatSubClassOfDown$Object)
DatSubClassOfDown <- DatSubClassOfDown[as.numeric(rownames(unique(DatSubClassOfDown["triple"]))),]
DatSubClassOfDown <- DatSubClassOfDown[,-ncol(DatSubClassOfDown)]

DatSubClassOfDown00 <- MergeMeshData(DatSubClassOfDown, MeshLabelR)
saveRDS(DatSubClassOfDown00, OutName)
#head(DatSubClassOfDown00)

agVisNetwork(Graph=DatSubClassOfDown00,
             Selected=NULL, 
             Browse=FALSE, 
             Output=TRUE,
             FilePath=FileName)

system(paste0("mv ", FileName, " ./03_Mesh_Out"))
system(paste0("mv ", OutName, " ./03_Mesh_Out"))

}

##Jpn
File <- "agVisNetwork_003_下位探索_Depth25_PhysicalPhenomena_210831-184747.Rds"
Dat <- readRDS(paste0("./03_Mesh_Out/", File))
head(Dat)

#Translate to Jpn
if(F){
proxy_url = "http://wwwproxy.osakac.ac.jp:8080"
Sys.setenv("http_proxy" = proxy_url)
Sys.setenv("https_proxy" = proxy_url)
Sys.setenv("ftp_proxy" = proxy_url)
}

DatJpn <- Label2Jpn(Dat, Auth_Key="43725ffd-d3d3-a301-c92d-8d7e2070f71c:fx")

agVisNetwork(Graph=DatJpn,
             Selected=NULL, 
             Browse=FALSE, 
             Output=TRUE,
             FilePath=sub(".Rds", "_Jpn.html", File))
saveRDS(DatJpn, sub(".Rds", "_Jpn.Rds", File))

system(paste0("mv ", sub(".Rds", "_Jpn.html", File), " ./03_Mesh_Out"))
system(paste0("mv ", sub(".Rds", "_Jpn.Rds", File), " ./03_Mesh_Out"))

```

