---
title: "Installation of agGraphSearch"
author:
  - name: Satoshi Kume
date: "`r Sys.Date()`"
graphics: no
package: agGraphSearch, knitr, SPARQL
output:
  BiocStyle::html_document:
  toc_float: true
vignette: >
  %\VignetteIndexEntry{Installation of agGraphSearch}
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{agGraphSearch}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r style, echo = FALSE, results = 'asis', message=FALSE}
BiocStyle::markdown()
```

**Last modified:** `r file.info("agGraphSearch-installation.Rmd")$mtime`<br/>
**Compiled**: `r date()`

# Getting started

To install `r Rpackage("agGraphSearch")`, start R and enter:

```{r installation, echo=TRUE, eval=FALSE}
install.packages( "devtools" )
devtools::install_github( "kumeS/agGraphSearch" )
```

Once `r Rpackage("agGraphSearch")` is installed, it can be loaded by the following command.

```{r library, echo=TRUE, eval=FALSE, message=FALSE}
library("agGraphSearch")
```

# How to use Rocker environment.

Optionally, you use the following sh command on Mac/Linux Terminal if you want to use the Rocker environment.

```sh
docker run \
       -d \
       --name RStudio \
       -v $(pwd)/XXX:/home/rstudio/XXX \
       -e ROOT=TRUE \
       -e PASSWORD=PassWord \
       -p 8787:8787 \
       rocker/rstudio:4.0.5
#XXX: Your folder path

#Then, browse the page
open http://localhost:8787
```

An alternative way, type the R code below if you want to run the Rocker environment from the R console.

```r
system("docker run \\
        -d \\
        --name RStudio \\
        -v $(pwd)/XXX:/home/rstudio/XXX \\
        -e ROOT=TRUE \\
        -e PASSWORD=PassWord \\
        -p 8787:8787 \\
       rocker/rstudio:4.0.5")
#XXX: Your folder path

#Then, browse the page
system("open http://localhost:8787")
```

See [Rocker page](https://hub.docker.com/r/rocker/rstudio) if you want to know details to the rocker image.

## Optional Rocker setting

Type the R code below for the settings.

```r
## run first on the terminal windows
#sudo apt-get update
#sudo apt-get install libxml2-dev libglpk-dev

#Install packages
install.packages("BiocManager")
BiocManager::install("BiocStyle")

install.packages( "devtools" )
devtools::install_github( "kumeS/agGraphSearch" )
library( "agGraphSearch" )
```

# Session information {.unnumbered}
```{r sessionInfo, echo=FALSE}
sessionInfo()
```

