---
title: "A workflow to use agGraphSearch and Wikidata with PolyInfo terms"
author:
  - name: Satoshi Kume
date: "`r Sys.Date()`"
graphics: no
package: agGraphSearch, knitr, SPARQL
output:
  BiocStyle::html_document:
  toc_float: true
vignette: >
  %\VignetteEncoding{UTF-8}
  %\VignetteDepends{agGraphSearch}
  %\VignetteIndexEntry{A workflow to use agGraphSearch and Wikidata with PolyInfo terms}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r style, echo=FALSE, message=FALSE, results='asis'}
BiocStyle::markdown()
```

**Last modified:** `r file.info("agGraphSearch-Wikidata-WF.Rmd")$mtime`<br />
**Compiled**: `r date()`

# Getting started

## Requirements

- macOSX 10.15 with Intel Core i7 or similar specs
- RAM: 32GB
- Available storage: > 20GB

## Installation of agGraphSearch

Once `r Rpackage("agGraphSearch")` is installed, it can be loaded by the following command.

```{r library, echo=TRUE, eval=FALSE}
#Clean the enbironment
rm(list=ls())

#Install
install.packages("devtools")
devtools::install_github( "kumeS/agGraphSearch", force = TRUE)
library(agGraphSearch)
library(magrittr)
```

## Generate temporary folders

```{r echo=TRUE, eval=FALSE}
#Create temporary folder path
tempDIR <- tempdir()
if(!dir.exists(paste0(tempDIR, "/", "Wiki_01_Out"))){dir.create(paste0(tempDIR, "/", "Wiki_01_Out"))}
if(!dir.exists(paste0(tempDIR, "/", "Wiki_02_Out"))){dir.create(paste0(tempDIR, "/", "Wiki_02_Out"))}
if(!dir.exists(paste0(tempDIR, "/", "Wiki_03_Out"))){dir.create(paste0(tempDIR, "/", "Wiki_03_Out"))}
if(!dir.exists(paste0(tempDIR, "/", "Wiki_04_Jpn"))){dir.create(paste0(tempDIR, "/", "Wiki_04_Jpn"))}
if(!dir.exists(paste0(tempDIR, "/", "Wiki_05_RDF"))){dir.create(paste0(tempDIR, "/", "Wiki_05_RDF"))}

#show the folders
dir(tempDIR)
```

# Read the search terms obtained from PolyInfo databse.

In this tutorial, the Japanese terms obtained from PolyInfo Database will be used and the number of terms is total 510.

```{r echo=TRUE, eval=FALSE}
#Read Japanese terms
f <- system.file("extdata", "PoLyInfo_terms_Jpn_v01.csv", package="agGraphSearch")
wordsj <- data.frame(readr::read_csv(f, col_names = T, show_col_types = FALSE))

#Processing
words <- unique(unlist(wordsj, use.names = F))
words <- words[!is.na(words)]

#show the head
head(words)
length(words)
```

I also showed how to use the English terms obtained from PolyInfo Database (total 463 terms).

```{r echo=TRUE, eval=FALSE}
if(F){
#Read English terms
f <- system.file("extdata", "PoLyInfo_terms_En_v01.csv", package="agGraphSearch")
wordse <- data.frame(readr::read_csv(f, col_names = T, show_col_types = FALSE))

#Processing
words <- unique(unlist(wordse, use.names = F))
words <- words[!is.na(words)]

#show the head
head(words)
}
```

# Wikidata datasets (25th Sep 2021)

## Download the Wikidata datasets from Google Drive.

Download below files and save on the local environment.

```{r echo=TRUE, eval=FALSE}
## Download Class-related hierarchy dataset (Common to English and Japanese)
browseURL("https://drive.google.com/file/d/1YcUVgCShQOOSY0ckv1h-B4eu-4mBHLVz/view?usp=sharing")

## Download Japanese labels
browseURL("https://drive.google.com/file/d/1NMJYwDjuAujxA6tdpqUwUBtxQxYzGZ8c/view?usp=sharing")

## Download English labels
#TBD

```

Then, I moved the files to your working directory. 
In this time, I manually moved their files to the "04_Wiki_PolyInfo_00" folder in the working directory .

## Import Wikidata datasets

```{r echo=TRUE, eval=FALSE}
#Load the hierarchy dataset
ClassHi <- readRDS("./04_Wiki_PolyInfo_00/Relation_P279_P31_df.Rds")

#Check data
head(ClassHi)
#table(ClassHi$Property)

#Remove loops
table(ClassHi$Subject != ClassHi$Object)
ClassHi <- ClassHi[ClassHi$Subject != ClassHi$Object,]

#Do not run
if(F){
#Load the label dataset
Labels01 <- readRDS("./04_Wiki_PolyInfo_00/Label_ja_rdfs_df.Rds")
Labels02 <- readRDS("./04_Wiki_PolyInfo_00/Label_ja_Altlabel_df.Rds")

#Bind, extract and check labels
Labels <- rbind(Labels01, Labels02)
head(Labels)
saveRDS(Labels, "./04_Wiki_PolyInfo_00/Label_ja_All_label_df.Rds")  
}

#Load the label dataset
Labels <- readRDS("./04_Wiki_PolyInfo_00/Label_ja_All_label_df.Rds")

```

# Linking of input terms to the wikidata labels

Input are 510 terms in Japanese.

```{r echo=TRUE, eval=FALSE}
#Show data
head(words)
head(Labels)

#Linking
LabelsR <- Labels[Labels$Object %in% words,]
LabelsR <- LabelsR[LabelsR$Subject %in% unique(ClassHi$Subject),]

#Check data
dim(LabelsR)
head(LabelsR)

#rename row
rownames(LabelsR) <- 1:nrow(LabelsR)
dim(LabelsR)

#Obtain the subject QID
QID.d <- data.frame(QID=unique(LabelsR$Subject))
```

# Check relations via SPARQL query

This program executes SPARQL with a for-loop.

Input entities are 247.

## excluding the adjacent entity

```{r echo=TRUE, eval=FALSE}
#proxy setting if you need.
#proxy_url = "http://wwwproxy.osakac.ac.jp:8080"
#ProxySet(proxy_url)

#Temp Function for excluding the adjacent entity
Tem00 <- function(Entity_ID0, Object0, Property0="?p", Count0="?p"){
Val00 <- wikiCount_QID_Property_Object(Entity_ID=Entity_ID0, Property=Property0, Object=Object0, Count=Count0)
return(Val00)
}

#set parameters
ExcluQ <- c("Q101352", "Q16521", "Q11424", "Q6256", 
            "Q12308941", "Q11879590", "Q5", "Q5327369", 
            "Q577", "Q4167410", "Q3305213", "Q13406463", 
            "Q35120", "Q3695082", "Q131257", "Q80071", 
            "Q4830453", "Q482994", "Q20202269", "Q2996394")
NumQ <- length(ExcluQ)

#run
for(n in seq_len(NumQ)){
#n <- 1
message(n, ": ", ExcluQ[n])
DatA <- QID.d$QID; DatB <- rep(paste0("wd:", ExcluQ[n]), length(DatA))
a <- furrr::future_map2(unlist(DatA), unlist(DatB), Tem00, .progress = TRUE)
eval(parse(text=paste0("QID.d$", ExcluQ[n], " <- c(unlist(a) > 0)")))

readr::write_excel_csv(QID.d, 
                       paste0(paste0(tempDIR, "/", "Wiki_01_Out"), 
                              "/ExcluQ_", formatC(n, width = 3, flag = "0"), "_", ExcluQ[n], ".csv"), col_names = T)
#show hits
print(eval(parse(text=paste0("QID.d[QID.d$", ExcluQ[n], " == TRUE,c(1, ncol(QID.d))]"))))
#remove hits
QID.d <- QID.d[unlist(a, use.names = F) == 0,]
print(dim(QID.d))
}

#show results
dim(QID.d)
head(QID.d)

```

## excluding the particular property

```{r echo=TRUE, eval=FALSE}
#Temp Function for excluding the particular property
Tem01 <- function(Entity_ID0, Property0, Object0="?o", Count0="?o"){
Val01 <- wikiCount_QID_Property_Object(Entity_ID=Entity_ID0, Property=Property0, Object=Object0, Count=Count0)
return(Val01)
}

#set parameters
ExcluP <- c("P131","P21","P747","P4743","P577")
NumP <- length(ExcluP)

#run
for(n in seq_len(NumP)){
#n <- 1
message(n, ": ", ExcluP[n])
DatA <- QID.d$QID; DatB <- rep(paste0("wdt:", ExcluP[n]), length(DatA))
a <- furrr::future_map2(unlist(DatA), unlist(DatB), Tem01, .progress = TRUE)
eval(parse(text=paste0("QID.d$", ExcluP[n], " <- c(unlist(a) > 0)")))

readr::write_excel_csv(QID.d, 
                       paste0(paste0(tempDIR, "/", "Wiki_01_Out"), 
                              "/ExcluP_", formatC(n, width = 3, flag = "0"), "_", ExcluP[n], ".csv"), col_names = T)
#show hits
print(eval(parse(text=paste0("QID.d[QID.d$", ExcluP[n], " == TRUE,c(1, ncol(QID.d))]"))))
#remove hits
QID.d <- QID.d[unlist(a, use.names = F) == 0,]
print(dim(QID.d))
}

#show results
dim(QID.d)
head(QID.d)

#saveRDS(QID.d, "./QID.d.Rds")
#QID.d <- readRDS("./QID.d.Rds")
```

## post-processing

```{r echo=TRUE, eval=FALSE}
#renames rows
rownames(QID.d) <- 1:nrow(QID.d)
QID.d01 <- QID.d[,-c(2:ncol(QID.d))]

#the number of QID
length(QID.d01)
head(QID.d01)
```

# Seaching upper concepts from the search entities

```{r echo=TRUE, eval=FALSE}
#show labels
LabelsR[LabelsR$Subject %in% QID.d01 & LabelsR$Property == "rdfs:label",]

##################################################################
#Upper search up to 30 steps
##################################################################
#set parameters
QID.list <- QID.d01
QID.dat <- NULL

#Run
for(n in 1:length(QID.list)){
#n <- 1
message("No.", n, ": ", QID.list[n])
Dat <- c(); x <- 0; Query <- QID.list[n]

repeat{
x <- x + 1
message("x: ", x)

#Both wdt:P279 and wdt:P31 when x = 1
b1 <- ClassHi[ClassHi$Subject %in% Query,]

#Only wdt:P279 when x >= 2
if(x >= 2){
  b1 <- b1[b1$Property == "wdt:P279",]
}

if(nrow(b1) == 0){
  rownames(Dat) <- 1:nrow(Dat)
  Dat$triple <- paste0(Dat$Subject, ".", Dat$Property, ".", Dat$Object)
  Dat <- Dat[as.numeric(rownames(unique(Dat["triple"]))),-c(ncol(Dat))]
  rownames(Dat) <- 1:nrow(Dat)
  #head(Dat)
  QID.dat[[n]] <- Dat
  names(QID.dat)[n] <- QID.list[n]
  break
  }
Dat <- rbind(Dat, b1)
Query <- b1$Object
if(x == 30){
  rownames(Dat) <- 1:nrow(Dat)
  Dat$triple <- paste0(Dat$Subject, ".", Dat$Property, ".", Dat$Object)
  Dat <- Dat[as.numeric(rownames(unique(Dat["triple"]))),-c(ncol(Dat))]
  rownames(Dat) <- 1:nrow(Dat)
  #head(Dat)
  QID.dat[[n]] <- Dat
  names(QID.dat)[n] <- QID.list[n]
  break
}
}}

#length(QID.dat)
#saveRDS(QID.dat, "./QID.dat.Rds")
#QID.dat <- readRDS("./QID.dat.Rds")
```

## Visualize Individual network diagrams.

```{r echo=TRUE, eval=FALSE}
library(agGraphSearch)
if(!dir.exists("04_Wiki_PolyInfo_01")){dir.create("04_Wiki_PolyInfo_01")}

for(n in 1:length(QID.dat)){
#n <- 1
message(n)
#head(QID.dat[[1]]); head(Labels)
Lab <- names(QID.dat)[n]; Lab00 <- paste(unlist(Labels[Labels$Subject == Lab & Labels$Property == "rdfs:label",c("Object", "Subject")]), collapse = ".")
Lab00

#Merge labels
QID.datR <- MergeWikiData(Data=QID.dat[[n]], 
                          Labels=Labels)
QID.datR <- QID.datR[QID.datR$subject != QID.datR$parentClass,]
QID.datR$subjectLabel <- paste0(QID.datR$subjectLabel, ".", QID.datR$subject)
QID.datR$parentClassLabel <- paste0(QID.datR$parentClassLabel, ".", QID.datR$parentClass)
head(QID.datR)

agGraphSearch:::agVisNetwork_cr(Graph=QID.datR,
                                NodeColorRandom=F, Count=2, 
                                Size=10, SmallSize=5, StarSize=10, 
                                FontSize=7, HeightSclale = "750px", 
                                WidthSclale = "110%", SEED=123, Selected=Lab00, 
                                Browse=F, output=T, file=paste0("./agVisNetwork_", formatC(n, flag="0", width=4), "_", Lab00, ".html"))
suppressMessages(filesstrings::file.move(files = paste0("./agVisNetwork_", formatC(n, flag="0", width=4), "_", Lab00, ".html"),
                        destinations = "./04_Wiki_PolyInfo_01", overwrite = T))

}


```

## Calculate the common upper entities

```{r echo=TRUE, eval=FALSE}
library(magrittr)
#QID.dat <- readRDS("./QID.dat.Rds")
#Labels <- readRDS("./04_Wiki_PolyInfo_00/Label_ja_All_label_df.Rds")
#str(QID.dat)

#################################################
#Calculate the common upper entities
#################################################
QID.dat_02 <- c()
CUcounts00 <- c()

for(n in seq_len(length(QID.dat))){
  #n <- 1
  a <- QID.dat[[n]]
  a$triple <- paste0(a$Subject, ".", a$Property, ".", a$Object)
  b <- a[as.numeric(rownames(unique(a["triple"]))),]
  
  #Remove loops
  b <- b[b$Subject != b$Object,]
  QID.dat_02 <- QID.dat_02 %>% rbind(b)
  
  #CU counts
  CUcounts00 <- c(CUcounts00, unique(b$Object))
}

head(QID.dat_02)
dim(QID.dat_02)
rownames(QID.dat_02) <- 1:nrow(QID.dat_02)

##Check NA
table(is.na(QID.dat_02))
table(is.na(QID.dat_02$Subject))
table(is.na(QID.dat_02$Object))

#################################################
## Visualize entire network diagrams
#################################################
#Merge labels
head(QID.dat_02)
QID.datR <- MergeWikiData(Data=QID.dat_02, 
                          Labels=Labels)
QID.datR <- QID.datR[QID.datR$subject != QID.datR$parentClass,]
QID.datR$subjectLabel <- paste0(QID.datR$subjectLabel, ".", QID.datR$subject)
QID.datR$parentClassLabel <- paste0(QID.datR$parentClassLabel, ".", QID.datR$parentClass)
head(QID.datR)

agGraphSearch:::agVisNetwork(Graph=QID.datR,
                             NodeColorRandom=F, Count=2, 
                             Size=10, SmallSize=5, StarSize=10, 
                             FontSize=7, 
                             Output=T, Browse=F,
                             FilePath= paste0("./agVisNetwork_entire.html"))
if(!dir.exists("04_Wiki_PolyInfo_02")){dir.create("04_Wiki_PolyInfo_02")}
suppressMessages(filesstrings::file.move(files = paste0("./agVisNetwork_entire.html"),
                        destinations = "./04_Wiki_PolyInfo_02", overwrite = T))

#################################################
#Count entities and triples
#################################################
#entities
E01 <- length(unique(c(QID.dat_02$Subject, QID.dat_02$Object)))
E01
#[1] 763

#triples
E02 <- length(unique(QID.dat_02$triple))
E02
#[1] 1292

#################################
#Calculate CU entities
#################################
CUcounts00
cu_table <- table(CUcounts00)
cu_table <- cu_table[rev(order(cu_table))]
cu_table1 <- data.frame(parentClass=names(cu_table),
                        Freq=as.numeric(cu_table), 
                        row.names = 1:length(cu_table),
                        stringsAsFactors = F)

head(cu_table1)
cu_table2 <- merge(cu_table1, 
                   Labels[Labels$Property == "rdfs:label",],
                   by.x = "parentClass", by.y = "Subject", 
                   all.x = T, all.y = F, sort=F)
cu_table3 <- cu_table2[cu_table2$Freq > 1,]
head(cu_table3)
tail(cu_table3)

#CU entities
dim(cu_table3)
#[1] 346   5

```

## Graph analysis algorism

```{r echo=TRUE, eval=FALSE}
QID.datRR <- NULL
for(n in 1:length(QID.dat)){
  #n <- 1
  message(n)
  datR <- MergeWikiData(Data=QID.dat[[n]], 
                        Labels=Labels)
  print(head(datR))
  QID.datRR[[n]] <- datR
  names(QID.datRR)[n] <- names(QID.dat)[n]
}

#set parameters
graphList <- QID.datRR
search_List <- QID.list
CU_List <- cu_table3$parentClass

#Calculation
SearchRnage <- agGraphAnalysis(graphList=graphList,
                               search_List=search_List,
                               CU_List=CU_List)
#system("mv -f ./Results_211018_1939 ./04_Wiki_PolyInfo_02")

#Levels
SearchRnage00 <- SearchRnage[!is.na(SearchRnage$Levels),]
SearchRnage00 <- SearchRnage00[order(SearchRnage00$Levels),]
rownames(SearchRnage00) <- 1:nrow(SearchRnage00)
head(SearchRnage00)
tail(SearchRnage00)

#Merge labels
SearchRnage01 <- merge(SearchRnage00,
                   Labels[Labels$Property == "rdfs:label",],
                   by.x = "CommonEntity", by.y = "Subject", 
                   all.x = T, all.y = F, sort=F)
SearchRnage01 <- SearchRnage01[order(SearchRnage01$Levels),]
rownames(SearchRnage01) <- 1:nrow(SearchRnage01)
SearchRnage01$Property <- "rdfs:label"
SearchRnage01$Object[is.na(SearchRnage01$Object)] <- SearchRnage01$CommonEntity[is.na(SearchRnage01$Object)]
head(SearchRnage01, n=15)
tail(SearchRnage01, n=15)

#saveRDS(SearchRnage01, "SearchRnage01.Rds")

```

# Subordinate search

```{r echo=TRUE, eval=FALSE}
if(!dir.exists("04_Wiki_PolyInfo_03")){dir.create("04_Wiki_PolyInfo_03")}
ECU.list <- SearchRnage01

#Run
for(n in 1:nrow(ECU.list)){
#n <- 1
message("No.", n, ": ", ECU.list$CommonEntity[n], " ", ECU.list$Object[n])
Dat <- c(); x <- 0; Query <- ECU.list$CommonEntity[n]

repeat{
x <- x + 1
message("x: ", x)

#Both wdt:P279 and wdt:P31
b1 <- ClassHi[ClassHi$Object %in% Query,]

#Only wdt:P279 when x = Levels
if(x != ECU.list$Levels[n]){
  b1 <- b1[b1$Property == "wdt:P279",]
}

if(nrow(b1) == 0){
  rownames(Dat) <- 1:nrow(Dat)
  Dat$triple <- paste0(Dat$Subject, ".", Dat$Property, ".", Dat$Object)
  Dat <- Dat[as.numeric(rownames(unique(Dat["triple"]))),-c(ncol(Dat))]
  rownames(Dat) <- 1:nrow(Dat)
  #head(Dat); dim(Dat)
  break
  }
Dat <- rbind(Dat, b1)
Query <- b1$Subject
if(x == ECU.list$Levels[n]){
  rownames(Dat) <- 1:nrow(Dat)
  Dat$triple <- paste0(Dat$Subject, ".", Dat$Property, ".", Dat$Object)
  Dat <- Dat[as.numeric(rownames(unique(Dat["triple"]))),-c(ncol(Dat))]
  rownames(Dat) <- 1:nrow(Dat)
  #head(Dat); dim(Dat)
  break
}
}
#head(Dat); dim(Dat)
print(dim(Dat))
saveRDS(Dat,
        paste0("./04_Wiki_PolyInfo_03/", 
               formatC(n, width = 4, flag = "0"),
                "_L", ECU.list$Levels[n], "_",
               ECU.list$CommonEntity[n],
               ".Rds"))
}

```

# Calucation

```{r echo=TRUE, eval=FALSE}
#SearchRnage01 <- readRDS("SearchRnage01.Rds")
dim(SearchRnage01)

#01 Barplot
a <- data.frame(No=names(table(SearchRnage01$Levels)),
                each_entity=as.numeric(table(SearchRnage01$Levels)))

head(a)
fig <- plotly::plot_ly(a, x = ~No, y = ~each_entity, type = 'bar', name = '',
               hovertemplate = paste('%{y}', sep=""),
               marker = list(color = 'rgb(158,202,225)', line = list(color = 'rgb(8,48,107)', width = 0.25)))
fig <- fig %>% plotly::layout(title = paste("Number of ECU entities", sep=""),
                      yaxis = list(title = 'Entity number', linewidth = 1),
                      xaxis = list(title = "NES", ticks = "outside", linewidth = 0,
                                     tick0 = 1, dtick = 1),
                      margin = list(l=50, r=10, b=50, t=50, pad=4))
fig

if(!dir.exists("04_Wiki_PolyInfo_04")){dir.create("04_Wiki_PolyInfo_04")}
Filename <- paste0("./Barplot_results_", format(Sys.time(), "%y%m%d"),"_01.html")
htmlwidgets::saveWidget(plotly::as_widget(fig), file=Filename)
system(paste0("mv ", Filename, " ./04_Wiki_PolyInfo_04"))

##02 
ECU.list <- SearchRnage01
ECU.list$UniTripleNum <- NA
ECU.list$UniEntityNum <- NA
TotalData <- NULL

for(n in 1:nrow(ECU.list)){
#n <- 1
message(n)

b <- readRDS(paste0("./04_Wiki_PolyInfo_03/", 
               formatC(n, width = 4, flag = "0"),
                "_L", ECU.list$Levels[n], "_",
               ECU.list$CommonEntity[n], ".Rds"))

#head(b)
b$triple <- paste0(b$Subject, ".",
                    b$Property, ".",
                    b$Object)
ECU.list$UniTripleNum[n] <- length(unique(b$triple))
ECU.list$UniEntityNum[n] <- length(unique(c(b$Subject, b$Object)))
#head(ECU.list)
#head(b); head(b[,-4])
TotalData[[n]] <- b[,-4]
}

head(ECU.list)
rownames(ECU.list) <- 1:nrow(ECU.list)
#str(TotalData)
TotalDataECU <- NULL

for(m in 1:7){
  #m <- 1
  message("m: ", m)
  d <- ECU.list[ECU.list$Levels == m,]
  d1 <- as.numeric(rownames(d))
  temp <- NULL
  for(n in d1){
    #n <- 1
    message("n: ", n)
    temp <- rbind(temp, TotalData[[n]])
  }
temp$triple <- paste0(temp$Subject, ".",
                       temp$Property, ".",
                       temp$Object)
rownames(temp) <- 1:nrow(temp)
temp <- temp[as.numeric(rownames(unique(temp["triple"]))),]
#head(temp)
TotalDataECU[[m]] <- temp
}

str(TotalDataECU)
CountDat <- data.frame(No=1:7,
                       UniEntityNum=NA,
                       UniTripleNum=NA,
                       AccEntityNum=NA,
                       AccTripleNum=NA)
temp <- NULL

for(n in 1:length(TotalDataECU)){
  #n <- 1
  message("n: ", n)
  e <- TotalDataECU[[n]]
  #head(e)
  CountDat$UniEntityNum[n]  <- length(unique(c(e$Subject, e$Object)))
  CountDat$UniTripleNum[n] <- length(unique(e$triple))
  
  temp <- rbind(temp, TotalDataECU[[n]])
  rownames(temp) <- 1:nrow(temp)
  temp <- temp[as.numeric(rownames(unique(temp["triple"]))),]
  CountDat$AccEntityNum[n]  <- length(unique(c(temp$Subject, temp$Object)))
  CountDat$AccTripleNum[n] <- length(unique(temp$triple))
}

CountDat


```


# Evaluation

```{r echo=TRUE, eval=FALSE}

```

